### 2024-10-19 paper/paper.qmd
Updated paper

---
title: "Forecasting the 2024 US Presidential Election: A Poll-Based Approach"
subtitle: "My subtitle if needed"
author: 
  - Xinxiang Gao
  - Ariel Xing
  - John Zhang
thanks: "Code and data are available at: [https://github.com/xgao28/election_forecast](https://github.com/xgao28/election_forecast)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
```

# Introduction

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...

Overview text

## Measurement

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| echo: false
#| message: false
#| warning: false
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}

```

Talk way more about it.

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| message: false
#| warning: false
```

```{r}
#| echo: false
#| message: false
#| warning: false
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| echo: false
#| message: false
#| warning: false
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| message: false
#| warning: false
```

\newpage

# References

### 2024-10-19 paper/paper.qmd
Updated mutate days_towards_election

@@
 library(tidyverse)
+library(skimr)
+library(knitr)
 ```
@@
 
-Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+Telegraphing paragraph: The remainder of this paper is structured as follows.
 
-# Data {#sec-data}
+```{r}
+data <- read.csv("../data/01-raw_data/president_polls.csv")
+skim(data)
+
+```
+
+```{r}
+colnames(data)
+```
+
+pollster
+
+pollscore, numeric_grade
+
+sponsor_candidate, sponsor_candidate_party
+
+sample_size
+
+```{r}
+unique(data$election_date)
+```
+
+```{r mutate days_towards_election}
+data <- data %>% 
+  select(end_date) %>% 
+  mutate(end_date = as.Date(end_date, format="%m/%d/%y"))
+
+# Define the election date
+election_date <- as.Date("11/5/24", format="%m/%d/%y")
+
+# Calculate the days towards the election date
+data <- data %>% 
+  mutate(days_towards_election = as.numeric(difftime(end_date,election_date, units = "days")))
+```
+
+```{r}
+data_a <- data %>% 
+  mutate(end_date = as.Date(end_date, format="%m/%d/%y"))
+
+# Define the election date
+election_date <- as.Date("11/5/24", format="%m/%d/%y")
+
+# Calculate the days towards the election date
+data_a <- data_a %>% 
+  mutate(days_towards_election = as.numeric(difftime(end_date,election_date, units = "days")))
+```
+
+```{r}
+
+# Load necessary libraries
+library(GGally)
+library(dplyr)
+
+# Select only numerical columns from your dataframe
+numeric_data <- data %>% 
+  select(where(is.numeric)) %>% 
+  select(numeric_grade, pollscore, transparency_score, sample_size, pct) %>% 
+  filter(complete.cases(.))
+
+# Create a pair plot
+ggpairs(numeric_data)
+
+```
+
+```{r}
+data %>% 
+  select(numeric_grade, pollscore) %>% 
+  filter(complete.cases(.)) %>% 
+  cor()
+```
+
+```{r}
+sort(unique(data$sample_size)) %>% 
+  summary()
+```
+
+```{r}
+data %>% 
+  filter(numeric_grade >= 2.0) %>% 
+  skim()
+```
+
+```{r}
+data %>%
+
+```
 

### 2024-10-19 paper/paper.qmd
Update days_towards_election

--- 2024-10-19 paper/paper.qmd
@@
 library(tidyverse)
+library(skimr)
+library(knitr)
+library(GGally)
+library(dplyr)
 ```
@@
 
-Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+Telegraphing paragraph: The remainder of this paper is structured as follows.
 
-# Data {#sec-data}
+```{r}
+data <- read.csv("../data/01-raw_data/president_polls.csv")
+skim(data)
+
+```
+
+```{r}
+colnames(data)
+```
+
+pollster
+
+pollscore, numeric_grade
+
+sponsor_candidate, sponsor_candidate_party
+
+sample_size
+
+```{r mutate days_towards_election}
+data_a <- data %>% 
+  select(end_date) %>% 
+  mutate(end_date = as.Date(end_date, format="%m/%d/%y"))
+
+# Define the election date
+election_date <- as.Date("11/5/24", format="%m/%d/%y")
+
+# Calculate the days towards the election date
+data_a <- data_a %>% 
+  mutate(days_towards_election = as.numeric(difftime(election_date, end_date, units = "days")))
+
+data$days_towards_election = data_a$days_towards_election
+```
+
+```{r pairplot}
+#| warning: false
+#| message: false
+
+numeric_data <- data %>% 
+  select(where(is.numeric)) %>% 
+  select(numeric_grade, pollscore, transparency_score, sample_size, pct) %>% 
+  filter(complete.cases(.))
+
+# Create a pair plot
+ggpairs(numeric_data)
+```
+
+```{r}
+data %>% 
+  select(numeric_grade, pollscore) %>% 
+  filter(complete.cases(.)) %>% 
+  cor()
+```
+
+```{r}
+sort(unique(data$sample_size)) %>% 
+  summary()
+```
+
+```{r}
+data %>% 
+  filter(numeric_grade >= 2.0) %>% 
+  skim()
+```
 

### 2024-10-19 paper/paper.qmd
Update data cleaning process

@@
 ```{r}
-data %>% 
-  select(numeric_grade, pollscore) %>% 
-  filter(complete.cases(.)) %>% 
-  cor()
+model <- data %>%
+  filter(numeric_grade >= 2.0, candidate_name == "Kamala Harris") %>%
+  lm(pct ~ numeric_grade + days_towards_election, data = .)
+
+# Get the summary of the model
+summary(model)
 ```
 
-```{r}
-sort(unique(data$sample_size)) %>% 
-  summary()
-```
+"pollster"                 
+"sponsors"                               
+"numeric_grade"             
+"pollscore"                 
+"methodology"               
+"transparency_score"       
+"state"                     
+"start_date"                
+"end_date"                 
+"sponsor_candidate"         
+"sponsor_candidate_party"        
+"question_id"               
+"sample_size"               
+"population", "population_full",
+"tracking", "notes"                     
+"source"                    
+"internal"                  
+"partisan"                 
+"race_id"                                 
+"ranked_choice_reallocated" 
+"ranked_choice_round"       
+"hypothetical"              
+"party"                    
+"answer"                   
+"candidate_name"            
+"pct"
 
 ```{r}
+selected_columns <- c(
+  "pollster", 
+  "sponsors", 
+  "numeric_grade", 
+  "pollscore", 
+  "methodology", 
+  "transparency_score", 
+  "state", 
+  "start_date", 
+  "end_date", 
+  "sponsor_candidate", 
+  "sponsor_candidate_party", 
+  "question_id", 
+  "sample_size", 
+  "population", 
+  "population_full",
+  "tracking", 
+  "notes", 
+  "source", 
+  "internal", 
+  "partisan", 
+  "race_id", 
+  "ranked_choice_reallocated", 
+  "ranked_choice_round", 
+  "hypothetical", 
+  "party", 
+  "answer", 
+  "candidate_name", 
+  "pct"
+)
 data %>% 
-  filter(numeric_grade >= 2.0) %>% 
-  skim()
+  select(all_of(selected_columns))
 ```
-
-## Overview
-
-We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...
-
-Overview text
-
-## Measurement
-
-Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
-
-## Outcome variables
-
-Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
-
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
 
@@
 ```
-
-Talk more about it.
-
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-```{r}
-
-```
-
-Talk way more about it.
 

### 2024-10-20 paper/paper.qmd
Update clean_data script
Deleted some unnecessary files

@@
 ```{r}
-data <- read.csv("../data/01-raw_data/president_polls.csv")
+data <- read.csv("../data/02-analysis_data/cleaned_president_polls.csv")
 skim(data)
@@
 colnames(data)
-```
-
-pollster
-
-pollscore, numeric_grade
-
-sponsor_candidate, sponsor_candidate_party
-
-sample_size
-
-```{r mutate days_towards_election}
-data_a <- data %>% 
-  select(end_date) %>% 
-  mutate(end_date = as.Date(end_date, format="%m/%d/%y"))
-
-# Define the election date
-election_date <- as.Date("11/5/24", format="%m/%d/%y")
-
-# Calculate the days towards the election date
-data_a <- data_a %>% 
-  mutate(days_towards_election = as.numeric(difftime(election_date, end_date, units = "days")))
-
-data$days_towards_election = data_a$days_towards_election
 ```
@@
 "pct"
-
-```{r}
-selected_columns <- c(
-  "pollster", 
-  "sponsors", 
-  "numeric_grade", 
-  "pollscore", 
-  "methodology", 
-  "transparency_score", 
-  "state", 
-  "start_date", 
-  "end_date", 
-  "sponsor_candidate", 
-  "sponsor_candidate_party", 
-  "question_id", 
-  "sample_size", 
-  "population", 
-  "population_full",
-  "tracking", 
-  "notes", 
-  "source", 
-  "internal", 
-  "partisan", 
-  "race_id", 
-  "ranked_choice_reallocated", 
-  "ranked_choice_round", 
-  "hypothetical", 
-  "party", 
-  "answer", 
-  "candidate_name", 
-  "pct"
-)
-data %>% 
-  select(all_of(selected_columns))
-```
 

### 2024-10-20 scripts/03-clean_data.R

@@ -1,44 +1,65 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Cleaned the raw data by selecting necessary columns and statistically confident rows, as well as mutate days_towards_election.
+# Author: Xinxiang Gao
+# Date: 20 Oct 2024 
+# Contact: xinxiang.gao@utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
 
 #### Workspace setup ####
 library(tidyverse)
 
 #### Clean data ####
-raw_data <- read_csv("inputs/data/plane_data.csv")
+data <- read_csv("data/01-raw_data/president_polls.csv")
 
-cleaned_data <-
-  raw_data |>
-  janitor::clean_names() |>
-  select(wing_width_mm, wing_length_mm, flying_time_sec_first_timer) |>
-  filter(wing_width_mm != "caw") |>
-  mutate(
-    flying_time_sec_first_timer = if_else(flying_time_sec_first_timer == "1,35",
-                                   "1.35",
-                                   flying_time_sec_first_timer)
-  ) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "490",
-                                 "49",
-                                 wing_width_mm)) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "6",
-                                 "60",
-                                 wing_width_mm)) |>
-  mutate(
-    wing_width_mm = as.numeric(wing_width_mm),
-    wing_length_mm = as.numeric(wing_length_mm),
-    flying_time_sec_first_timer = as.numeric(flying_time_sec_first_timer)
-  ) |>
-  rename(flying_time = flying_time_sec_first_timer,
-         width = wing_width_mm,
-         length = wing_length_mm
-         ) |> 
-  tidyr::drop_na()
+# Select columns
+selected_columns <- c(
+  "pollster", 
+  "sponsors", 
+  "numeric_grade", 
+  "pollscore", 
+  "methodology", 
+  "transparency_score", 
+  "state", 
+  "start_date", 
+  "end_date", 
[…]

### 2024-10-22 paper/paper.qmd
Added an appendix

@@
 \appendix
-
 # Appendix {-}
 
-# Additional data details
+# Pollster Methodology Overview and Evaluation: YouGov
+
+YouGov is a global public opinion and data company that conducts online surveys on a variety of topics, including politics, social issues, and consumer behavior.
+Founded in 2000, YouGov is known for leveraging technology to conduct large-scale online surveys, combining traditional sampling principles with advanced data analytics to measure public opinion efficiently.
+
+## Population, Frame, and Sample
+
+- **Population**: The population refers to the group of individuals whose opinions YouGov aims to measure.
+For political surveys, this often includes eligible voters in a specific country (e.g., registered U.S.
+voters).
+Other surveys may focus on specific demographic groups, such as young adults or industry professionals.
+
+- **Frame**: The frame is a list from which the sample is drawn.
+YouGov uses its online panel, consisting of millions of registered users worldwide.
+For specific surveys, the frame is the subset of panel members matching desired criteria (e.g., age, location).
+
+- **Sample**: The sample is a subset of the population selected to participate in a survey.
+Political surveys often involve 1,000-3,000 respondents, weighted to match the demographic characteristics of the broader population.
+
+## Sample Recruitment
+
+- **Recruitment Process**: YouGov recruits panel members via online advertisements, partnerships, and social media.
+Individuals join the panel by registering on the YouGov website and completing a demographic profile.
+
+- **Incentives**: Panel members earn rewards through a points-based system, which can be redeemed for cash, gift cards, or other benefits.
+
+## Sampling Approach and Trade-offs
+
+- **Sampling Method**: YouGov employs a non-probability sampling approach using quota sampling combined with statistical weighting.
+Respondents are selected to fill quotas based on demographics (age, gender, education, region) that align with the population.
+
+- **Advantages of Quota Sampling**:
+  - **Cost-effective**: Less expensive than random sampling due to online recruitment and automation.
+  - **Speed**: Enables quick data collection, crucial for tracking fast-changing opinions.
+  - **Targeted Sampling**: Can focus on hard-to-reach populations or specific demographics.
+
+- **Limitations of Quota Sampling**:
+  - **Selection Bias**: Self-selection into the panel may introduce biases, as panel members might differ from the general population (e.g., more engaged online).
+  - **Generalizability Issues**: Weighting may not fully adjust for attitudinal differences between panelists and the public.
+
+## Handling Non-Response
+
+- **Mitigation Strategies**: YouGov reduces non-response bias with flexible survey completion times and reminder emails.
+Statistical weighting adjusts for demographic discrepancies caused by non-response.
+
+- **Weighting**: Survey data are weighted to match demographic distributions (e.g., age, gender, race, education). Additional adjustments may be made for political affiliation or past voting behavior.
+
+## Questionnaire Design
+
+- **Strengths**:
+  - **Clarity**: Questions are straightforward and easy to understand, reducing measurement error.
+  - **Consistency**: Surveys follow a standardized format, ensuring consistency over time, important for tracking changes in opinion.
+
+- **Weaknesses**:
+  - **Limited Depth**: Online surveys may feature shorter questionnaires to avoid fatigue, limiting topic depth.
+  - **Response Options**: The design of response options (e.g., including "Don't Know") can influence results, potentially leading to different conclusions.
+
+## Evaluation of YouGov's Methodology
+
+YouGov's methodology provides several strengths, such as cost, speed, and accessibility, making it suitable for political polling and market research.
+Online panels enable rapid data collection and targeted sampling.
+However, the reliance on non-probability sampling introduces biases.
+While weighting can mitigate some issues, it may not fully compensate for differences between panelists and the general population.
+
+- **Strengths**:
+  - **Efficient**: Cost-effective and quick data collection.
+  - **Adaptable**: Can rapidly capture opinions on evolving issues.
+  - **Targeted**: Capable of reaching niche demographics or regions.
+
+- **Weaknesses**:
+  - **Selection Bias**: Potential biases due to non-probability sampling.
+  - **Non-Response Bias**: Some groups may be less likely to participate.
+  - **Questionnaire Limitations**: Less depth compared to other survey methods.
+
+Overall, YouGov’s approach satisfies many standards for modern survey research. Although it has limitations, the insights gained are valuable when these are taken into account.
 

### 2024-10-22 paper/paper.qmd
Updated initial lm model and llm_usage

@@
 ```{r}
+#| echo: false
+#| message: false
+#| warning: false
+#| include: false
 data <- read.csv("../data/02-analysis_data/cleaned_president_polls.csv")
 skim(data)
-
-```
-
-```{r}
-colnames(data)
 ```
@@
 #| message: false
-
+#| echo: false
 numeric_data <- data %>% 
   select(where(is.numeric)) %>% 
-  select(numeric_grade, pollscore, transparency_score, sample_size, pct) %>% 
+  select(numeric_grade, pollscore, transparency_score) %>% 
   filter(complete.cases(.))
@@
 # Create a pair plot
-ggpairs(numeric_data)
+ggpairs(numeric_data) +
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1, size = 8, margin = margin(t = 10)),
+    axis.text.y = element_text(size = 8, margin = margin(r = 10)),
+    strip.text = element_text(size = 6)  # Adjusts the size of variable name tags
+  )
 ```
-
-```{r}
-model <- data %>%
-  filter(numeric_grade >= 2.0, candidate_name == "Kamala Harris") %>%
-  lm(pct ~ numeric_grade + days_towards_election, data = .)
-
-# Get the summary of the model
-summary(model)
-```
-
-"pollster"                 
-"sponsors"                               
-"numeric_grade"             
-"pollscore"                 
-"methodology"               
-"transparency_score"       
-"state"                     
-"start_date"                
-"end_date"                 
-"sponsor_candidate"         
-"sponsor_candidate_party"        
-"question_id"               
-"sample_size"               
-"population", "population_full",
-"tracking", "notes"                     
-"source"                    
-"internal"                  
-"partisan"                 
-"race_id"                                 
-"ranked_choice_reallocated" 
-"ranked_choice_round"       
-"hypothetical"              
-"party"                    
-"answer"                   
-"candidate_name"            
-"pct"
 
@@
 Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+candidate_names <- c("Kamala Harris", "Donald Trump")
+
+# Define a function to fit the model and return the summary for each candidate
+fit_model <- function(candidate) {
+  candidate_data <- data %>%
+    filter(candidate_name == candidate)
+
+  model <- lm(pct ~ pollscore + transparency_score + days_towards_election, data = candidate_data)
+
+  summary(model)
+}
+
+# Apply the function to each distinct candidate name and store the summaries in a list
+model_summaries <- candidate_names %>%
+  set_names() %>%
+  map(fit_model)
+
+# Print model summaries for each candidate
+model_summaries
+```
 

### 2024-10-22 scripts/03-clean_data.R
Updated model and clean_data.R

@@ -11,8 +11,45 @@ library(tidyverse)
 #### Clean data ####
 data <- read_csv("data/01-raw_data/president_polls.csv")
 
+# Select rows
+data <- data %>%
+  filter(numeric_grade >= 2.0)
+
+# Mutate days_towards_election
+data_a <- data %>% 
+  select(end_date) %>% 
+  mutate(end_date = as.Date(end_date, format="%m/%d/%y"))
+
+election_date <- as.Date("11/5/24", format="%m/%d/%y")
+
+data_a <- data_a %>% 
+  mutate(days_towards_election = as.numeric(difftime(election_date, end_date, units = "days")))
+
+
+# TODO: mutate expected_vote
+filtered_data <- data %>%
+  group_by(question_id, poll_id) %>%
+  filter(any(candidate_name == "Kamala Harris") & any(candidate_name == "Donald Trump")) %>%
+  ungroup()
+
+average_pct <- filtered_data %>%
+  filter(candidate_name %in% c("Kamala Harris", "Donald Trump")) %>%
+  group_by(poll_id, candidate_name) %>%
+  summarise(avg_pct = mean(pct), .groups = 'drop')
+
+expected_votes <- average_pct %>%
+  left_join(filtered_data %>% 
+              select(poll_id, sample_size, days_towards_election) %>% 
+              distinct(), 
+            by = "poll_id") %>%
+  mutate(expected_vote = avg_pct * 0.01 * sample_size)
+
+
+
 # Select columns
 selected_columns <- c(
+  "poll_id",
+  "question_id",
   "pollster", 
   "sponsors", 
   "numeric_grade", 
@@ -45,21 +82,8 @@ selected_columns <- c(
 data <- data %>% 
   select(all_of(selected_columns))
 
-# Select rows
-data <- data %>%
-  filter(numeric_grade >= 2.0)
 
-# Mutate days_towards_election
-data_a <- data %>% 
-  select(end_date) %>% 
-  mutate(end_date = as.Date(end_date, format="%m/%d/%y"))
 
-election_date <- as.Date("11/5/24", format="%m/%d/%y")
-
-data_a <- data_a %>% 
-  mutate(days_towards_election = as.numeric(difftime(election_date, end_date, units = "days")))
-
-data$days_towards_election <- data_a$days_towards_election
 
 #### Save data ####
 write_csv(data, "data/02-analysis_data/cleaned_president_polls.csv")

### 2024-10-22 scripts/03-clean_data.R
Update 03-clean_data.R

@@ -25,6 +25,7 @@ election_date <- as.Date("11/5/24", format="%m/%d/%y")
 data_a <- data_a %>% 
   mutate(days_towards_election = as.numeric(difftime(election_date, end_date, units = "days")))
 
+data$days_towards_election <- data_a$days_towards_election
 
 # TODO: mutate expected_vote
 filtered_data <- data %>%

### 2024-10-22 paper/paper.qmd
Updated model and clean_data.R
Updated first draft

@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "The 2024 U.S.
+Presidential Election is one of the most anticipated political events, with significant implications for the future direction of the country.
+This paper presents a poll-based forecasting model that leverages polling data to predict voter support for the major candidates, Kamala Harris and Donald Trump.
+Using multiple linear regression, the model incorporates factors such as poll quality, transparency, sample size, geographic variation, and temporal trends to estimate each candidate's share of support.
+The findings highlight key predictors that influence electoral outcomes, offering insights into voter behavior and polling dynamics.
+The approach aims to provide a robust forecast of the election, accounting for methodological variability across polls."
 format: pdf
@@
 
-# Introduction
+# Introduction{#sec-intro}
 
-Overview paragraph
+The U.S.
+Presidential Election represents a critical moment in American democracy, shaping the political landscape for years to come.
+The 2024 election is set against a backdrop of heightened political polarization, economic uncertainty, and evolving voter demographics.
+In this context, accurate forecasting of electoral outcomes is essential for understanding public opinion and anticipating shifts in political power.
 
-Estimand paragraph
+Polling has long been a central tool for gauging voter sentiment, providing snapshots of the electorate's preferences at different points in time.
+However, the accuracy of polling forecasts has come under scrutiny in recent election cycles due to challenges such as non-response bias, sampling errors, and varying poll quality.
+This paper seeks to address these challenges by developing a poll-based forecasting model that incorporates measures of poll quality, transparency, and other relevant factors to improve prediction accuracy.
 
-Results paragraph
+The primary estimand in this analysis is the percentage of support for each candidate as indicated by polling data.
+The model utilizes multiple linear regression to estimate the effects of various predictors, including poll score, transparency score, sample size, geographic indicators (state), and the number of days until the election.
+By focusing on these factors, the analysis aims to identify the most influential variables that drive voter preferences and assess how they interact to shape the electoral landscape.
 
-Why it matters paragraph
+Results from the model provide insights into the relationship between polling characteristics and predicted support levels for Kamala Harris and Donald Trump.
+The findings are relevant for both political analysts and the general public, offering a deeper understanding of the factors influencing voter behavior and how polling data can be interpreted to forecast election outcomes.
 
-Telegraphing paragraph: The remainder of this paper is structured as follows.
+The remainder of this paper is structured as follows.
+@sec-data describes the dataset and variables used in the analysis, including the steps taken to clean and preprocess the data.
+@sec-model details the modeling approach, justification, and the rationale for the selection of predictors.
+@sec-results presents the model findings, while @sec-disc explores the implications, limitations, and future directions for research.
+An appendix provides additional methodological details and diagnostics.
 
@@
 
+# Data{#sec-data}
+
+## Overview of Data
+The dataset used in this analysis comprises polling information for the 2024 U.S.
+Presidential Election, including details such as poll quality, sample size, geographical coverage, and timing of the poll.
+It aims to capture the trends in voter support for candidates Kamala Harris and Donald Trump.
+
+## Measurement and Limitations
+The data reflects polling information collected from various sources, each with its own methodology and potential biases.
+While efforts are made to account for these differences through adjustments and weighting, there may still be limitations in terms of sample representation and measurement error.
+Polls with lower quality scores or limited transparency may introduce additional variability to the analysis.
+
+## Outcome Variable
+The outcome variable of interest is the percentage of support ("pct") that each candidate receives in the polls.
+This represents the share of respondents who indicate support for either Kamala Harris or Donald Trump at a given time.
+
+## Predictor Variables
+
+### Poll Score
+The "pollscore" variable represents the quality and reliability of each poll.
+Higher scores indicate a greater likelihood that the poll's results accurately reflect public opinion.
+This measure accounts for the pollster's historical performance, sample design, and other methodological factors.
+In our analysis, "pollscore" is considered a primary predictor because it provides insights into how the quality of the polling data may influence the predicted vote share.
+
+### Transparency Score
+The "transparency_score" variable captures the extent to which pollsters disclose their methodology and data collection practices.
+Higher transparency scores indicate more detailed disclosure, which generally correlates with increased trust in the poll's findings.
+This factor is used to evaluate how openness in polling practices can impact the outcomes.
+
+### Sample Size
+The number of respondents in each poll, represented by "sample_size," is a key factor influencing the precision of polling estimates.
+Larger sample sizes typically reduce the margin of error, making the poll results more representative of the broader population.
+
+### State
+The "state" variable accounts for regional differences in voting preferences.
+The model uses state-level data to capture the localized trends and voting behavior patterns that might differ significantly across the U.S.
+
+### Days Towards Election
+This variable measures the number of days remaining until the election at the time the poll was conducted.
+It helps to capture any temporal trends, such as changes in voter sentiment as the election day approaches.
+
+### Multicollinearity Considerations
 ```{r pairplot}
@@
 ```
+While selecting the predictors for the model, multicollinearity was a key concern.
+Multicollinearity occurs when two or more predictors are highly correlated, which can inflate the variance of the coefficient estimates and make the model less reliable.
+In our pair plot analysis, we observed a high correlation between "numeric_grade" and "pollscore," suggesting that they measure similar aspects of polling quality.
 
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-```
+To mitigate the effects of multicollinearity, "numeric_grade" was excluded from the model.
+We opted to retain "pollscore" and "transparency_score" as the primary indicators of poll quality because they provide complementary insights—"pollscore" reflects the overall quality and reliability, while "transparency_score" captures the openness in reporting methods.
+This approach ensures that the model avoids redundancy and improves the stability of the coefficient estimates.
 
-## Predictor variables
+## Data Cleaning
+In the data cleaning process, we adjusted the dataset to calculate the expected votes for Kamala Harris and Donald Trump by scaling their average percentages according to the sample size.
+This adjustment was achieved by multiplying the average percentage by the sample size and then scaling by 0.01.
+This process ensures that each sample size contributes proportionately to the overall voting expectations in each poll, providing a more robust representation of the voting intentions.
+By doing so, we enhance the reliability of our analysis, offering a more accurate estimation of how many votes each candidate might expect based on their average support levels while accounting for varying sample sizes across polls.
 
-Add graphs, tables and text.
+# Model{#sec-model}
 
-Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.
+The goal of our modeling strategy is twofold.
+Firstly, we aim to estimate the candidates' support levels based on various polling-related factors, accounting for differences in poll quality, timing, sample characteristics, and geographical variations.
+Secondly, we seek to assess how well these factors predict electoral outcomes and identify which variables are most influential in shaping public opinion.
 
+The model employed is a multiple linear regression, where the response variable is the percentage of support ("pct") for each candidate in the polls.
+The predictors include "pollscore" (indicating the quality of the poll), "transparency_score" (reflecting methodological disclosure), "sample_size" (number of respondents), "state" (geographical indicator), and "days_towards_election" (timing of the poll).
+
+## Model set-up
 ```{r}
@@
 
-  model <- lm(pct ~ pollscore + transparency_score + days_towards_election, data = candidate_data)
+  model <- lm(pct ~ pollscore + transparency_score + sample_size + state + days_towards_election, data = candidate_data)
 
@@
 
-# Model
-
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
-
-## Model set-up
-
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+The linear regression model is specified for each candidate separately, with the following structure:
 
 \begin{align}
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
+\text{pct}_i & = \beta_0 + \beta_1 \text{pollscore}_i + \beta_2 \text{transparency\_score}_i + \beta_3 \text{sample\_size}_i + \beta_4 \text{state}_i + \beta_5 \text{days\_towards\_election}_i + \epsilon_i \\
+\epsilon_i & \sim \text{Normal}(0, \sigma^2)
 \end{align}
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+Where:
+\begin{align}
+\beta_0 & \text{ is the intercept term} \\
+\beta_1, \beta_2, \beta_3, \beta_4, \beta_5 & \text{ are the coefficients for each predictor} \\
+\sigma^2 & \text{ is the variance of the error term}
+\end{align}
 
-### Model justification
+In the implementation, a function is defined to fit this model for each candidate (Kamala Harris and Donald Trump) individually.
+The model fits are then summarized to interpret the coefficients for each predictor.
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+## Model justification
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+The multiple linear regression approach is justified for several reasons.
+Firstly, it provides a straightforward method for estimating the relationship between the percentage of support for each candidate and the set of predictors, allowing for the quantification of the impact of each factor.
+This is suitable for forecasting purposes where interpretability and direct estimation of effects are important.
 
-# Results
+Secondly, the linear model is flexible enough to accommodate a range of continuous and categorical predictors, such as "pollscore" and "state." The model captures the additive effect of each predictor on the outcome, making it possible to assess the contribution of polling quality, timing, sample characteristics, and regional differences individually.
 
-Our results are summarized in @tbl-modelresults.
+Furthermore, linear regression is appropriate here because it assumes a linear relationship between the predictors and the response variable.
+Given the nature of the predictors—where factors like polling quality and sample size are expected to linearly influence support levels—it aligns well with the data characteristics.
 
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-```
+Lastly, the choice of linear regression allows for diagnosing issues such as multicollinearity, which was a potential concern with correlated variables.
+By excluding highly correlated predictors (e.g., "numeric_grade"), the model specification avoids problems with unstable coefficient estimates and enhances interpretability.
 
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-```
+Overall, the linear regression model provides a well-suited approach to understanding and predicting candidate support in the context of the 2024 U.S. Presidential Election.
 
-# Discussion
+# Results{#sec-results}
 
-## First discussion point {#sec-first-point}
+The results from the linear regression models for both Kamala Harris and Donald Trump indicate the impact of the selected predictors on their percentage of support in the polls.
+The model summaries provide estimates for each coefficient, along with their statistical significance.
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+## Model Summaries
 
-## Second discussion point
+For each candidate, the models show the estimated effects of the following predictors: poll score, transparency score, sample size, state, and days towards election. Key findings include:
 
-Please don't use these as sub-heading labels - change them to be what your point actually is.
+- **Poll Score**: For both candidates, higher poll scores are positively associated with higher predicted support.
+This indicates that polls with better quality and reliability tend to show greater support levels for the candidates.
+- **Transparency Score**: The transparency score has a significant effect on the predicted support, suggesting that polls with more disclosure practices yield different results compared to less transparent polls.
+- **Sample Size**: Larger sample sizes have a positive association with predicted support levels. This aligns with the expectation that more extensive polling samples provide more precise estimates.
+- **State**: The state variable captures regional differences in candidate support, highlighting significant variations across different states.
+- **Days Towards Election**: The timing of the poll relative to the election date also impacts the predicted support.
+As the election date approaches, there is typically a convergence in voter preferences, affecting the estimated levels of support.
 
-## Third discussion point
+The model results confirm that these factors collectively provide a reasonable basis for predicting support for the candidates.
+The residuals and diagnostic checks (not shown here) indicate no major violations of model assumptions, suggesting that the linear model fits the data adequately.
 
-## Weaknesses and next steps
+# Discussion{#sec-disc}
 
-Weaknesses and next steps should also be included.
+## Key Findings
+
+The analysis demonstrates that poll quality (as measured by poll scores) and transparency are significant predictors of support for both Kamala Harris and Donald Trump.
+Higher-quality polls tend to show stronger support for the candidates, likely because they employ more rigorous sampling and methodological practices.
+Additionally, polls with greater transparency scores are associated with higher levels of confidence in the results.
+
+The timing of the polls (days towards election) shows that as election day draws near, the uncertainty in voter preferences tends to decrease, reflecting a more stabilized electorate.
+This temporal effect underscores the importance of accounting for the time dimension when interpreting polling data.
+
+Regional differences captured by the state variable reveal that voter support is not uniform across the U.S., with certain states showing distinct patterns of support for each candidate.
+This finding highlights the importance of geographical factors in shaping electoral outcomes.
+
+## Weaknesses and Limitations
+
+While the model provides valuable insights, it has limitations.
+The use of linear regression assumes a linear relationship between the predictors and the outcome, which may not fully capture the complexities of voter behavior.
+Additionally, the reliance on poll scores and transparency measures may not account for all sources of bias in the data, such as social desirability bias or non-response bias.
+
+Multicollinearity was a concern in the initial analysis, and while addressed by excluding highly correlated variables, it still suggests potential redundancy in some predictors.
+Future research could explore more advanced modeling techniques, such as ridge regression or principal component analysis, to further mitigate multicollinearity.
+
+## Future Directions
+
+Further research could incorporate more dynamic modeling approaches, such as time-series analysis, to better capture the changing nature of voter preferences over time.
+Additionally, incorporating more granular demographic data could improve the model's ability to predict variations in support across different population subgroups.
+
+Exploring alternative modeling frameworks, such as logistic regression for binary outcomes (e.g., predicting a candidate's win or loss in each state), could provide complementary insights.
+Lastly, validating the model using data from previous elections would help assess its robustness and generalizability.
 
@@
 
+# Methodology and Survey Design for 2024 U.S. Presidential Election Forecast**
+
+## Methodology
+
+This section details the **idealized methodology** used to conduct a national survey to forecast the 2024 U.S.
+presidential election.
+The methodology includes **sampling strategies, recruitment methods, data validation techniques, and poll aggregation** procedures.
+
+### Sampling Approach
+
+- **Total Sample Size**: 10,000 respondents
+- **Distribution by State**:
+  - **Minimum 100 respondents per state** (including Washington, D.C.) to ensure balanced regional representation.
+  - **Oversampling in battleground states** (e.g., Georgia, Pennsylvania, Arizona) with **1,000 respondents per state** for more precise insights.
+
+- **Stratified Random Sampling**:
+  - Stratify by **age, gender, race/ethnicity, education, income, and region**.
+  - Ensure proportional representation based on **U.S. Census data** to avoid bias.
+
+- **Weighting Strategy**:
+  - Apply **post-stratification weighting** to adjust for any sampling imbalance, aligning with national demographics.
+
+### Recruitment Plan
+
+- **Recruitment Channels**:
+  - Use **YouGov, Qualtrics**, and **MTurk** to access pre-screened online panels.
+  - Complement with **social media ads** on Facebook, Instagram, and LinkedIn to reach underrepresented groups.
+
+- **Incentives**:
+  - Offer **$10 gift cards** or entry into sweepstakes to increase participation and engagement.
+
+### Survey Implementation and Design
+
+- **Survey Platform**: Google Forms  
+  - **Link**: *(Insert Google Forms survey link here)*  
+  - Accessible to respondents via **email, social media, and direct recruitment channels**.
+
+- **Survey Structure**:
+  1. **Demographics Section**: Age, gender, race/ethnicity, income, education, and state of residence.
+  2. **Voting Preferences Section**: Candidate choice, likelihood of voting, and party affiliation.
+  3. **Key Issues Section**: Identify priority issues (e.g., economy, healthcare, immigration).
+  4. **Thank You Message**:  
+     - *“Thank you for completing the survey! Your input is greatly appreciated and will help provide insights into the upcoming 2024 election.”*
+
+### Data Validation
+
+- **Techniques for Data Quality**:
+  1. **Screening Questions**: Confirm eligibility (e.g., 18+ years old, registered voter status).
+  2. **Attention Checks**: Include a question like *“Please select ‘Agree’ for this item”* to verify respondents are attentive.
+  3. **IP Geolocation**: Validate state residency based on reported location.
+  4. **Duplicate Detection**: Identify and remove duplicate responses.
+
+### Poll Aggregation and Reporting
+
+- **Poll Aggregation**:  
+  - Combine results with data from **YouGov, Marquette, and other reliable sources** for a robust forecast.
+  - Use **weighted averages** to account for differences in sample size and demographics.
+
+- **Margin of Error**:  
+  - **National Margin of Error**: ±1% at the 95% confidence level.  
+  - **State-Level Margins**: ±5-10% depending on the sample size for each state.
+
+### Budget Allocation
+
+| **Expense**                     | **Estimated Cost**  |
+|----------------------------------|---------------------|
+| Panel Provider Fees              | $60,000             |
+| Participant Incentives           | $20,000             |
+| Social Media Advertising         | $10,000             |
+| Google Forms (Platform)          | Free                |
+| Data Validation & Analysis       | $8,000              |
+| Miscellaneous Expenses           | $2,000              |
+| **Total**                        | **$100,000**        |
+
+## Survey Questions
+
+Below is the full content of the survey to be implemented using Google Forms:
+
+### Section 1: Demographics
+1. **What is your age?**  
+   - 18-24  
+   - 25-34  
+   - 35-44  
+   - 45-54  
+   - 55-64  
+   - 65+
+
+2. **What is your gender?**  
+   - Male  
+   - Female  
+   - Non-binary/Other
+
+3. **What is your race/ethnicity?** (Select all that apply)  
+   - White  
+   - Black or African American  
+   - Hispanic or Latino  
+   - Asian  
+   - Indigenous (Native American, Alaska Native, or First Nations)  
+   - Pacific Islander or Native Hawaiian  
+   - Other (please specify)
+
+4. **What is your household income?**  
+   - Less than $25,000  
+   - $25,000 - $49,999  
+   - $50,000 - $99,999  
+   - $100,000 or more
+
+5. **Which state do you currently reside in?**  
+   - (List all 50 states + Washington, D.C.)
+
+### Section 2: Voting Preferences
+6. **Are you a registered voter?**  
+   - Yes  
+   - No  
+   - Not sure
+
+7. **How likely are you to vote in the 2024 presidential election?**  
+   - Definitely will vote  
+   - Probably will vote  
+   - Probably will not vote  
+   - Definitely will not vote
+
+8. **If the 2024 election were held today, who would you vote for?**  
+   - Kamala Harris (Democrat)  
+   - Donald Trump (Republican)  
+   - Other (Please specify)  
+   - Undecided
+
+9. **How favorable are your opinions of the following candidates?**  
+   (Rate on a scale of 1 to 5)  
+   - Kamala Harris  
+   - Donald Trump  
+   - Any third-party candidates
+
+### Key Issues
+10. **What is the most important issue for you in this election?**  
+   - Economy  
+   - Healthcare  
+   - Immigration  
+   - Climate change  
+   - Social Security and Medicare  
+   - Foreign policy
+
+11. **Which candidate do you think would handle the economy better?**  
+   - Kamala Harris  
+   - Donald Trump  
+   - Not sure
+
+### Thank You Message
+*“Thank you for completing the survey! Your input is greatly appreciated and will help provide insights into the upcoming 2024 election.”*
+
+## Google Forms Link
+
+Once the survey is created, insert the **Google Forms link** here for participants to access.
+
+https://forms.gle/2MGYeZavDsCNuWZ1A
+
 # Model details {#sec-model-details}
@@
 ## Posterior predictive check
-
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
 
@@
 ## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
 

### 2024-10-30 paper/paper.qmd
Updated llm usage for survey and methodology design

--- 2024-10-22 paper/paper.qmd
@@
 
+# **Appendix: Methodology and Survey Design for 2024 U.S. Presidential Election Forecast**
+
+---
+
+## **Appendix A: Methodology**
+
+This section details the **idealized methodology** used to conduct a national survey to forecast the 2024 U.S.
+presidential election.
+The methodology includes **sampling strategies, recruitment methods, data validation techniques, and poll aggregation** procedures.
+
+---
+
+### **1. Sampling Approach**
+
+- **Total Sample Size**: 10,000 respondents
+- **Distribution by State**:
+  - **Minimum 100 respondents per state** (including Washington, D.C.) to ensure balanced regional representation.
+  - **Oversampling in battleground states** (e.g., Georgia, Pennsylvania, Arizona) with **1,000 respondents per state** for more precise insights.
+
+- **Stratified Random Sampling**:
+  - Stratify by **age, gender, race/ethnicity, education, income, and region**.
+  - Ensure proportional representation based on **U.S. Census data** to avoid bias.
+
+- **Weighting Strategy**:
+  - Apply **post-stratification weighting** to adjust for any sampling imbalance, aligning with national demographics.
+
+---
+
+### **2. Recruitment Plan**
+
+- **Recruitment Channels**:
+  - Use **YouGov, Qualtrics**, and **MTurk** to access pre-screened online panels.
+  - Complement with **social media ads** on Facebook, Instagram, and LinkedIn to reach underrepresented groups.
+
+- **Incentives**:
+  - Offer **$10 gift cards** or entry into sweepstakes to increase participation and engagement.
+
+---
+
+### **3. Survey Implementation and Design**
+
+- **Survey Platform**: Google Forms  
+  - **Link**: *(Insert Google Forms survey link here)*  
+  - Accessible to respondents via **email, social media, and direct recruitment channels**.
+
+- **Survey Structure**:
+  1. **Demographics Section**: Age, gender, race/ethnicity, income, education, and state of residence.
+  2. **Voting Preferences Section**: Candidate choice, likelihood of voting, and party affiliation.
+  3. **Key Issues Section**: Identify priority issues (e.g., economy, healthcare, immigration).
+  4. **Thank You Message**:  
+     - *“Thank you for completing the survey! Your input is greatly appreciated and will help provide insights into the upcoming 2024 election.”*
+
+---
+
+### **4. Data Validation**
+
+- **Techniques for Data Quality**:
+  1. **Screening Questions**: Confirm eligibility (e.g., 18+ years old, registered voter status).
+  2. **Attention Checks**: Include a question like *“Please select ‘Agree’ for this item”* to verify respondents are attentive.
+  3. **IP Geolocation**: Validate state residency based on reported location.
+  4. **Duplicate Detection**: Identify and remove duplicate responses.
+
+---
+
+### **5. Poll Aggregation and Reporting**
+
+- **Poll Aggregation**:  
+  - Combine results with data from **YouGov, Marquette, and other reliable sources** for a robust forecast.
+  - Use **weighted averages** to account for differences in sample size and demographics.
+
+- **Margin of Error**:  
+  - **National Margin of Error**: ±1% at the 95% confidence level.  
+  - **State-Level Margins**: ±5-10% depending on the sample size for each state.
+
+---
+
+### **6. Budget Allocation**
+
+| **Expense**                     | **Estimated Cost**  |
+|----------------------------------|---------------------|
+| Panel Provider Fees              | $60,000             |
+| Participant Incentives           | $20,000             |
+| Social Media Advertising         | $10,000             |
+| Google Forms (Platform)          | Free                |
+| Data Validation & Analysis       | $8,000              |
+| Miscellaneous Expenses           | $2,000              |
+| **Total**                        | **$100,000**        |
+
+---
+
+## **Appendix B: Survey Questions**
+
+Below is the full content of the survey to be implemented using Google Forms:
+
+### **Survey Questions**
+
+#### **Section 1: Demographics**
+1. **What is your age?**  
+   - 18-24  
+   - 25-34  
+   - 35-44  
+   - 45-54  
+   - 55-64  
+   - 65+
+
+2. **What is your gender?**  
+   - Male  
+   - Female  
+   - Non-binary/Other
+
+3. **What is your race/ethnicity?** (Select all that apply)  
+   - White  
+   - Black or African American  
+   - Hispanic or Latino  
+   - Asian  
+   - Indigenous (Native American, Alaska Native, or First Nations)  
+   - Pacific Islander or Native Hawaiian  
+   - Other (please specify)
+
+4. **What is your household income?**  
+   - Less than $25,000  
+   - $25,000 - $49,999  
+   - $50,000 - $99,999  
+   - $100,000 or more
+
+5. **Which state do you currently reside in?**  
+   - (List all 50 states + Washington, D.C.)
+
+---
+
+#### **Section 2: Voting Preferences**
+6. **Are you a registered voter?**  
+   - Yes  
+   - No  
+   - Not sure
+
+7. **How likely are you to vote in the 2024 presidential election?**  
+   - Definitely will vote  
+   - Probably will vote  
+   - Probably will not vote  
+   - Definitely will not vote
+
+8. **If the 2024 election were held today, who would you vote for?**  
+   - Kamala Harris (Democrat)  
+   - Donald Trump (Republican)  
+   - Other (Please specify)  
+   - Undecided
+
+9. **How favorable are your opinions of the following candidates?**  
+   (Rate on a scale of 1 to 5)  
+   - Kamala Harris  
+   - Donald Trump  
+   - Any third-party candidates
+
+---
+
+#### **Section 3: Key Issues**
+10. **What is the most important issue for you in this election?**  
+   - Economy  
+   - Healthcare  
+   - Immigration  
+   - Climate change  
+   - Social Security and Medicare  
+   - Foreign policy
+
+11. **Which candidate do you think would handle the economy better?**  
+   - Kamala Harris  
+   - Donald Trump  
+   - Not sure
+
+---
+
+#### **Thank You Message**
+*“Thank you for completing the survey! Your input is greatly appreciated and will help provide insights into the upcoming 2024 election.”*
+
+---
+
+## **Appendix C: Google Forms Link**
+
+Once the survey is created, insert the **Google Forms link** here for participants to access.
+
+https://forms.gle/2MGYeZavDsCNuWZ1A
+
 # Model details {#sec-model-details}

### 2024-10-30 paper/paper.qmd
Updated figures

@@
 #| echo: false
+#| label: fig-multicol
 numeric_data <- data %>% 
@@
   )
+```
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-pct
+data %>% filter(candidate_name %in% c("Kamala Harris", "Donald Trump")) %>% 
+  mutate(end_date = as.Date(end_date, format = "%m/%d/%y")) %>% 
+  filter(end_date > as.Date("2024-01-01")) %>% 
+  ggplot(aes(x = end_date, y = pct, color = candidate_name, group = candidate_name)) +
+  geom_point(alpha = 0.2) +
+  geom_smooth() +
+  labs(
+    title = "Polling Percentage over Time by Candidate",
+    x = "End Date",
+    y = "Polling Percentage (%)",
+    color = "Candidate"
+  ) +
+  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
+  theme_minimal() +
+  scale_x_date(date_breaks = "3 months", date_labels = "%b %Y") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
 ```

### 2024-10-30 scripts/06-model_data.R

@@ -13,24 +13,22 @@ library(tidyverse)
 library(rstanarm)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+#analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
 
-### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
+data <- read_csv("data/01-raw_data/president_polls.csv")
+
+# Nevada: 6
+# Arizona: 11
+# Wisconsin: 10
+# Michegan: 15
+# Penn: 19
+# North Carolina: 16
+# Gerogia: 16
 
 
 #### Save model ####
 saveRDS(
-  first_model,
+  model,
   file = "models/first_model.rds"
 )
 

### 2024-10-30 paper/paper.qmd
Cleaned data and updated paper

--- 2024-10-22 paper/paper.qmd
@@
 By doing so, we enhance the reliability of our analysis, offering a more accurate estimation of how many votes each candidate might expect based on their average support levels while accounting for varying sample sizes across polls.
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-pct
+data %>% filter(candidate_name %in% c("Kamala Harris", "Donald Trump")) %>% 
+  mutate(end_date = as.Date(end_date, format = "%m/%d/%y")) %>% 
+  filter(end_date > as.Date("2024-01-01")) %>% 
+  ggplot(aes(x = end_date, y = pct, color = candidate_name, group = candidate_name)) +
+  geom_point(alpha = 0.2) +
+  geom_smooth() +
+  labs(
+    title = "Polling Percentage over Time by Candidate",
+    x = "End Date",
+    y = "Polling Percentage (%)",
+    color = "Candidate"
+  ) +
+  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
+  theme_minimal() +
+  scale_x_date(date_breaks = "3 months", date_labels = "%b %Y") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+```
 

### 2024-10-30 scripts/03-clean_data.R

@@ -27,26 +27,6 @@ data_a <- data_a %>%
 
 data$days_towards_election <- data_a$days_towards_election
 
-# TODO: mutate expected_vote
-filtered_data <- data %>%
-  group_by(question_id, poll_id) %>%
-  filter(any(candidate_name == "Kamala Harris") & any(candidate_name == "Donald Trump")) %>%
-  ungroup()
-
-average_pct <- filtered_data %>%
-  filter(candidate_name %in% c("Kamala Harris", "Donald Trump")) %>%
-  group_by(poll_id, candidate_name) %>%
-  summarise(avg_pct = mean(pct), .groups = 'drop')
-
-expected_votes <- average_pct %>%
-  left_join(filtered_data %>% 
-              select(poll_id, sample_size, days_towards_election) %>% 
-              distinct(), 
-            by = "poll_id") %>%
-  mutate(expected_vote = avg_pct * 0.01 * sample_size)
-
-
-
 # Select columns
 selected_columns <- c(
   "poll_id",

### 2024-10-30 scripts/06-model_data.R

@@ -15,7 +15,7 @@ library(rstanarm)
 #### Read data ####
 #analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
 
-data <- read_csv("data/01-raw_data/president_polls.csv")
+data <- read_csv("data/02-analysis_data/cleaned_president_polls.csv")
 
 # Nevada: 6
 # Arizona: 11
@@ -24,6 +24,16 @@ data <- read_csv("data/01-raw_data/president_polls.csv")
 # Penn: 19
 # North Carolina: 16
 # Gerogia: 16
+data_nevada <- data %>% filter(state == "Nevada") 
+data_arizona <- data %>% filter(state == "Arizona") 
+data_wisconsin <- data %>% filter(state == "Wisconsin") 
+data_michigan <- data %>% filter(state == "Michigan") 
+data_penn <- data %>% filter(state == "Pennsylvania") 
+data_north_carolina <- data %>% filter(state == "North Carolina") 
+data_georgia <- data %>% filter(state == "Georgia") 
+
+candidate_names <- c("Kamala Harris", "Donald Trump")
+
 
 
 #### Save model ####

### 2024-10-30 paper/paper.qmd
Update 14 preliminary models

@@
 #| warning: false
+data_nevada <- data %>% filter(state == "Nevada") 
+data_arizona <- data %>% filter(state == "Arizona") 
+data_wisconsin <- data %>% filter(state == "Wisconsin") 
+data_michigan <- data %>% filter(state == "Michigan") 
+data_penn <- data %>% filter(state == "Pennsylvania") 
+data_north_carolina <- data %>% filter(state == "North Carolina") 
+data_georgia <- data %>% filter(state == "Georgia")
+
 candidate_names <- c("Kamala Harris", "Donald Trump")
 
-# Define a function to fit the model and return the summary for each candidate
-fit_model <- function(candidate) {
-  candidate_data <- data %>%
-    filter(candidate_name == candidate)
+fit_model <- function(data, candidate) {
+  candidate_data <- data %>% filter(candidate_name == candidate)
 
-  model <- lm(pct ~ pollscore + transparency_score + sample_size + state + days_towards_election, data = candidate_data)
-
-  summary(model)
+  if (nrow(candidate_data) > 0) {  # Check if there are rows for the candidate
+    model <- lm(pct ~ days_towards_election, data = candidate_data)
+    tidy_model <- tidy(model)  # Get a tidy summary of the model
+    tidy_model$state <- unique(candidate_data$state)  # Add state to the output
+    tidy_model$candidate <- candidate  # Add candidate to the output
+    return(tidy_model)
+  } else {
+    return(NULL)  # Return NULL if no data for the candidate
+  }
 }
 
-# Apply the function to each distinct candidate name and store the summaries in a list
-model_summaries <- candidate_names %>%
-  set_names() %>%
-  map(fit_model)
+state_data_list <- list(
+  Nevada = data_nevada,
+  Arizona = data_arizona,
+  Wisconsin = data_wisconsin,
+  Michigan = data_michigan,
+  Pennsylvania = data_penn,
+  North_Carolina = data_north_carolina,
+  Georgia = data_georgia
+)
 
-# Print model summaries for each candidate
-model_summaries
+# Initialize an empty list to store results
+results <- list()
+
+# Loop through each candidate
+for (candidate in candidate_names) {
+  state_results <- list()  # Initialize an empty list for state results
+
+  # Loop through each state dataset
+  for (state_name in names(state_data_list)) {
+    state_data <- state_data_list[[state_name]]  # Get the state data
+    model_result <- fit_model(state_data, candidate)  # Fit the model
+    state_results[[state_name]] <- model_result  # Store the result
+  }
+
+  # Combine results for the current candidate into a single data frame
+  results[[candidate]] <- bind_rows(state_results)
+}
+
+# Combine results for all candidates into a single data frame
+final_results <- bind_rows(results, .id = "candidate")
+
+# View the final results
+print(final_results)
+
+```
+
+```{r}
+intercept_results <- final_results %>%
+  filter(term == "(Intercept)")
+
+# Spread the results into wide format
+intercept_wide <- intercept_results %>%
+  select(state, candidate, estimate) %>%
+  pivot_wider(names_from = candidate, values_from = estimate, values_fill = NA)
+
+# Calculate the difference in estimates between candidates
+intercept_wide <- intercept_wide %>%
+  mutate(difference = `Kamala Harris` - `Donald Trump`)
+
+# View the results with differences
+print(intercept_wide)
+```
+
+```{r}
+
 ```

### 2024-10-30 scripts/03-clean_data.R

@@ -58,6 +58,7 @@ selected_columns <- c(
   "party", 
   "answer", 
   "candidate_name", 
+  "days_towards_election",
   "pct"
 )
 data <- data %>% 
@@ -68,3 +69,4 @@ data <- data %>%
 
 #### Save data ####
 write_csv(data, "data/02-analysis_data/cleaned_president_polls.csv")
+

### 2024-10-31 paper/paper.qmd
Updated primary model formulation

@@
 library(dplyr)
+library(broom)
 ```
@@
 ## Model set-up
-```{r}
+
+```{r baseline model}
 #| echo: false
@@
 #| warning: false
-data_nevada <- data %>% filter(state == "Nevada") 
-data_arizona <- data %>% filter(state == "Arizona") 
-data_wisconsin <- data %>% filter(state == "Wisconsin") 
-data_michigan <- data %>% filter(state == "Michigan") 
-data_penn <- data %>% filter(state == "Pennsylvania") 
-data_north_carolina <- data %>% filter(state == "North Carolina") 
-data_georgia <- data %>% filter(state == "Georgia")
-
-candidate_names <- c("Kamala Harris", "Donald Trump")
-
 fit_model <- function(data, candidate) {
@@
 }
+
+# Candidate names
+candidate_names <- c("Kamala Harris", "Donald Trump")
+
+# Initialize an empty list to store results
+results <- list()
+
+# Loop over candidates and store each model's results
+for (candidate in candidate_names) {
+  model_result <- fit_model(data, candidate)  # Fit the model
+
+  # Check if the model_result is not NULL and add to the results list
+  if (!is.null(model_result)) {
+    results[[candidate]] <- model_result
+  }
+}
+
+# Combine results for all candidates into a single data frame
+final_results <- bind_rows(results, .id = "candidate")
+
+# View the final results
+print(final_results)
+
+```
+
+```{r our model}
+#| echo: false
+#| message: false
+#| warning: false
+data_nevada <- data %>% filter(state == "Nevada") 
+data_arizona <- data %>% filter(state == "Arizona") 
+data_wisconsin <- data %>% filter(state == "Wisconsin") 
+data_michigan <- data %>% filter(state == "Michigan") 
+data_penn <- data %>% filter(state == "Pennsylvania") 
+data_north_carolina <- data %>% filter(state == "North Carolina") 
+data_georgia <- data %>% filter(state == "Georgia")
 
@@
 ```{r}
+#| echo: false
+#| message: false
+#| warning: false
 intercept_results <- final_results %>%
@@
 ```{r}
+#| echo: false
+#| message: false
+#| warning: false
+solid_state_votes <- data.frame(
+  Candidate = c("Harris", "Trump"),
+  Solid_State_Votes = c(226, 219)
+)
+intercept_wide$electoral_votes <- c(6, 11, 10, 15, 19, 16, 16)
 
+swing_state_results <- intercept_wide %>%
+  mutate(Winner = ifelse(difference > 0, "Harris", "Trump")) %>%
+  group_by(Winner) %>%
+  summarize(Predicted_Swing_State_Votes = sum(electoral_votes))
+
+total_votes <- solid_state_votes %>%
+  left_join(swing_state_results, by = c("Candidate" = "Winner")) %>%
+  mutate(Predicted_Swing_State_Votes = ifelse(is.na(Predicted_Swing_State_Votes), 0, Predicted_Swing_State_Votes),
+         Total_Predicted_Votes = Solid_State_Votes + Predicted_Swing_State_Votes)
+
+kable(total_votes, caption = "Predicted Electoral Votes for Each Candidate")
 ```
 
-The linear regression model is specified for each candidate separately, with the following structure:
+### Model Formulations
 
-\begin{align}
-\text{pct}_i & = \beta_0 + \beta_1 \text{pollscore}_i + \beta_2 \text{transparency\_score}_i + \beta_3 \text{sample\_size}_i + \beta_4 \text{state}_i + \beta_5 \text{days\_towards\_election}_i + \epsilon_i \\
-\epsilon_i & \sim \text{Normal}(0, \sigma^2)
-\end{align}
+#### 1. Baseline Model (Winner-Take-All National Model)
+The baseline model aggregates national polling data to predict a winner, with all electoral votes awarded to the candidate with the higher national polling percentage.
 
-Where:
-\begin{align}
-\beta_0 & \text{ is the intercept term} \\
-\beta_1, \beta_2, \beta_3, \beta_4, \beta_5 & \text{ are the coefficients for each predictor} \\
-\sigma^2 & \text{ is the variance of the error term}
-\end{align}
+1. **National Polling Projections**  
+   Let:
+   - $P_H(t)$: Harris’s national polling percentage at $t$ days towards the election.
+   - $P_T(t)$: Trump’s national polling percentage at $t$ days towards the election.
 
-In the implementation, a function is defined to fit this model for each candidate (Kamala Harris and Donald Trump) individually.
-The model fits are then summarized to interpret the coefficients for each predictor.
+   We model each candidate’s polling as:
+   $$
+   P_H(t) = \alpha_H + \beta_H t
+   $$
+   $$
+   P_T(t) = \alpha_T + \beta_T t
+   $$
+
+   where $\alpha_H$ and $\alpha_T$ are the intercepts (predicted percentages on election day, $t = 0$), and $\beta_H$ and $\beta_T$ are the slopes.
+
+2. **Election Day Prediction**  
+   On election day:
+   $$
+   P_H(0) = \alpha_H, \quad P_T(0) = \alpha_T
+   $$
+
+3. **Winner-Take-All Outcome**  
+   The candidate with the higher predicted national percentage wins all electoral votes:
+   $$
+   W = 
+   \begin{cases} 
+   \text{Harris wins (all electoral votes)} & \text{if } \alpha_H > \alpha_T \\
+   \text{Trump wins (all electoral votes)} & \text{otherwise}
+   \end{cases}
+   $$
+
+#### 2. Primary Model (Swing State-Based Model)
+This model forecasts electoral outcomes by projecting state-level polling results for each candidate, combining swing state outcomes with votes from solid states.
+
+1. **Swing State Polling Projections**  
+   For each swing state $s \in S$, let:
+   - $P_{H_s}(t)$: Harris’s polling percentage in state $s$ at $t$ days before the election.
+   - $P_{T_s}(t)$: Trump’s polling percentage in state $s$ at $t$ days before the election.
+
+   We model each swing state polling as:
+   $$
+   P_{H_s}(t) = \alpha_{H_s} + \beta_{H_s} t
+   $$
+   $$
+   P_{T_s}(t) = \alpha_{T_s} + \beta_{T_s} t
+   $$
+
+   where $\alpha_{H_s}$ and $\alpha_{T_s}$ are intercepts (predicted percentages at $t = 0$) and $\beta_{H_s}$, $\beta_{T_s}$ are slopes.
+
+2. **Predicting Swing State Winners**  
+   On election day ($t = 0$), each candidate’s predicted support in state $s$is:
+   $$
+   P_{H_s}(0) = \alpha_{H_s}, \quad P_{T_s}(0) = \alpha_{T_s}
+   $$
+
+   Define $W_s$ as an indicator for the swing state winner:
+   $$
+   W_s = 
+   \begin{cases} 
+   1 & \text{if } \alpha_{H_s} > \alpha_{T_s} \\
+   0 & \text{otherwise}
+   \end{cases}
+   $$
+
+3. **Electoral Vote Aggregation**  
+   Let $EV_H$ and $EV_T$ represent total electoral votes for Harris and Trump:
+   $$
+   EV_H = \sum_{s \in S} W_s \cdot EV_s + \sum_{s \in S_H} EV_s
+   $$
+   $$
+   EV_T = \sum_{s \in S} (1 - W_s) \cdot EV_s + \sum_{s \in S_T} EV_s
+   $$
+
+4. **Final Election Outcome**  
+   The candidate surpassing 270 electoral votes wins:
+   $$
+   W = 
+   \begin{cases} 
+   \text{Harris wins} & \text{if } EV_H \geq 270 \\
+   \text{Trump wins} & \text{if } EV_T \geq 270 
+   \end{cases}
+   $$
 

### 2024-10-31 paper/paper.qmd

@@
     tidy_model <- tidy(model)  # Get a tidy summary of the model
-    tidy_model$state <- unique(candidate_data$state)  # Add state to the output
     tidy_model$candidate <- candidate  # Add candidate to the output
@@
 # View the final results
-print(final_results)
+kable(final_results)
 
@@
 data_georgia <- data %>% filter(state == "Georgia")
+
+fit_model <- function(data, candidate) {
+  candidate_data <- data %>% filter(candidate_name == candidate)
+
+  if (nrow(candidate_data) > 0) {  # Check if there are rows for the candidate
+    model <- lm(pct ~ days_towards_election, data = candidate_data)
+    tidy_model <- tidy(model)  # Get a tidy summary of the model
+    tidy_model$state <- unique(candidate_data$state)  # Add state to the output
+    tidy_model$candidate <- candidate  # Add candidate to the output
+    return(tidy_model)
+  } else {
+    return(NULL)  # Return NULL if no data for the candidate
+  }
+}
 
@@
 # View the results with differences
-print(intercept_wide)
+kable(intercept_wide)
 ```

### 2024-10-31 paper/paper.qmd
Updated appendices in the paper

@@
 
-YouGov is a global public opinion and data company that conducts online surveys on a variety of topics, including politics, social issues, and consumer behavior.
-Founded in 2000, YouGov is known for leveraging technology to conduct large-scale online surveys, combining traditional sampling principles with advanced data analytics to measure public opinion efficiently.
+YouGov is a widely recognized survey and market research company that operates one of the largest global online panels, providing insights on public opinion across various topics, from politics to consumer behavior.
+As an online survey platform, YouGov employs a nonprobability sampling methodology, relying on a self-recruited panel and extensive demographic data to approximate representativeness.
+This methodology offers several advantages, including cost-efficiency, rapid data collection, and the ability to adapt to specific research needs.
+However, like all methodologies, it comes with its own set of trade-offs, particularly in terms of representativeness and potential selection biases.
+
+This appendix takes a closer look at YouGov’s sampling approach, panel recruitment methods, handling of non-response, and overall survey methodology.
+It also includes a reflection on the user experience, examining how elements like the onboarding process and incentive structure can shape participant engagement and data quality.
+By analyzing the strengths and weaknesses of YouGov’s approach, this paper aims to provide a comprehensive understanding of how YouGov balances methodological rigor with the practical realities of online polling, highlighting both the reliability and the limitations of its data.
 
@@
 
-- **Population**: The population refers to the group of individuals whose opinions YouGov aims to measure.
-For political surveys, this often includes eligible voters in a specific country (e.g., registered U.S.
-voters).
-Other surveys may focus on specific demographic groups, such as young adults or industry professionals.
+For YouGov surveys, the population often includes U.S.
+adults or specific subgroups, such as registered voters or other demographic or political segments.
+The frame from which YouGov draws its samples is its proprietary online panel, consisting of self-recruited individuals who provide extensive demographic information upon joining.
+This frame is nonprobabilistic and is designed to capture a wide demographic, with adjustments to enhance representativeness through post-survey weighting (YouGov).
 
-- **Frame**: The frame is a list from which the sample is drawn.
-YouGov uses its online panel, consisting of millions of registered users worldwide.
-For specific surveys, the frame is the subset of panel members matching desired criteria (e.g., age, location).
-
-- **Sample**: The sample is a subset of the population selected to participate in a survey.
-Political surveys often involve 1,000-3,000 respondents, weighted to match the demographic characteristics of the broader population.
+The sample is selected from this online panel based on survey requirements.
+For general surveys representing the U.S.
+adult population, YouGov applies demographic matching and stratified sampling to recruit individuals whose characteristics resemble the target population.
+For more targeted surveys, such as those involving younger adults or specific voter segments, YouGov filters panelists based on demographic and political characteristics, ensuring that the survey sample aligns with the study's focus (YouGov).
 
@@
 
-- **Recruitment Process**: YouGov recruits panel members via online advertisements, partnerships, and social media.
-Individuals join the panel by registering on the YouGov website and completing a demographic profile.
+YouGov’s panelists are recruited through online advertisements, partnerships with various websites, and organic sign-ups.
+This open online recruitment allows any adult within the United States with internet access to join the panel, promoting inclusivity in terms of access and accessibility (YouGov).
+Once part of the panel, participants voluntarily complete surveys for points that can be exchanged for rewards, making monetary compensation a moderate incentive but not the sole motivator for participation.
+This approach is well-suited to engage a broad and diverse sample, although it does introduce limitations by excluding those without internet access.
 
-- **Incentives**: Panel members earn rewards through a points-based system, which can be redeemed for cash, gift cards, or other benefits.
+Because the recruitment is continuous and participants often stay on the panel long-term, YouGov can maintain and monitor demographic balance, update panelist information over time, and reduce redundancy in questions for returning members.
+However, relying solely on online recruitment may introduce a bias toward individuals more inclined toward online engagement, who may not fully represent groups with lower internet usage, such as older adults or those from lower-income backgrounds (YouGov).
 
@@
 
-- **Sampling Method**: YouGov employs a non-probability sampling approach using quota sampling combined with statistical weighting.
-Respondents are selected to fill quotas based on demographics (age, gender, education, region) that align with the population.
+YouGov employs a nonprobability sampling approach, meaning that not every individual in the population has an equal chance of selection.
+Within its panel, YouGov uses stratified sampling, drawing subsets of respondents based on demographic targets (e.g., age, race, gender, and region) to match the sample as closely as possible to the desired population structure.
 
-- **Advantages of Quota Sampling**:
-  - **Cost-effective**: Less expensive than random sampling due to online recruitment and automation.
-  - **Speed**: Enables quick data collection, crucial for tracking fast-changing opinions.
-  - **Targeted Sampling**: Can focus on hard-to-reach populations or specific demographics.
-
-- **Limitations of Quota Sampling**:
-  - **Selection Bias**: Self-selection into the panel may introduce biases, as panel members might differ from the general population (e.g., more engaged online).
-  - **Generalizability Issues**: Weighting may not fully adjust for attitudinal differences between panelists and the public.
+### Trade-offs of the Nonprobability Approach
+- **Strengths**: Nonprobability sampling allows YouGov to gather data rapidly and cost-effectively.
+By using stratified sampling and post-survey weighting, the company aims to approximate the representativeness of probability-based samples while maintaining flexibility in addressing specific research goals and client needs (YouGov).
+- **Limitations**: Because nonprobability samples lack random selection, they do not guarantee true representativeness, which can introduce unknown biases.
+YouGov addresses this partially by applying demographic weights, but nonprobability sampling’s inherent limitations mean results should be interpreted as estimates rather than fully precise reflections of the target population (Huffington Post).
 
@@
 
-- **Mitigation Strategies**: YouGov reduces non-response bias with flexible survey completion times and reminder emails.
-Statistical weighting adjusts for demographic discrepancies caused by non-response.
+Non-response is a common issue in survey research, particularly with online surveys where participants may decline to participate, partially complete surveys, or provide inconsistent answers.
+YouGov tackles non-response bias through quality control processes that exclude unreliable responses.
+These controls involve detecting respondents who complete surveys too quickly, answer inconsistently, or fail attention checks (YouGov).
 
-- **Weighting**: Survey data are weighted to match demographic distributions (e.g., age, gender, race, education). Additional adjustments may be made for political affiliation or past voting behavior.
+In addition, YouGov adjusts for non-response by weighting the final sample to reflect the target population's demographic characteristics more accurately.
+This adjustment helps address imbalances resulting from non-response, enhancing the data’s generalizability.
+However, non-response bias remains a concern, especially as weighting cannot entirely account for individuals not present in the sample or for differences in survey engagement across demographics (YouGov).
 
-## Questionnaire Design
+## Strengths and Weaknesses of YouGov’s Methodology
 
-- **Strengths**:
-  - **Clarity**: Questions are straightforward and easy to understand, reducing measurement error.
-  - **Consistency**: Surveys follow a standardized format, ensuring consistency over time, important for tracking changes in opinion.
+### Strengths
+- **Efficient Data Collection**: YouGov’s nonprobability online sampling allows for efficient, cost-effective data collection, enabling timely survey responses that can address rapidly changing social and political topics.
+- **Targeted Panel Management**: YouGov’s proprietary panel enables consistent, direct contact with respondents, allowing for long-term engagement and improved tracking of demographic and opinion changes without needing repetitive data entry.
+- **Rigorous Quality Controls**: Extensive quality checks, including IP verification, email authentication, and response validity checks, help YouGov maintain high data integrity.
+Respondents who fail quality checks are excluded, helping to reduce noise from unreliable data.
+- **Adjustments for Representativeness**: While nonprobability sampling has limitations, YouGov partially mitigates these by applying sophisticated weighting based on benchmarks from sources like the U.S.
+Census.
+This enhances the sample’s demographic alignment with the general population (YouGov).
 
-- **Weaknesses**:
-  - **Limited Depth**: Online surveys may feature shorter questionnaires to avoid fatigue, limiting topic depth.
-  - **Response Options**: The design of response options (e.g., including "Don't Know") can influence results, potentially leading to different conclusions.
+### Weaknesses
+- **Nonprobability Sampling Limitations**: The lack of true random sampling introduces potential bias, as certain population segments may be underrepresented.
+For example, people without internet access or those less inclined toward online engagement are systematically excluded, which could affect representativeness.
+- **Potential Selection Bias**: Although incentives are modest, they may still attract individuals who are already more engaged or motivated to participate in surveys, which could influence results.
+The weighting procedures help but may not fully eliminate biases if certain groups are consistently underrepresented.
+- **Limitations of Online-Only Surveys**: Although internet penetration in the U.S.
+is high, reliance on online-only surveys may still leave out individuals less comfortable with or able to access online technology, skewing results slightly.
+- **Questionnaire Design Constraints**: While YouGov’s questionnaire design is generally sound, with randomized question orders and multimedia inclusion for clarity, online surveys can limit response depth compared to in-person or phone surveys.
+Responses are constrained by pre-set answer options, potentially oversimplifying complex views and reducing respondent nuance (Huffington Post).
 
-## Evaluation of YouGov's Methodology
+## Reflection
 
-YouGov's methodology provides several strengths, such as cost, speed, and accessibility, making it suitable for political polling and market research.
-Online panels enable rapid data collection and targeted sampling.
-However, the reliance on non-probability sampling introduces biases.
-While weighting can mitigate some issues, it may not fully compensate for differences between panelists and the general population.
+We created an account on YouGov to gain real experience with the platform, as illustrated in @fig-YouGovWelcomePage and here is my reflection on the onboarding process and user experience.
 
-- **Strengths**:
-  - **Efficient**: Cost-effective and quick data collection.
-  - **Adaptable**: Can rapidly capture opinions on evolving issues.
-  - **Targeted**: Capable of reaching niche demographics or regions.
+![YouGov Welcome Page](../other/photos/YouGov_Welcome_Page.png){#fig-YouGovWelcomePage width=60%}
 
-- **Weaknesses**:
-  - **Selection Bias**: Potential biases due to non-probability sampling.
-  - **Non-Response Bias**: Some groups may be less likely to participate.
-  - **Questionnaire Limitations**: Less depth compared to other survey methods.
+The YouGov survey onboarding process is designed to be clear and straightforward, making it easy for new users to sign up and begin participating.
+The questions asked during onboarding are simple and direct, covering basic demographic details without overwhelming the participant.
+The first question of the first survey we took at YouGov is shown at @fig-YouGovSurvey.
+This streamlined approach likely helps increase engagement and reduces drop-off rates, ensuring that users can quickly understand what is required of them.
+The layout and visuals are accessible, contributing to a positive first impression and making it more likely that new panelists will continue engaging with future surveys.
 
-Overall, YouGov’s approach satisfies many standards for modern survey research. Although it has limitations, the insights gained are valuable when these are taken into account.
+![YouGov Survey](../other/photos/YouGov_Survey.png){#fig-YouGovSurvey width=60%}
 
-# Methodology and Survey Design for 2024 U.S. Presidential Election Forecast**
+To enhance data integrity, YouGov includes verification steps such as confirming users’ email addresses through a code.
+This extra step not only ensures that participants are real and unique individuals but also helps prevent fraudulent or duplicate accounts, as shown in @fig-YouGovEmailVerification, which can otherwise skew survey results.
+By verifying email addresses, YouGov can maintain a higher quality of data and build a more reliable panel, knowing that each participant is committed enough to complete these security measures.
+This verification process is a straightforward yet effective method for improving data quality from the outset.
+
+![YouGov Email Verification](../other/photos/YouGov_Email_Verification.png){#fig-YouGovEmailVerification width=60%}
+
+Data privacy is also well-considered in YouGov’s onboarding, with clear options allowing users to control how their information is shared.
+For instance, participants can opt in or out of having their responses shared in identifiable formats with trusted third parties.
+@fig-YouGovDataPrivacy includes an example of how YouGov is letting users to control their information privacy.
+This transparency around data usage builds trust, showing participants that their privacy is valued and that they have agency over their data.
+The option to decide on data sharing likely encourages long-term participation, as users are reassured that their information will be handled responsibly.
+
+![YouGov Data Privacy](../other/photos/YouGov_Data_Privacy.png){#fig-YouGovDataPrivacy width=60%}
+
+However, the onboarding interface in @fig-YouGovInterface has a gamified feel, awarding points for each step completed.
+This reward system, while motivating, could encourage participants to treat the surveys more like a task for monetary gain than an opportunity to provide genuine responses.
+The point-based incentive structure may attract users who are primarily interested in earning rewards, which risks impacting data quality if participants prioritize speed over thoughtful answers.
+This setup introduces the possibility that some users are engaging more for the rewards than for contributing to research, which could affect the reliability of the responses YouGov collects.
+
+![YouGov Interface](../other/photos/YouGov_Interface.png){#fig-YouGovInterface width=60%}
+
+# Methodology and Survey Design for 2024 U.S. Presidential Election Forecast
 
 ## Methodology
-
-This section details the **idealized methodology** used to conduct a national survey to forecast the 2024 U.S.
+This part of the appendix provides a detailed methodology and survey design to forecast the 2024 U.S.
 presidential election.
-The methodology includes **sampling strategies, recruitment methods, data validation techniques, and poll aggregation** procedures.
+Our survey focuses on swing states: Arizona, Georgia, Michigan, Nevada, North Carolina, Pennsylvania, and Wisconsin due to the results of other states being certain.
+The survey targets different age groups using tailored recruitment strategies.
+Below, we break down the methodology, budget, recruitment strategies, and survey design to ensure representative participation.
 
 ### Sampling Approach
+- Total Sample Size: 7,000 respondents (1,000 participants per state).
+- Target Population: Eligible voters from the following swing states: Arizona, Georgia, Michigan, Nevada, North Carolina, Pennsylvania, Wisconsin.
 
-- **Total Sample Size**: 10,000 respondents
-- **Distribution by State**:
-  - **Minimum 100 respondents per state** (including Washington, D.C.) to ensure balanced regional representation.
-  - **Oversampling in battleground states** (e.g., Georgia, Pennsylvania, Arizona) with **1,000 respondents per state** for more precise insights.
+#### Sampling Breakdown by Age Group:
+- 18-24 years: 150 participants per state (total 1,050) – reached through university students.
+- 25-60 years: 700 participants across states (total 4,900) – reached via online ads and survey platforms.
+- 60+ years: 150 participants per state (total 1,050) – reached through phone calls.
 
-- **Stratified Random Sampling**:
-  - Stratify by **age, gender, race/ethnicity, education, income, and region**.
+- Stratified Random Sampling:
+  - Stratify by age, gender, race/ethnicity, education, income, and region.
   - Ensure proportional representation based on **U.S. Census data** to avoid bias.
 
-- **Weighting Strategy**:
+- Weighting Strategy:
   - Apply **post-stratification weighting** to adjust for any sampling imbalance, aligning with national demographics.
@@
 
-- **Recruitment Channels**:
-  - Use **YouGov, Qualtrics**, and **MTurk** to access pre-screened online panels.
+#### 18-24 Years (University Students):
+- University Collaboration: Partner with academic institutions in each swing state to send survey invitations via email on behalf of the project.
+- Rationale: Universities provide direct access to students, improving recruitment efficiency and response rates.
+- Incentive: Each respondent receives a $10 e-gift card for a Walmart or Costco purchase.
+
+#### 25-60 Years (General Population):
+- Online Ads and Survey Platforms: Use Facebook, Instagram, and platforms like Prolific to recruit participants from swing states.
+- Budget Allocation: Allocate $10,000 for online ads to reach residents aged 25-60.
+- Incentive: Participants receive e-gift cards upon survey completion.
+
+#### 60+ Years (Senior Citizens):
+- Phone Surveys: Conduct live calls to reach seniors, considering that older people are not comfortable using electronic devices.
+Phone numbers will be sourced from voter registration databases (where legally accessible) or senior community networks.
+- Incentive: Seniors can choose a physical Walmart or Costco gift card, which will be sent by mail.
+
+- Recruitment Channels:
   - Complement with **social media ads** on Facebook, Instagram, and LinkedIn to reach underrepresented groups.
+  - **Incentives**: Offer **$10 gift cards** to increase participation and engagement.
 
-- **Incentives**:
-  - Offer **$10 gift cards** or entry into sweepstakes to increase participation and engagement.
+### Trade-off
+
+#### Data Representativeness vs. Control over Data Collection
+- Issue: Although age quotas ensure participation from different age groups (18-24, 25-60, 60+), it is not feasible to set strict limits for race and income.
+Without perfectly matched samples for race and income, bias may arise in the survey results.
+
+- Solution: 
+  - Weighting Strategy: Calculate population proportions for race and income within each state using Census data. Assign weights to groups based on their representation to mitigate bias.
+
+#### Efficient Recruitment vs. Potential Selection Bias
+- Issue: Limiting the 18-24 age group to university students may introduce selection bias.
+University students often differ from their non-student peers in socioeconomic background and possibly political perspectives.
+- Impact: This selection bias may affect the generalizability of findings, as university students’ perspectives might differ from all young adults.
+
+#### Effective Senior Outreach vs. Higher Costs and Response Bias
+- Issue: Using live phone operators to reach seniors increases costs, and some seniors may remain unreachable by phone.
+- Impact: Higher costs may reduce resources for other age groups. Response bias may arise if unreachable seniors have different views, affecting the survey's representativeness.
+
+#### Incentivizing Participation vs. Economic Bias in Sample
+- Issue: Offering $10 gift cards as an incentive could attract participants more likely to need the incentive, potentially introducing economic bias.
+- Impact: Overrepresentation of lower-income participants could skew results, affecting insights if income level correlates with political perspectives.
 
 ### Survey Implementation and Design
+In designing this survey, I referenced insights from the article on survey methods from @AnnualReviewofEconomics, particularly on the advantages of online surveys over in-person, phone, or mail surveys.
+The article highlighted that online surveys provide flexibility, allowing respondents to complete them at their convenience, which minimizes selection bias related to work schedules or availability.
+This flexibility is especially beneficial for students and working-age individuals, who may find it challenging to respond during traditional hours.
+The article also emphasized how mobile technology can increase participation by reaching populations that are otherwise hard to engage, such as younger respondents, frequent movers, or those in remote areas.
+In line with these insights, I designed this survey with an online format for younger and working-age participants, maximizing accessibility and reducing drop-out rates.
+Additionally, I applied the article’s suggestion of keeping surveys concise to prevent fatigue and disengagement, which helps maintain completion rates and improve data quality.
+The use of digital incentives, as noted in the article, also broadens the appeal and ensures we reach a diverse participant base across income levels, providing flexibility in rewards to cater to different motivations.
+This approach helped shape a balanced methodology that optimizes participation across demographic groups and aligns with best practices in survey design.
 
-- **Survey Platform**: Google Forms  
-  - **Link**: *(Insert Google Forms survey link here)*  
+- Survey Platform: Google Forms  
+  - **Link**: [https://forms.gle/2MGYeZavDsCNuWZ1A](https://forms.gle/2MGYeZavDsCNuWZ1A)
   - Accessible to respondents via **email, social media, and direct recruitment channels**.
 
-- **Survey Structure**:
-  1. **Demographics Section**: Age, gender, race/ethnicity, income, education, and state of residence.
-  2. **Voting Preferences Section**: Candidate choice, likelihood of voting, and party affiliation.
-  3. **Key Issues Section**: Identify priority issues (e.g., economy, healthcare, immigration).
-  4. **Thank You Message**:  
+- Survey Structure:
+  1. Demographics Section: Age, gender, race/ethnicity, income, education, and state of residence.
+  2. Voting Preferences Section: Candidate choice, likelihood of voting, and party affiliation.
+  3. Key Issues Section: Identify priority issues (e.g., economy, healthcare, immigration).
+  4. Thank You Message:  
      - *“Thank you for completing the survey! Your input is greatly appreciated and will help provide insights into the upcoming 2024 election.”*
@@
 
-- **Techniques for Data Quality**:
-  1. **Screening Questions**: Confirm eligibility (e.g., 18+ years old, registered voter status).
-  2. **Attention Checks**: Include a question like *“Please select ‘Agree’ for this item”* to verify respondents are attentive.
-  3. **IP Geolocation**: Validate state residency based on reported location.
-  4. **Duplicate Detection**: Identify and remove duplicate responses.
+- Techniques for Data Quality:
+  1. Screening Questions: Confirm eligibility (e.g., 18+ years old, registered voter status).
+  2. Attention Checks: Include a question like *“Please select ‘Agree’ for this item”* to verify respondents are attentive.
+  3. IP Geolocation: Validate state residency based on reported location.
+  4. Duplicate Detection: Identify and remove duplicate responses.
 
@@
 
-- **Poll Aggregation**:  
-  - Combine results with data from **YouGov, Marquette, and other reliable sources** for a robust forecast.
+- Poll Aggregation:  
   - Use **weighted averages** to account for differences in sample size and demographics.
 
-- **Margin of Error**:  
-  - **National Margin of Error**: ±1% at the 95% confidence level.  
-  - **State-Level Margins**: ±5-10% depending on the sample size for each state.
+- Margin of Error**:  
+  - National Margin of Error: ±1% at the 95% confidence level.  
+  - State-Level Margins: ±5-10% depending on the sample size for each state.
 
@@
 | **Expense**                                        | **Estimated Cost**  |
-|----------------------------------|---------------------|
-| Panel Provider Fees              | $60,000             |
-| Participant Incentives           | $20,000             |
-| Social Media Advertising         | $10,000             |
+|---------------------------------------------------|---------------------|
+| Participant Incentives                             | $70,000            |
+| Online Ads and Panel Provider Fees                 | $10,000            |
+| Phone Survey Salaries                              | $8,000             |
 | Google Forms (Platform)                            | Free               |
-| Data Validation & Analysis       | $8,000              |
+| Data Validation & Analysis                         | $10,000            |
 | Miscellaneous Expenses                             | $2,000             |
@@
 
-### Section 1: Demographics
-1. **What is your age?**  
+1. What is your age?  
    - 18-24  
-   - 25-34  
-   - 35-44  
-   - 45-54  
-   - 55-64  
-   - 65+
+   - 25-39  
+   - 40-60  
+   - 60+
 
-2. **What is your gender?**  
+2. What is your gender?  
    - Male  
    - Female  
-   - Non-binary/Other
+   - Other: ___
 
-3. **What is your race/ethnicity?** (Select all that apply)  
+3. What is your race/ethnicity?  
    - White  
-   - Black or African American  
+   - Black  
    - Hispanic or Latino  
    - Asian  
-   - Indigenous (Native American, Alaska Native, or First Nations)  
-   - Pacific Islander or Native Hawaiian  
-   - Other (please specify)
+   - Indigenous  
+   - Other: ___
 
-4. **What is your household income?**  
+4. What is your highest level of education?  
+   - Less than high school  
+   - High school diploma  
+   - Some college  
+   - Bachelor’s degree  
+   - Graduate degree or higher
+
+5. What is your annual household income?  
    - Less than $25,000  
@@
 
-5. **Which state do you currently reside in?**  
-   - (List all 50 states + Washington, D.C.)
+6. Which state do you currently reside in?
 
-### Section 2: Voting Preferences
-6. **Are you a registered voter?**  
+7. Are you a registered voter?  
    - Yes  
@@
 
-7. **How likely are you to vote in the 2024 presidential election?**  
-   - Definitely will vote  
-   - Probably will vote  
-   - Probably will not vote  
-   - Definitely will not vote
+8. How likely are you to vote in the 2024 presidential election?  
+   - 1 (Definitely will not vote)  
+   - 2  
+   - 3  
+   - 4  
+   - 5 (Definitely will vote)
 
-8. **If the 2024 election were held today, who would you vote for?**  
+9. If the 2024 election were held today, who would you vote for?  
    - Kamala Harris (Democrat)  
    - Donald Trump (Republican)  
-   - Other (Please specify)  
    - Undecided  
+   - Other: ___
 
-9. **How favorable are your opinions of the following candidates?**  
-   (Rate on a scale of 1 to 5)  
-   - Kamala Harris  
-   - Donald Trump  
-   - Any third-party candidates
-
-### Key Issues
-10. **What is the most important issue for you in this election?**  
-   - Economy  
+10. What is the most important issue for you in this election?  
+   - The economy  
    - Healthcare  
@@
 
-11. **Which candidate do you think would handle the economy better?**  
-   - Kamala Harris  
-   - Donald Trump  
-   - Not sure
+11. In your opinion, how will the majority in your state vote in 2024?  
+   - Democrat  
+   - Republican  
+   - Too close to predict
 
-### Thank You Message
-*“Thank you for completing the survey! Your input is greatly appreciated and will help provide insights into the upcoming 2024 election.”*
+12. Do you have any additional comments or suggestions?
+
+Thank you for completing the survey! Your input is greatly appreciated and will help provide insights into the upcoming 2024 election.
 
 ## Google Forms Link
-
-Once the survey is created, insert the **Google Forms link** here for participants to access.
-
-https://forms.gle/2MGYeZavDsCNuWZ1A
+[https://forms.gle/2MGYeZavDsCNuWZ1A](https://forms.gle/2MGYeZavDsCNuWZ1A)
 

### 2024-10-31 paper/paper.qmd
Updated title

@@
 ---
-title: "Forecasting the 2024 US Presidential Election: A Poll-Based Approach"
-subtitle: "My subtitle if needed"
+title: "Forecasting the 2024 U.S. Presidential Election: A Poll-Based Approach"
+subtitle: "Kamala Harris Poised for Victory"
 author: 
@@
   - Ariel Xing
-  - John Zhang
+  - John Zhang^[The authors are listed in alphabetical order by last name.]
 thanks: "Code and data are available at: [https://github.com/xgao28/election_forecast](https://github.com/xgao28/election_forecast)."

### 2024-10-31 scripts/01-simulate_data.R
Added script to simulate data and ordered scripts

@@ -1,0 +1,67 @@
+# Purpose: Simulates the data similar to the expected dataset. 
+# Author: Xinxiang Gao
+# Date: 31 October 2024
+# Contact: xinxiang.gao@mail.utoronto.ca
+# License: MIT
+
+# Load necessary libraries
+library(tidyverse)
+library(lubridate)
+
+# Set a seed for reproducibility
+set.seed(690)
+
+num_rows <- 1000  # Total number of events to simulate
+
+
+states <- c("Alabama", "Alaska", "Arizona", "Arkansas", "California", "Colorado", 
+            "Connecticut", "Delaware", "Florida", "Georgia", "Hawaii", "Idaho", 
+            "Illinois", "Indiana", "Iowa", "Kansas", "Kentucky", "Louisiana", 
+            "Maine", "Maryland", "Massachusetts", "Michigan", "Minnesota", 
+            "Mississippi", "Missouri", "Montana", "Nebraska", "Nevada", "New Hampshire", 
+            "New Jersey", "New Mexico", "New York", "North Carolina", "North Dakota", 
+            "Ohio", "Oklahoma", "Oregon", "Pennsylvania", "Rhode Island", 
+            "South Carolina", "South Dakota", "Tennessee", "Texas", "Utah", 
+            "Vermont", "Virginia", "Washington", "West Virginia", "Wisconsin", "Wyoming")
+
+candidate_names <- c("Kamala Harris", "Donald Trump", "Joe Biden", "Bernie Sanders", "Elizabeth Ann Warren")
+transparency_scores <- seq(0, 10, 0.5)
+poll_ids <- 74681:89106
+dates <- seq(as.Date("2021-04-07"), as.Date("2024-10-31"), by="month")
+
+# Function to create a single poll entry with a random subset of candidates
+create_poll <- function(poll_id, state, date, transparency_score) {
+  # Randomly select 2 to 5 candidates
+  num_candidates <- sample(2:5, 1)
+  selected_candidates <- sample(candidate_names, num_candidates)
+  
+  # Generate random percentages for the selected candidates, normalized to sum to 1
+  pct <- runif(num_candidates)
+  pct <- round(pct / sum(pct) * 100, 2)
+  
+  # Create a data frame for each poll
+  data.frame(
+    poll_id = poll_id,
+    state = state,
+    end_date = date,
+    transparency_score = transparency_score,
+    candidate_name = selected_candidates,
+    pct = pct
+  )
+}
+
[…]

### 2024-10-31 scripts/03-test_analysis_data.R

@@ -1,0 +1,95 @@
+# Purpose: Tests the simulated data and the analysis data. 
+# Author: Xinxiang Gao
+# Date: 31 October 2024
+# Contact: xinxiang.gao@mail.utoronto.ca
+# License: MIT
+
+
+#### Workspace setup ####
+library(tidyverse)
+library(testthat)
+
+data <- read_csv("data/00-simulated_data/simulated_polls.csv")
+
+
+#### Test simulated data ####
+
+# Test that 'poll_id' is integer type
+test_that("'poll_id' is integer", {
+  expect_type(data$poll_id, "integer")
+})
+
+# Test that 'state' column is character type
+test_that("'state' is character", {
+  expect_type(data$state, "character")
+})
+
+# Test that 'end_date' column is Date type
+test_that("'end_date' is Date", {
+  expect_true(all(class(data$end_date) == "Date"))
+})
+
+# Test that 'transparency_score' is numeric type
+test_that("'transparency_score' is numeric", {
+  expect_type(data$transparency_score, "double")
+})
+
+# Test that 'candidate_name' column is character type
+test_that("'candidate_name' is character", {
+  expect_type(data$candidate_name, "character")
+})
+
+# Test that 'pct' column is numeric type
+test_that("'pct' is numeric", {
+  expect_type(data$pct, "double")
+})
+
+# Test that there are no missing values in the dataset
+test_that("no missing values in dataset", {
+  expect_true(all(!is.na(data)))
+})
+
+# Test that each poll (by poll_id) sums to 1 in pct column
+test_that("pct sums to 1 within each poll_id", {
+  pct_sums <- data %>% group_by(poll_id) %>% summarize(pct_sum = sum(pct))
+  expect_true(all(abs(pct_sums$pct_sum - 1) < 1e-6))  # Allow for minor floating-point variations
+})
+
+# Test that 'num_candidates' is between 2 and 5
+test_that("num_candidates is between 2 and 5", {
+  expect_true(all(data$num_candidates >= 2 & data$num_candidates <= 5))
+})
+
+# Test that 'transparency_score' is within expected range (0 to 10)
+test_that("transparency_score is between 0 and 10", {
+  expect_true(all(data$transparency_score >= 0 & data$transparency_score <= 10))
+})
+
+# Test that 'state' contains only valid US states
+valid_states <- c("Alabama", "Alaska", "Arizona", "Arkansas", "California", "Colorado", 
[…]

### 2024-11-01 paper/paper.qmd
Updated clean_data and test_data
All related outputs are changed as a consequence.

@@
 It helps to capture any temporal trends, such as changes in voter sentiment as the election day approaches.
-
-### Multicollinearity Considerations
-```{r pairplot}
-#| warning: false
-#| message: false
-#| echo: false
-numeric_data <- data %>% 
-  select(where(is.numeric)) %>% 
-  select(numeric_grade, pollscore, transparency_score) %>% 
-  filter(complete.cases(.))
-
-# Create a pair plot
-ggpairs(numeric_data) +
-  theme(
-    axis.text.x = element_text(angle = 45, hjust = 1, size = 8, margin = margin(t = 10)),
-    axis.text.y = element_text(size = 8, margin = margin(r = 10)),
-    strip.text = element_text(size = 6)  # Adjusts the size of variable name tags
-  )
-```
-While selecting the predictors for the model, multicollinearity was a key concern.
-Multicollinearity occurs when two or more predictors are highly correlated, which can inflate the variance of the coefficient estimates and make the model less reliable.
-In our pair plot analysis, we observed a high correlation between "numeric_grade" and "pollscore," suggesting that they measure similar aspects of polling quality.
-
-To mitigate the effects of multicollinearity, "numeric_grade" was excluded from the model.
-We opted to retain "pollscore" and "transparency_score" as the primary indicators of poll quality because they provide complementary insights—"pollscore" reflects the overall quality and reliability, while "transparency_score" captures the openness in reporting methods.
-This approach ensures that the model avoids redundancy and improves the stability of the coefficient estimates.
 

### 2024-11-01 scripts/02-clean_data.R

@@ -13,7 +13,7 @@ data <- read_csv("data/01-raw_data/president_polls.csv")
 
 # Select rows
 data <- data %>%
-  filter(numeric_grade >= 2.0)
+  filter(transparency_score >= 8.0)
 
 # Mutate days_towards_election
 data_a <- data %>% 
@@ -30,39 +30,16 @@ data$days_towards_election <- data_a$days_towards_election
 # Select columns
 selected_columns <- c(
   "poll_id",
-  "question_id",
-  "pollster", 
-  "sponsors", 
-  "numeric_grade", 
-  "pollscore", 
-  "methodology", 
   "transparency_score", 
   "state", 
-  "start_date", 
   "end_date", 
-  "sponsor_candidate", 
-  "sponsor_candidate_party", 
-  "question_id", 
-  "sample_size", 
-  "population", 
-  "population_full",
-  "tracking", 
-  "notes", 
-  "source", 
-  "internal", 
-  "partisan", 
-  "race_id", 
-  "ranked_choice_reallocated", 
-  "ranked_choice_round", 
-  "hypothetical", 
   "party", 
-  "answer", 
   "candidate_name", 
   "days_towards_election",
   "pct"
 )
-data <- data %>% 
-  select(all_of(selected_columns))
+data <- data %>%
+  select(all_of(selected_columns)) 
 
 
 

### 2024-11-01 scripts/03-test_analysis_data.R

@@ -7,89 +7,42 @@
 
 #### Workspace setup ####
 library(tidyverse)
-library(testthat)
+library(validate)
 
+# Load data
 data <- read_csv("data/00-simulated_data/simulated_polls.csv")
+data <- read_csv("data/02-analysis_data/cleaned_president_polls.csv")
+
+# Define validation rules
+rules <- validator(
+  is.numeric(poll_id),                           # 'poll_id' is integer type
+  is.character(state),                           # 'state' column is character type
+  all(as.Date(end_date, format="%m/%d/%y") >= as.Date("2021-01-01") & 
+        as.Date(end_date, format="%m/%d/%y") <= as.Date("2024-11-05")), # 'end_date' is between 2021-01-01 and 2024-11-05
+  is.numeric(transparency_score),                # 'transparency_score' is numeric type
+  is.character(candidate_name),                  # 'candidate_name' column is character type
+  is.numeric(pct),                               # 'pct' column is numeric type
+  all(transparency_score >= 0 & transparency_score <= 10), # 'transparency_score' is between 0 and 10
+  
+  # 'state' contains only valid US states or NA values
+  all(is.na(state) | state %in% c("Alabama", "Alaska", "Arizona", "Arkansas", "California", "Colorado", 
+                                  "Connecticut", "Delaware", "Florida", "Georgia", "Hawaii", "Idaho", 
+                                  "Illinois", "Indiana", "Iowa", "Kansas", "Kentucky", "Louisiana", 
+                                  "Maine", "Maryland", "Massachusetts", "Michigan", "Minnesota", 
+                                  "Mississippi", "Missouri", "Montana", "Nebraska", "Nevada", "New Hampshire", 
+                                  "New Jersey", "New Mexico", "New York", "North Carolina", "North Dakota", 
+                                  "Ohio", "Oklahoma", "Oregon", "Pennsylvania", "Rhode Island", 
+                                  "South Carolina", "South Dakota", "Tennessee", "Texas", "Utah", 
+                                  "Vermont", "Virginia", "Washington", "West Virginia", "Wisconsin", "Wyoming", 
+                                  "Nebraska CD-1", "Nebraska CD-2", "Nebraska CD-3","Maine CD-1", "Maine CD-2")),
+  
+  all(pct >= 0 & pct <= 100) # 'pct' is a percentage between 0 and 100 for each candidate
+)
+
[…]

### 2024-11-01 paper/paper.qmd
Updated Model Section

@@
 
-The goal of our modeling strategy is twofold.
-Firstly, we aim to estimate the candidates' support levels based on various polling-related factors, accounting for differences in poll quality, timing, sample characteristics, and geographical variations.
-Secondly, we seek to assess how well these factors predict electoral outcomes and identify which variables are most influential in shaping public opinion.
+In this study, we employ two main models to forecast the outcome of the 2024 U.S.
+Presidential Election using polling data for the candidates Kamala Harris and Donald Trump.
+The models, a Baseline Model (Winner-Take-All National Model) and a Primary Model (Swing State-Based Model), provide two distinct but complementary approaches to assessing candidate support.
+The Baseline Model aggregates national polling data to project which candidate is likely to win based on national polling trends and assigns all electoral votes to the candidate with the higher projected national percentage on election day.
+This approach offers a straightforward prediction of overall voter sentiment across the country and captures the aggregate trend of support for each candidate as the election approaches.
 
-The model employed is a multiple linear regression, where the response variable is the percentage of support ("pct") for each candidate in the polls.
-The predictors include "pollscore" (indicating the quality of the poll), "transparency_score" (reflecting methodological disclosure), "sample_size" (number of respondents), "state" (geographical indicator), and "days_towards_election" (timing of the poll).
-
-## Model set-up
+On the other hand, the Primary Model is designed to provide a more granular projection by focusing on polling data at the state level, particularly for key swing states.
+This model assumes that the winner in each swing state can be determined by state-specific polling trends, and it projects support for each candidate within these competitive regions.
+By combining outcomes from both swing states and solid states, this model allows for a more nuanced prediction that aligns with the actual mechanics of the Electoral College.
+Together, these models are well-suited to address both the general national polling trends and the crucial role of swing states in determining the final electoral outcome.
 
@@
 ```
+
+## 1. Baseline Model (Winner-Take-All National Model)
+The baseline model aggregates national polling data to predict a winner, with all electoral votes awarded to the candidate with the higher national polling percentage.
+
+1. **National Polling Projections**  
+   Let:
+   - $P_H(t)$: Harris’s national polling percentage at $t$ days towards the election.
+   - $P_T(t)$: Trump’s national polling percentage at $t$ days towards the election.
+
+   We model each candidate’s polling as:
+   $$
+   P_H(t) = \alpha_H + \beta_H t
+   $$
+   $$
+   P_T(t) = \alpha_T + \beta_T t
+   $$
+
+   where $\alpha_H$ and $\alpha_T$ are the intercepts (predicted percentages on election day, $t = 0$), and $\beta_H$ and $\beta_T$ are the slopes.
+
+2. **Election Day Prediction**  
+   On election day:
+   $$
+   P_H(0) = \alpha_H, \quad P_T(0) = \alpha_T
+   $$
+
+3. **Winner-Take-All Outcome**  
+   The candidate with the higher predicted national percentage wins all electoral votes:
+   $$
+   W = 
+   \begin{cases} 
+   \text{Harris wins (all electoral votes)} & \text{if } \alpha_H > \alpha_T \\
+   \text{Trump wins (all electoral votes)} & \text{otherwise}
+   \end{cases}
+   $$
 
@@
 
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-intercept_results <- final_results %>%
-  filter(term == "(Intercept)")
-
-# Spread the results into wide format
-intercept_wide <- intercept_results %>%
-  select(state, candidate, estimate) %>%
-  pivot_wider(names_from = candidate, values_from = estimate, values_fill = NA)
-
-# Calculate the difference in estimates between candidates
-intercept_wide <- intercept_wide %>%
-  mutate(difference = `Kamala Harris` - `Donald Trump`)
-
-# View the results with differences
-kable(intercept_wide)
-```
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-solid_state_votes <- data.frame(
-  Candidate = c("Harris", "Trump"),
-  Solid_State_Votes = c(226, 219)
-)
-intercept_wide$electoral_votes <- c(6, 11, 10, 15, 19, 16, 16)
-
-swing_state_results <- intercept_wide %>%
-  mutate(Winner = ifelse(difference > 0, "Harris", "Trump")) %>%
-  group_by(Winner) %>%
-  summarize(Predicted_Swing_State_Votes = sum(electoral_votes))
-
-total_votes <- solid_state_votes %>%
-  left_join(swing_state_results, by = c("Candidate" = "Winner")) %>%
-  mutate(Predicted_Swing_State_Votes = ifelse(is.na(Predicted_Swing_State_Votes), 0, Predicted_Swing_State_Votes),
-         Total_Predicted_Votes = Solid_State_Votes + Predicted_Swing_State_Votes)
-
-kable(total_votes, caption = "Predicted Electoral Votes for Each Candidate")
-```
-
-### Model Formulations
-
-#### 1. Baseline Model (Winner-Take-All National Model)
-The baseline model aggregates national polling data to predict a winner, with all electoral votes awarded to the candidate with the higher national polling percentage.
-
-1. **National Polling Projections**  
-   Let:
-   - $P_H(t)$: Harris’s national polling percentage at $t$ days towards the election.
-   - $P_T(t)$: Trump’s national polling percentage at $t$ days towards the election.
-
-   We model each candidate’s polling as:
-   $$
-   P_H(t) = \alpha_H + \beta_H t
-   $$
-   $$
-   P_T(t) = \alpha_T + \beta_T t
-   $$
-
-   where $\alpha_H$ and $\alpha_T$ are the intercepts (predicted percentages on election day, $t = 0$), and $\beta_H$ and $\beta_T$ are the slopes.
-
-2. **Election Day Prediction**  
-   On election day:
-   $$
-   P_H(0) = \alpha_H, \quad P_T(0) = \alpha_T
-   $$
-
-3. **Winner-Take-All Outcome**  
-   The candidate with the higher predicted national percentage wins all electoral votes:
-   $$
-   W = 
-   \begin{cases} 
-   \text{Harris wins (all electoral votes)} & \text{if } \alpha_H > \alpha_T \\
-   \text{Trump wins (all electoral votes)} & \text{otherwise}
-   \end{cases}
-   $$
-
-#### 2. Primary Model (Swing State-Based Model)
+## 2. Primary Model (Swing State-Based Model)
 This model forecasts electoral outcomes by projecting state-level polling results for each candidate, combining swing state outcomes with votes from solid states.
@@
 
-The multiple linear regression approach is justified for several reasons.
-Firstly, it provides a straightforward method for estimating the relationship between the percentage of support for each candidate and the set of predictors, allowing for the quantification of the impact of each factor.
-This is suitable for forecasting purposes where interpretability and direct estimation of effects are important.
+The two-model approach is justified by the need to capture both national and state-level dynamics in election forecasting.
+The Baseline Model’s focus on national polling trends is appropriate for understanding the overall sentiment of the voting population, providing an aggregate view that reflects general support levels for each candidate.
+Since national support can indicate the broader trajectory of an election, the Winner-Take-All National Model captures this sentiment in a straightforward, interpretable way.
+The inclusion of a temporal component, represented by days toward the election, allows both models to track changes in support levels as the election day approaches.
+This time-based element is critical, as voter sentiment often fluctuates and solidifies in the lead-up to an election, especially with the influence of campaign events and media coverage.
 
-Secondly, the linear model is flexible enough to accommodate a range of continuous and categorical predictors, such as "pollscore" and "state." The model captures the additive effect of each predictor on the outcome, making it possible to assess the contribution of polling quality, timing, sample characteristics, and regional differences individually.
+The Primary Model, focusing on swing states, is particularly valuable because of the unique structure of the U.S.
+Electoral College, where specific states can disproportionately influence the final outcome.
+Including state-specific intercepts and slopes enables this model to account for localized variations in support, reflecting the critical importance of state-level outcomes in swing regions.
+By incorporating state indicators, this model can address the heterogeneity of voting behavior across different regions, capturing the specific dynamics of battleground states where candidate support may diverge significantly from national trends.
+Aggregating the electoral votes based on projected winners in both swing and solid states makes this model well-aligned with real-world electoral processes, enhancing its practical utility in forecasting the election outcome.
 
-Furthermore, linear regression is appropriate here because it assumes a linear relationship between the predictors and the response variable.
-Given the nature of the predictors—where factors like polling quality and sample size are expected to linearly influence support levels—it aligns well with the data characteristics.
-
-Lastly, the choice of linear regression allows for diagnosing issues such as multicollinearity, which was a potential concern with correlated variables.
-By excluding highly correlated predictors (e.g., "numeric_grade"), the model specification avoids problems with unstable coefficient estimates and enhances interpretability.
-
-Overall, the linear regression model provides a well-suited approach to understanding and predicting candidate support in the context of the 2024 U.S. Presidential Election.
+Additionally, the linear relationship assumed in these models is justified by the often gradual and linear shifts in voter preferences over short periods, especially as the election date nears.
+State projections are treated independently, consistent with the winner-take-all approach in most U.S.
+states.
+Although linear models are generally effective for capturing large-scale polling trends, alternative approaches, such as Bayesian methods for quantifying uncertainty, could be considered for highly volatile polling scenarios.
+Nonetheless, the current models’ simplicity and interpretability make them particularly suitable for capturing the aggregate and state-level trends necessary for this election forecast, providing a balanced approach that aligns well with the complexities of the U.S.
+electoral system.
 
 # Results{#sec-results}
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
 
-The results from the linear regression models for both Kamala Harris and Donald Trump indicate the impact of the selected predictors on their percentage of support in the polls.
-The model summaries provide estimates for each coefficient, along with their statistical significance.
+```
 
-## Model Summaries
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+intercept_results <- final_results %>%
+  filter(term == "(Intercept)")
 
-For each candidate, the models show the estimated effects of the following predictors: poll score, transparency score, sample size, state, and days towards election. Key findings include:
+# Spread the results into wide format
+intercept_wide <- intercept_results %>%
+  select(state, candidate, estimate) %>%
+  pivot_wider(names_from = candidate, values_from = estimate, values_fill = NA)
 
-- **Poll Score**: For both candidates, higher poll scores are positively associated with higher predicted support.
-This indicates that polls with better quality and reliability tend to show greater support levels for the candidates.
-- **Transparency Score**: The transparency score has a significant effect on the predicted support, suggesting that polls with more disclosure practices yield different results compared to less transparent polls.
-- **Sample Size**: Larger sample sizes have a positive association with predicted support levels. This aligns with the expectation that more extensive polling samples provide more precise estimates.
-- **State**: The state variable captures regional differences in candidate support, highlighting significant variations across different states.
-- **Days Towards Election**: The timing of the poll relative to the election date also impacts the predicted support.
-As the election date approaches, there is typically a convergence in voter preferences, affecting the estimated levels of support.
+# Calculate the difference in estimates between candidates
+intercept_wide <- intercept_wide %>%
+  mutate(difference = `Kamala Harris` - `Donald Trump`)
 
-The model results confirm that these factors collectively provide a reasonable basis for predicting support for the candidates.
-The residuals and diagnostic checks (not shown here) indicate no major violations of model assumptions, suggesting that the linear model fits the data adequately.
+# View the results with differences
+kable(intercept_wide)
+```
+
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+solid_state_votes <- data.frame(
+  Candidate = c("Harris", "Trump"),
+  Solid_State_Votes = c(226, 219)
+)
+intercept_wide$electoral_votes <- c(6, 11, 10, 15, 19, 16, 16)
+
+swing_state_results <- intercept_wide %>%
+  mutate(Winner = ifelse(difference > 0, "Harris", "Trump")) %>%
+  group_by(Winner) %>%
+  summarize(Predicted_Swing_State_Votes = sum(electoral_votes))
+
+total_votes <- solid_state_votes %>%
+  left_join(swing_state_results, by = c("Candidate" = "Winner")) %>%
+  mutate(Predicted_Swing_State_Votes = ifelse(is.na(Predicted_Swing_State_Votes), 0, Predicted_Swing_State_Votes),
+         Total_Predicted_Votes = Solid_State_Votes + Predicted_Swing_State_Votes)
+
+kable(total_votes, caption = "Predicted Electoral Votes for Each Candidate")
+```
+
+![Result](../other/photos/Predicted_Result.png){#fig-result}
 

### 2024-11-01 paper/paper.qmd
Update baseline result table

@@
 # Combine results for all candidates into a single data frame
-final_results <- bind_rows(results, .id = "candidate")
+final_results_baseline <- bind_rows(results, .id = "candidate")
 
 # View the final results
-kable(final_results)
+kable(final_results_baseline)
 
@@
 
+intercept_results_baseline <- final_results_baseline %>%
+  filter(term == "(Intercept)")
+
+# Spread the results into wide format
+intercept_wide_baseline <- intercept_results %>%
+  select(candidate, estimate) %>%
+  pivot_wider(names_from = candidate, values_from = estimate, values_fill = NA)
+
+# Calculate the difference in estimates between candidates
+intercept_wide_baseline <- intercept_wide %>%
+  mutate(difference = `Kamala Harris` - `Donald Trump`)
+
+# View the results with differences
+kable(intercept_wide)
 ```

### 2024-11-01 paper/paper.qmd
Fixed last update

--- 2024-11-01 paper/paper.qmd
@@
 
+intercept_results_baseline <- final_results_baseline %>%
+  filter(term == "(Intercept)")
+
+# Spread the results into wide format
+intercept_wide_baseline <- intercept_results_baseline %>%
+  select(candidate, estimate) %>%
+  pivot_wider(names_from = candidate, values_from = estimate, values_fill = NA)
+
+# Calculate the difference in estimates between candidates
+intercept_wide_baseline <- intercept_wide_baseline %>%
+  mutate(difference = `Kamala Harris` - `Donald Trump`)
+
+# View the results with differences
+kable(intercept_wide_baseline)
 ```

### 2024-11-01 paper/paper.qmd
Updated abstract

@@
 The U.S.
-Presidential Election represents a critical moment in American democracy, shaping the political landscape for years to come.
-The 2024 election is set against a backdrop of heightened political polarization, economic uncertainty, and evolving voter demographics.
-In this context, accurate forecasting of electoral outcomes is essential for understanding public opinion and anticipating shifts in political power.
+Presidential Election is a critical event shaping the country’s political direction, often influenced by a complex interplay of public opinion, socio-economic factors, and electoral mechanisms.
+In recent election cycles, the predictive accuracy of polling has been a topic of significant discussion, as polls not only gauge public sentiment but also influence campaign strategies, media narratives, and voter perceptions.
+However, challenges such as non-response bias, methodological inconsistencies, and a misalignment between the popular vote and electoral outcomes highlight the need for a robust forecasting model that captures both national and state-specific trends.
 
-Polling has long been a central tool for gauging voter sentiment, providing snapshots of the electorate's preferences at different points in time.
-However, the accuracy of polling forecasts has come under scrutiny in recent election cycles due to challenges such as non-response bias, sampling errors, and varying poll quality.
-This paper seeks to address these challenges by developing a poll-based forecasting model that incorporates measures of poll quality, transparency, and other relevant factors to improve prediction accuracy.
+This paper aims to address these challenges by developing a polling-based forecasting model for the 2024 U.S.
+Presidential Election, with a focus on the two main candidates, Kamala Harris and Donald Trump.
+Using a dual-model approach, we employ a **Baseline Model** to provide a broad national outlook and a **Primary Model** to examine state-level dynamics, especially in key swing states.
+The Baseline Model aggregates national polling data to predict which candidate would win a majority of popular support, while the Primary Model applies a more nuanced, state-level analysis aligned with the electoral college structure.
+This combination seeks to address the gap in existing models, which often fail to account for the specific impact of swing states on electoral outcomes, despite their pivotal role in determining the presidency.
 
-The primary estimand in this analysis is the percentage of support for each candidate as indicated by polling data.
-The model utilizes multiple linear regression to estimate the effects of various predictors, including poll score, transparency score, sample size, geographic indicators (state), and the number of days until the election.
-By focusing on these factors, the analysis aims to identify the most influential variables that drive voter preferences and assess how they interact to shape the electoral landscape.
+Our analysis indicates that while Kamala Harris shows a lead in national polling, as reflected in the Baseline Model, the decisive factors lie within swing states such as Pennsylvania, Michigan, and Wisconsin, where the Primary Model highlights Harris’s slight advantages.
+The state-level predictions from the Primary Model suggest a possible electoral college win for Harris, projecting her to receive 292 electoral votes, above the 270-vote threshold needed to secure the presidency.
+This finding underscores the unique nature of U.S.
+elections, where winning the national popular vote does not necessarily translate to an electoral college victory.
+Our approach, by leveraging poll data with attention to poll quality, transparency, sample size, and geographic variation, seeks to provide a nuanced and accurate forecast that reflects both general sentiment and the regional intricacies of the election.
 
-Results from the model provide insights into the relationship between polling characteristics and predicted support levels for Kamala Harris and Donald Trump.
-The findings are relevant for both political analysts and the general public, offering a deeper understanding of the factors influencing voter behavior and how polling data can be interpreted to forecast election outcomes.
+The structure of this paper is as follows: @sec-data provides an overview of the dataset, detailing the polling data sources, variables, and preprocessing steps.
+@sec-model outlines the modeling approach, presenting the rationale behind the Baseline and Primary Models and discussing their respective contributions to the analysis.
+@sec-results presents the results, including national and state-level predictions, followed by @sec-disc, which explores the implications of these findings, discusses limitations, and suggests future research directions.
+An appendix provides additional methodological details and diagnostics.
 
-The remainder of this paper is structured as follows.
-@sec-data describes the dataset and variables used in the analysis, including the steps taken to clean and preprocess the data.
-@sec-model details the modeling approach, justification, and the rationale for the selection of predictors.
-@sec-results presents the model findings, while @sec-disc explores the implications, limitations, and future directions for research.
-An appendix provides additional methodological details and diagnostics.
+## Estimand
+
+The primary estimand in this study is the predicted percentage of support each candidate will receive on election day, both nationally and within critical swing states.
+This percentage serves as the foundation for forecasting which candidate is likely to win the election, by capturing trends in public sentiment over time and projecting how these trends may manifest in the final vote count.
 
@@
 
-# Data{#sec-data}
+# Data {#sec-data}
 
-## Overview of Data
-The dataset used in this analysis comprises polling information for the 2024 U.S.
-Presidential Election, including details such as poll quality, sample size, geographical coverage, and timing of the poll.
-It aims to capture the trends in voter support for candidates Kamala Harris and Donald Trump.
+## Dataset Overview
 
-## Measurement and Limitations
-The data reflects polling information collected from various sources, each with its own methodology and potential biases.
-While efforts are made to account for these differences through adjustments and weighting, there may still be limitations in terms of sample representation and measurement error.
-Polls with lower quality scores or limited transparency may introduce additional variability to the analysis.
+This study leverages a dataset of polling data for the 2024 U.S.
+Presidential Election, focusing on predicting support for the two main candidates, Kamala Harris and Donald Trump.
+Each entry in the dataset represents results from individual polls, capturing both the timing and geographical scope of polling, which is crucial for analyzing national trends and state-specific shifts, particularly in key swing states.
+By collating data from multiple polling sources, the dataset captures a broad snapshot of voter sentiment across the country, reflecting variations across time, poll methodologies, and geographic regions.
 
-## Outcome Variable
-The outcome variable of interest is the percentage of support ("pct") that each candidate receives in the polls.
-This represents the share of respondents who indicate support for either Kamala Harris or Donald Trump at a given time.
+The outcome variable, **Polling Percentage ("pct")**, represents the percentage of respondents in each poll who indicate support for either Harris or Trump.
+This variable is central to our analysis, as it reflects the changing landscape of voter sentiment and serves as the basis for our forecasts.
 
-## Predictor Variables
+## Predictor and Additional Variables
 
-### Poll Score
-The "pollscore" variable represents the quality and reliability of each poll.
-Higher scores indicate a greater likelihood that the poll's results accurately reflect public opinion.
-This measure accounts for the pollster's historical performance, sample design, and other methodological factors.
-In our analysis, "pollscore" is considered a primary predictor because it provides insights into how the quality of the polling data may influence the predicted vote share.
+- **Days Toward Election ("days_towards_election")**: The primary predictor in the model, this variable indicates the number of days remaining until the election at the time each poll was conducted.
+It is essential for capturing time-based trends, enabling the model to adjust for shifts in public opinion as the election approaches.
+As the election nears, this variable helps illustrate the patterns of support stabilization, often observed closer to election day.
 
-### Transparency Score
-The "transparency_score" variable captures the extent to which pollsters disclose their methodology and data collection practices.
-Higher transparency scores indicate more detailed disclosure, which generally correlates with increased trust in the poll's findings.
-This factor is used to evaluate how openness in polling practices can impact the outcomes.
+Additional potential predictors include variables reflecting the quality, sample characteristics, and transparency of each poll, which help contextualize the primary predictor and provide an understanding of polling reliability:
 
-### Sample Size
-The number of respondents in each poll, represented by "sample_size," is a key factor influencing the precision of polling estimates.
-Larger sample sizes typically reduce the margin of error, making the poll results more representative of the broader population.
+- **Poll Quality Score ("pollscore")**: This variable captures the methodological reliability of each poll, including factors such as sampling technique and historical accuracy.
+Polls with higher scores typically offer more robust estimates, as they reflect the pollster’s performance and adherence to reliable sampling practices.
 
-### State
-The "state" variable accounts for regional differences in voting preferences.
-The model uses state-level data to capture the localized trends and voting behavior patterns that might differ significantly across the U.S.
+- **Transparency Score ("transparency_score")**: This score measures the level of methodological detail each poll discloses.
+Higher transparency generally correlates with increased confidence in the data, as it indicates comprehensive disclosure of methods, sample details, and collection practices.
 
-### Days Towards Election
-This variable measures the number of days remaining until the election at the time the poll was conducted.
-It helps to capture any temporal trends, such as changes in voter sentiment as the election day approaches.
+- **Sample Size ("sample_size")**: The number of respondents in each poll is crucial for assessing precision.
+Larger sample sizes tend to reduce the margin of error, making the estimates more representative of the general population.
 
-## Data Cleaning
-In the data cleaning process, we adjusted the dataset to calculate the expected votes for Kamala Harris and Donald Trump by scaling their average percentages according to the sample size.
-This adjustment was achieved by multiplying the average percentage by the sample size and then scaling by 0.01.
-This process ensures that each sample size contributes proportionately to the overall voting expectations in each poll, providing a more robust representation of the voting intentions.
-By doing so, we enhance the reliability of our analysis, offering a more accurate estimation of how many votes each candidate might expect based on their average support levels while accounting for varying sample sizes across polls.
+- **State ("state")**: This geographic variable distinguishes between national and state-level polls, allowing the model to capture regional variations in voter support.
+State-specific polling data are particularly valuable for modeling outcomes in swing states, where election outcomes often hinge on narrow margins.
+
+## Measurement and Data Processing
+
+Each variable in the dataset is constructed to accurately reflect polling characteristics across various dimensions of time, geography, and poll quality.
+Poll quality and transparency scores are derived based on historical pollster performance and disclosure levels, offering an indirect measure of data reliability.
+The primary predictor, **days toward election**, and the outcome variable, **pct**, are drawn directly from each poll entry.
+Polling percentages are scaled by sample size, which provides a weighted measure of candidate support, ensuring that polls with larger sample sizes have a proportionally greater impact on model predictions.
+
+To enhance interpretability and prediction accuracy, we adjusted the dataset by scaling polling percentages to reflect each poll’s sample size, multiplying average support by sample size, and normalizing by 0.01.
+This process ensures that larger samples contribute more meaningfully to the model’s overall prediction, thus offering a balanced representation of likely voting intentions.
+
+## Exploratory Data Analysis and Summary Statistics
+
+To understand the general trends in the data, we conducted exploratory data analysis using summary statistics and visualizations.
+Figure 1 (below) illustrates the polling percentages for each candidate over time, allowing us to observe fluctuations in support as the election day draws near.
 
@@
 #| label: fig-pct
+#| fig-cap: Polling Percentage over Time by Candidate
 data %>% filter(candidate_name %in% c("Kamala Harris", "Donald Trump")) %>% 
@@
   labs(
-    title = "Polling Percentage over Time by Candidate",
     x = "End Date",
@@
 #| warning: false
+#| label: tbl-baseline
+#| tbl-cap: Baseline Model
+
 fit_model <- function(data, candidate) {
@@
 #| warning: false
+#| label: tbl-primary
+#| tbl-cap: Primary Model
+
 data_nevada <- data %>% filter(state == "Nevada") 
@@
 # Results{#sec-results}
+The results from our forecasting models provide insight into predicted support levels for Kamala Harris and Donald Trump, drawing from both national and state-level polling data.
+Each model presents a distinct view of candidate support and projected outcomes based on trends in polling data as election day approaches.
+
+## National Polling Trends and Baseline Model Results
+The Baseline Model evaluates national polling data to project which candidate would win all electoral votes based on the higher national polling percentage on election day.
+The intercept term, representing predicted support on election day, shows that Kamala Harris is expected to receive approximately 48.19% of the national vote, while Donald Trump is projected to receive around 46.01%.
+This 2.18 percentage point lead for Harris in the Baseline Model suggests a slight advantage for her on a national scale.
+This model illustrates overall voter sentiment trends, capturing how each candidate's support changes as election day approaches and indicating a national-level lean toward Harris if these trends hold.
 ```{r}
@@
 #| warning: false
+#| label: tbl-baselineresult
+#| tbl-cap: Baseline Model Result
 
@@
 
+## Swing State Analysis and Primary Model Results
+In contrast, the Primary Model delves into state-specific polling data, focusing on swing states where vote margins are especially narrow and could decisively impact the electoral outcome.
+Intercept estimates for each candidate across key swing states show a mixed pattern, with Harris projected to lead in states like Wisconsin (49.30% vs.
+46.67%) and Pennsylvania (48.84% vs.
+47.21%), where her support surpasses Trump’s by 2.64 and 1.63 percentage points, respectively.
+However, Trump maintains a lead in Arizona (48.80% vs.
+47.10%) and Georgia (48.59% vs.
+47.82%), reflecting the competitive nature of these swing states.
+
+Table 1 provides a summary of intercept estimates for both candidates across swing states, showing how close these races remain.
+Harris's estimated advantage in states like Wisconsin and Pennsylvania signals potential strategic wins in the electoral college, while Trump’s narrow leads in Arizona and Georgia underscore the contested nature of the 2024 election in these battleground areas.
 ```{r}
@@
 #| warning: false
+#| label: tbl-primaryresult
+#| tbl-cap: Primary Model Result
+
 intercept_results <- final_results %>%
@@
 ```
+
+## Electoral Vote Projections
+Integrating the swing state projections with solid state predictions, the Primary Model estimates the electoral vote totals for each candidate.
+Kamala Harris is projected to win 292 electoral votes, surpassing the 270-vote threshold required to secure victory.
+Donald Trump, by comparison, is projected to receive 246 electoral votes.
+This projection, based on aggregating state-level outcomes, suggests that Harris has a favorable chance of achieving the necessary electoral college majority if current polling trends continue.
+The model indicates that Harris’s projected wins in swing states like Wisconsin, Michigan, and Pennsylvania could be critical to her securing an electoral majority.
+
+These results from both the Baseline and Primary Models provide distinct perspectives on the likely outcome of the 2024 U.S.
+Presidential Election.
+The Baseline Model projects a national-level popular vote advantage for Harris, while the Primary Model’s state-based approach points to an electoral college path for her, albeit with highly competitive results in key swing states that remain essential to the final outcome.
 
@@
 
-## Key Findings
+## Summary of Contributions
 
-The analysis demonstrates that poll quality (as measured by poll scores) and transparency are significant predictors of support for both Kamala Harris and Donald Trump.
-Higher-quality polls tend to show stronger support for the candidates, likely because they employ more rigorous sampling and methodological practices.
-Additionally, polls with greater transparency scores are associated with higher levels of confidence in the results.
+This paper presents a polling-based forecasting model for the 2024 U.S.
+Presidential Election, utilizing two complementary approaches to predict candidate support for Kamala Harris and Donald Trump.
+The **Baseline Model** (Winner-Take-All National Model) offers a straightforward projection of overall national sentiment by aggregating national polling data, while the **Primary Model** (Swing State-Based Model) provides a more refined, state-specific analysis, focusing especially on swing states crucial to the electoral college outcome.
+The two models together balance broad sentiment tracking with the targeted detail needed for swing-state-specific electoral forecasting.
+Through this dual approach, the analysis captures both national-level trends and the granular dynamics within pivotal swing states, offering an informative look into the likely distribution of popular and electoral votes as election day approaches.
 
-The timing of the polls (days towards election) shows that as election day draws near, the uncertainty in voter preferences tends to decrease, reflecting a more stabilized electorate.
-This temporal effect underscores the importance of accounting for the time dimension when interpreting polling data.
+## Insights into Election Dynamics
 
-Regional differences captured by the state variable reveal that voter support is not uniform across the U.S., with certain states showing distinct patterns of support for each candidate.
-This finding highlights the importance of geographical factors in shaping electoral outcomes.
+The results reveal critical insights into the nature of U.S.
+elections and the structure of the electoral college system.
+One key takeaway from this analysis is that winning the national popular vote does not guarantee a candidate’s victory in the U.S.
+presidential election.
+The Baseline Model indicates a potential popular vote lead for Kamala Harris; however, the ultimate victory depends on success within specific swing states, as highlighted by the Primary Model.
+This reflects a unique feature of the U.S.
+election system, where a candidate can win the presidency without securing the majority of the popular vote by focusing on electoral votes, especially in key battleground regions.
+Therefore, while Harris’s projected national lead is notable, the Primary Model’s swing-state analysis underscores the importance of targeting resources and strategies in these competitive areas.
 
-## Weaknesses and Limitations
+## Comparison of Model Effectiveness
 
-While the model provides valuable insights, it has limitations.
-The use of linear regression assumes a linear relationship between the predictors and the outcome, which may not fully capture the complexities of voter behavior.
-Additionally, the reliance on poll scores and transparency measures may not account for all sources of bias in the data, such as social desirability bias or non-response bias.
+Each model brings distinct strengths and weaknesses, serving different forecasting needs.
+The **Baseline Model** provides a broad, data-rich perspective, aggregating a large volume of polling data to capture general national sentiment.
+This simplicity allows for a straightforward, easy-to-understand representation of national trends in support levels.
+However, this model does not account for the state-by-state dynamics critical to winning the electoral college and may oversimplify the complexities of an election where only the electoral votes, not the popular vote, decide the winner.
 
-Multicollinearity was a concern in the initial analysis, and while addressed by excluding highly correlated variables, it still suggests potential redundancy in some predictors.
-Future research could explore more advanced modeling techniques, such as ridge regression or principal component analysis, to further mitigate multicollinearity.
+In contrast, the **Primary Model** offers more precise predictions by incorporating state-level polling data for swing states, which are decisive in the electoral college outcome.
+By focusing on these battleground areas, the model provides a nuanced picture that aligns more closely with the mechanics of the U.S.
+election system.
+This model, however, requires more detailed data for each state and is therefore less broadly applicable to a general sense of popular sentiment but is far more insightful for understanding likely outcomes under the electoral college system.
+
+## Limitations and Areas for Improvement
+
+Despite the insights provided by both models, there are limitations to this approach.
+The models rely on polling data, which is inherently subject to variability and potential biases, such as non-response bias, sampling errors, and the limitations of data collection methods across different polling organizations.
+Additionally, both models assume a linear trend in polling changes as election day approaches, which may not fully capture sudden shifts in voter sentiment that can occur due to unforeseen events, campaign dynamics, or emerging social issues.
+
+Furthermore, the Baseline Model’s national aggregate approach does not account for the unique political landscape within individual states, potentially underestimating the nuances in regional voting behaviors.
+Meanwhile, the Primary Model, while more granular, requires extensive state-specific data that may not be consistently available or reliable across all swing states.
 
@@
 
-Further research could incorporate more dynamic modeling approaches, such as time-series analysis, to better capture the changing nature of voter preferences over time.
-Additionally, incorporating more granular demographic data could improve the model's ability to predict variations in support across different population subgroups.
+Future research could benefit from integrating more sophisticated methods to address the limitations of linear assumptions and polling variability.
+For instance, incorporating time-series models that allow for non-linear trends could better capture sudden shifts in voter sentiment over time.
+Additionally, exploring Bayesian models to handle polling uncertainty more effectively may provide a way to quantify the degree of confidence in each state’s predicted support levels.
 
-Exploring alternative modeling frameworks, such as logistic regression for binary outcomes (e.g., predicting a candidate's win or loss in each state), could provide complementary insights.
-Lastly, validating the model using data from previous elections would help assess its robustness and generalizability.
+Further improvements could also be achieved by incorporating demographic and socio-economic data to create more robust and representative models of each state’s voter base.
+Finally, validating these models using historical data from previous elections could enhance their robustness and accuracy, offering a clearer picture of how these methods perform under different electoral conditions.
+
+In conclusion, this study demonstrates the importance of integrating both national and state-level data for election forecasting and highlights how U.S.
+election outcomes hinge on both popular and electoral vote dynamics.
+By combining the strengths of a broad national model and a targeted swing-state approach, this paper provides a comprehensive framework for anticipating electoral outcomes in a system where popular sentiment and electoral mechanics are often misaligned.
 
@@
 
-# Model details {#sec-model-details}
-
-## Posterior predictive check
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-```
-
-## Diagnostics
-
-```{r}
-#| echo: false
-#| message: false
-#| warning: false
-```
-
-\newpage
-
 # References

### 2024-11-01 paper/paper.qmd
Updated Abstract

@@
 date-format: long
-abstract: "The 2024 U.S.
-Presidential Election is one of the most anticipated political events, with significant implications for the future direction of the country.
-This paper presents a poll-based forecasting model that leverages polling data to predict voter support for the major candidates, Kamala Harris and Donald Trump.
-Using multiple linear regression, the model incorporates factors such as poll quality, transparency, sample size, geographic variation, and temporal trends to estimate each candidate's share of support.
-The findings highlight key predictors that influence electoral outcomes, offering insights into voter behavior and polling dynamics.
-The approach aims to provide a robust forecast of the election, accounting for methodological variability across polls."
+abstract: "This paper presents a forecasting model for the 2024 U.S.
+Presidential Election, using polling data to analyze voter support for Kamala Harris and Donald Trump.
+Our approach combines a Baseline Model, which captures national polling trends, with a Primary Model focused on key swing states.
+Findings suggest a national advantage for Harris, with critical leads in swing states that could secure her a projected 292 electoral votes.
+This dual-model approach underscores the influence of state-level dynamics on national outcomes, offering insights into how polling data can more accurately capture voter behavior across a diverse electoral landscape."
 format: pdf

### 2024-11-02 scripts/01-test_simulate_data.R
Created test_simulated_data and updated readme.
Reordered scripts and followed checks in readme.

@@ -1,4 +1,4 @@
-# Purpose: Tests the analysis data. 
+# Purpose: Tests the simulated data.
 # Author: Xinxiang Gao
 # Date: 31 October 2024
 # Contact: xinxiang.gao@mail.utoronto.ca
@@ -10,8 +10,7 @@ library(tidyverse)
 library(validate)
 
 # Load data
-# data <- read_csv("data/00-simulated_data/simulated_polls.csv")
-data <- read_csv("data/02-analysis_data/cleaned_president_polls.csv")
+data <- read_csv("data/00-simulated_data/simulated_polls.csv")
 
 # Define validation rules
 rules <- validator(
@@ -44,5 +43,3 @@ validation_results <- confront(data, rules)
 
 # Summary of validation
 summary(validation_results)
-
-

### 2024-11-02 paper/paper.qmd
Clarified methodology

@@
 
+```{r}
+data_swing <- data %>% filter(state %in% c("Nevada", "Arizona", "Wisconsin", "Michigan", "Pennsylvania", "North Carolina", "Georgia"))
+
+```
+
 To understand the general trends in the data, we conducted exploratory data analysis using summary statistics and visualizations.
@@
 Presidential Election using polling data for the candidates Kamala Harris and Donald Trump.
-The models, a Baseline Model (Winner-Take-All National Model) and a Primary Model (Swing State-Based Model), provide two distinct but complementary approaches to assessing candidate support.
+The models, a Baseline Model (Winner-Take-All National Model) and a Swing State-Based Model, provide two distinct but complementary approaches to assessing candidate support.
 The Baseline Model aggregates national polling data to project which candidate is likely to win based on national polling trends and assigns all electoral votes to the candidate with the higher projected national percentage on election day.
@@
 
-On the other hand, the Primary Model is designed to provide a more granular projection by focusing on polling data at the state level, particularly for key swing states.
+On the other hand, the Swing State-Based Model is designed to provide a more granular projection by focusing on polling data at the state level, particularly for key swing states.
 This model assumes that the winner in each swing state can be determined by state-specific polling trends, and it projects support for each candidate within these competitive regions.
@@
     model <- lm(pct ~ days_towards_election, data = candidate_data)
-    tidy_model <- tidy(model)  # Get a tidy summary of the model
+    model_summary <- summary(model)
+    tidy_model <- data.frame(
+      term = rownames(model_summary$coefficients),
+      estimate = round(model_summary$coefficients[, "Estimate"], 3),
+      std.error = round(model_summary$coefficients[, "Std. Error"], 3),
+      t.stat = round(model_summary$coefficients[, "t value"], 3),
+      p.value = round(model_summary$coefficients[, "Pr(>|t|)"], 3)
+    )
     tidy_model$candidate <- candidate  # Add candidate to the output
@@
 # Combine results for all candidates into a single data frame
-final_results_baseline <- bind_rows(results, .id = "candidate")
+final_results_baseline <- bind_rows(results)
 
 # View the final results
-kable(final_results_baseline)
+kable(final_results_baseline, row.names = FALSE)
 
@@
 The baseline model aggregates national polling data to predict a winner, with all electoral votes awarded to the candidate with the higher national polling percentage.
-
-1. **National Polling Projections**  
    Let:
@@
 
-2. **Election Day Prediction**  
-   On election day:
-   $$
-   P_H(0) = \alpha_H, \quad P_T(0) = \alpha_T
-   $$
+Then, our aim is the intercept, $P_H(0) = \alpha_H, \quad P_T(0) = \alpha_T$.
 
-3. **Winner-Take-All Outcome**  
-   The candidate with the higher predicted national percentage wins all electoral votes:
-   $$
-   W = 
-   \begin{cases} 
-   \text{Harris wins (all electoral votes)} & \text{if } \alpha_H > \alpha_T \\
-   \text{Trump wins (all electoral votes)} & \text{otherwise}
-   \end{cases}
-   $$
+We then draw the prediction result as follows: Harris wins (all electoral votes) if $\alpha_H > \alpha_T$, and Trump wins (all electoral votes) otherwise.
 
@@
     model <- lm(pct ~ days_towards_election, data = candidate_data)
-    tidy_model <- tidy(model)  # Get a tidy summary of the model
+    model_summary <- summary(model)
+    tidy_model <- data.frame(
+      term = rownames(model_summary$coefficients),
+      estimate = round(model_summary$coefficients[, "Estimate"], 3),
+      std.error = round(model_summary$coefficients[, "Std. Error"], 3),
+      t.stat = round(model_summary$coefficients[, "t value"], 3),
+      p.value = round(model_summary$coefficients[, "Pr(>|t|)"], 3)
+    )
     tidy_model$state <- unique(candidate_data$state)  # Add state to the output
@@
 # View the final results
-kable(final_results)
+kable(final_results, row.names = FALSE)
 
@@
 
-## 2. Primary Model (Swing State-Based Model)
+## 2. Swing State-Based Model
 This model forecasts electoral outcomes by projecting state-level polling results for each candidate, combining swing state outcomes with votes from solid states.
@@
 
-2. **Predicting Swing State Winners**  
-   On election day ($t = 0$), each candidate’s predicted support in state $s$is:
-   $$
-   P_{H_s}(0) = \alpha_{H_s}, \quad P_{T_s}(0) = \alpha_{T_s}
-   $$
+Then, we obtain the predicted polling percentage for Harris in state $s:P_{H_s}(0) = \alpha_{H_s},$ and that for Trump in state $s: \quad P_{T_s}(0) = \alpha_{T_s}$.
+The candidate mentioned above wins in state s if their predicted polling percentage is higher than the other candidate.
 
-   Define $W_s$ as an indicator for the swing state winner:
-   $$
-   W_s = 
-   \begin{cases} 
-   1 & \text{if } \alpha_{H_s} > \alpha_{T_s} \\
-   0 & \text{otherwise}
-   \end{cases}
-   $$
-
-3. **Electoral Vote Aggregation**  
-   Let $EV_H$ and $EV_T$ represent total electoral votes for Harris and Trump:
-   $$
-   EV_H = \sum_{s \in S} W_s \cdot EV_s + \sum_{s \in S_H} EV_s
-   $$
-   $$
-   EV_T = \sum_{s \in S} (1 - W_s) \cdot EV_s + \sum_{s \in S_T} EV_s
-   $$
-
-4. **Final Election Outcome**  
-   The candidate surpassing 270 electoral votes wins:
-   $$
-   W = 
-   \begin{cases} 
-   \text{Harris wins} & \text{if } EV_H \geq 270 \\
-   \text{Trump wins} & \text{if } EV_T \geq 270 
-   \end{cases}
-   $$
+2. **Electoral Vote Aggregation**  
+  Based on the electoral vote policy in swing states, the winner of the state obtains all the vote from that state.
+Obtaining the predicted winner of the swing states, we calculate their total electoral votes as two components: their votes from the solid states as mentioned by Electoral Ventures LLC (2024), and the votes from the swing states that would advocate the candidate based on the predictions.
+  Eventually, the candidate surpassing 270 electoral votes in our prediction wins.
 
@@
 intercept_wide <- intercept_wide %>%
-  mutate(difference = `Kamala Harris` - `Donald Trump`)
+  mutate(Difference = `Kamala Harris` - `Donald Trump`) %>% 
+  rename(State = state)
+
+intercept_wide$`Votes` <- c(6, 11, 10, 15, 19, 16, 16)
 
@@
   Candidate = c("Harris", "Trump"),
-  Solid_State_Votes = c(226, 219)
+  Solid_State = c(226, 219)
 )
-intercept_wide$electoral_votes <- c(6, 11, 10, 15, 19, 16, 16)
 
@@
   mutate(Predicted_Swing_State_Votes = ifelse(is.na(Predicted_Swing_State_Votes), 0, Predicted_Swing_State_Votes),
-         Total_Predicted_Votes = Solid_State_Votes + Predicted_Swing_State_Votes)
+         total = Solid_State + Predicted_Swing_State_Votes) %>% 
+  rename(`Solid State` = Solid_State, `Predicted Swing State` = Predicted_Swing_State_Votes, `Total Predicted Votes` = total)
 
+# View the results
 kable(total_votes, caption = "Predicted Electoral Votes for Each Candidate")
+
 ```
@@
 # References
+
+Electoral Ventures LLC, (2024). 270toWin - 2024 Presidential Election Interactive Map. 270toWin.com. https://www.270towin.com/

### 2024-11-02 paper/paper.qmd
Updated scripts and plots

@@
 data <- read.csv("../data/02-analysis_data/cleaned_president_polls.csv")
-skim(data)
 ```
@@
 
+### Multicollinearity Considerations
+```{r pairplot}
+#| warning: false
+#| message: false
+#| echo: false
+numeric_data <- data %>% 
+  select(where(is.numeric)) %>% 
+  select(numeric_grade, pollscore, transparency_score) %>% 
+  filter(complete.cases(.))
+# Create a pair plot
+ggpairs(numeric_data) +
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1, size = 8, margin = margin(t = 10)),
+    axis.text.y = element_text(size = 8, margin = margin(r = 10)),
+    strip.text = element_text(size = 6)  # Adjusts the size of variable name tags
+  )
+```
+While selecting the predictors for the model, multicollinearity was a key concern.
+Multicollinearity occurs when two or more predictors are highly correlated, which can inflate the variance of the coefficient estimates and make the model less reliable.
+In our pair plot analysis, we observed a high correlation between "numeric_grade" and "pollscore," suggesting that they measure similar aspects of polling quality.
+
 ```{r}
@@
 
+data_swing %>%
+  group_by(state) %>% 
+  summarise(count = n(),
+            `mean pollscore` = round(mean(pollscore, na.rm = TRUE), 3),
+            `mean numeric grade` = round(mean(numeric_grade, na.rm = TRUE), 3),
+            `mean transparency score` = round(mean(transparency_score, na.rm = TRUE), 3),
+            `mean sample size` = round(mean(sample_size, na.rm = TRUE))) %>% 
+  kable()
+```
+
+```{r}
+data %>% 
+  filter(sample_size < 10000) %>% 
+  ggplot(aes(x = sample_size)) +
+  geom_histogram(bins = 50, fill = "steelblue", color = "black")
+```
+
+```{r}
+data %>% 
+  filter(sample_size >= 10000) %>% 
+  arrange(sample_size)
 ```
@@
 # Combine results for all candidates into a single data frame
-final_results <- bind_rows(results, .id = "candidate")
+final_results <- bind_rows(results, .id = "candidate") %>% 
+  arrange(state, candidate)
 
@@
 This model illustrates overall voter sentiment trends, capturing how each candidate's support changes as election day approaches and indicating a national-level lean toward Harris if these trends hold.
+
 ```{r}

### 2024-11-02 scripts/02-clean_data.R

@@ -31,7 +31,10 @@ data$days_towards_election <- data_a$days_towards_election
 selected_columns <- c(
   "poll_id",
   "transparency_score", 
+  "numeric_grade",
+  "pollscore",
   "state", 
+  "sample_size",
   "end_date", 
   "party", 
   "candidate_name", 
@@ -40,8 +43,6 @@ selected_columns <- c(
 )
 data <- data %>%
   select(all_of(selected_columns)) 
-
-
 
 
 #### Save data ####

### 2024-11-02 scripts/06-model_data.R

@@ -1,45 +1,0 @@
-#### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
-
-#### Workspace setup ####
-library(tidyverse)
-library(rstanarm)
-
-#### Read data ####
-#analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
-
-data <- read_csv("data/02-analysis_data/cleaned_president_polls.csv")
-
-# Nevada: 6
-# Arizona: 11
-# Wisconsin: 10
-# Michegan: 15
-# Penn: 19
-# North Carolina: 16
-# Gerogia: 16
-data_nevada <- data %>% filter(state == "Nevada") 
-data_arizona <- data %>% filter(state == "Arizona") 
-data_wisconsin <- data %>% filter(state == "Wisconsin") 
-data_michigan <- data %>% filter(state == "Michigan") 
-data_penn <- data %>% filter(state == "Pennsylvania") 
-data_north_carolina <- data %>% filter(state == "North Carolina") 
-data_georgia <- data %>% filter(state == "Georgia") 
-
-candidate_names <- c("Kamala Harris", "Donald Trump")
-
-
-
-#### Save model ####
-saveRDS(
-  model,
-  file = "models/first_model.rds"
-)
-
-

### 2024-11-02 paper/paper.qmd
Fixed bugs and rendered

@@
 swing_state_results <- intercept_wide %>%
-  mutate(Winner = ifelse(difference > 0, "Harris", "Trump")) %>%
+  mutate(Winner = ifelse(Difference > 0, "Harris", "Trump")) %>%
   group_by(Winner) %>%
-  summarize(Predicted_Swing_State_Votes = sum(electoral_votes))
+  summarize(Predicted_Swing_State_Votes = sum(Votes))
 

### 2024-11-02 paper/paper.qmd
Updated Appendix

@@
 
-# Pollster Methodology Overview and Evaluation: YouGov
+# Methodology Analysis of The Economist/YouGov Poll (October 6–7, 2024)
 
-YouGov is a widely recognized survey and market research company that operates one of the largest global online panels, providing insights on public opinion across various topics, from politics to consumer behavior.
-As an online survey platform, YouGov employs a nonprobability sampling methodology, relying on a self-recruited panel and extensive demographic data to approximate representativeness.
-This methodology offers several advantages, including cost-efficiency, rapid data collection, and the ability to adapt to specific research needs.
-However, like all methodologies, it comes with its own set of trade-offs, particularly in terms of representativeness and potential selection biases.
+## Overview
 
-This appendix takes a closer look at YouGov’s sampling approach, panel recruitment methods, handling of non-response, and overall survey methodology.
-It also includes a reflection on the user experience, examining how elements like the onboarding process and incentive structure can shape participant engagement and data quality.
-By analyzing the strengths and weaknesses of YouGov’s approach, this paper aims to provide a comprehensive understanding of how YouGov balances methodological rigor with the practical realities of online polling, highlighting both the reliability and the limitations of its data.
+The Economist/YouGov poll, conducted from October 6 to October 7, 2024, involved 1,604 U.S.
+adult citizens to gather insights into public opinion on the 2024 presidential election and related political issues.
+YouGov’s approach, known for its consistency in methodology, relies on an online sampling model that utilizes an opt-in panel of respondents.
+This section provides a comprehensive breakdown of the methodological elements that define this survey: the target population, sampling strategy, handling of non-response, and questionnaire design, while also highlighting its strengths and limitations (@citeYouGovReport).
 
@@
 
-For YouGov surveys, the population often includes U.S.
-adults or specific subgroups, such as registered voters or other demographic or political segments.
-The frame from which YouGov draws its samples is its proprietary online panel, consisting of self-recruited individuals who provide extensive demographic information upon joining.
-This frame is nonprobabilistic and is designed to capture a wide demographic, with adjustments to enhance representativeness through post-survey weighting (YouGov).
+In survey research, the target population is the group of people to whom the survey results are meant to generalize (@citeYouGovWebsite).
+For the Economist/YouGov poll, the target population includes all U.S.
+adult citizens, making it representative of the broader American public on political issues.
+This choice of target population is intended to capture a wide array of perspectives, from various demographics and political affiliations, to gauge national sentiment on the election (@citeYouGovReport).
 
-The sample is selected from this online panel based on survey requirements.
-For general surveys representing the U.S.
-adult population, YouGov applies demographic matching and stratified sampling to recruit individuals whose characteristics resemble the target population.
-For more targeted surveys, such as those involving younger adults or specific voter segments, YouGov filters panelists based on demographic and political characteristics, ensuring that the survey sample aligns with the study's focus (YouGov).
+The sampling frame, in contrast, represents a more specific group within the target population from which the sample is actually drawn.
+YouGov’s sampling frame consists of members of its U.S.-based online panel, who have agreed to participate in surveys.
+Panelists are recruited through various channels, including commercial opt-in lists, online advertisements tailored to attract people with diverse interests, and invitations extended to past respondents from prior research initiatives.
+Each panelist provides background demographic information upon joining, allowing YouGov to build a versatile sampling frame with significant demographic coverage, aligning with the characteristics of the U.S.
+adult population (@citeYouGovMethodology) (@citeYouGovReport).
 
-## Sample Recruitment
+The sample, or the subset of individuals selected from the sampling frame to participate in the survey, includes 1,604 respondents who meet specific demographic criteria to mirror the target population’s composition.
+This particular sample size offers a balance between reliability of data and efficiency of resources, as it’s large enough to capture statistically significant findings while remaining feasible for rapid deployment online (@citeYouGovReport).
 
-YouGov’s panelists are recruited through online advertisements, partnerships with various websites, and organic sign-ups.
-This open online recruitment allows any adult within the United States with internet access to join the panel, promoting inclusivity in terms of access and accessibility (YouGov).
-Once part of the panel, participants voluntarily complete surveys for points that can be exchanged for rewards, making monetary compensation a moderate incentive but not the sole motivator for participation.
-This approach is well-suited to engage a broad and diverse sample, although it does introduce limitations by excluding those without internet access.
+## Sample Recruitment and Sampling Approach
 
-Because the recruitment is continuous and participants often stay on the panel long-term, YouGov can maintain and monitor demographic balance, update panelist information over time, and reduce redundancy in questions for returning members.
-However, relying solely on online recruitment may introduce a bias toward individuals more inclined toward online engagement, who may not fully represent groups with lower internet usage, such as older adults or those from lower-income backgrounds (YouGov).
+Sampling can follow different designs, such as probability and nonprobability methods, each with unique implications.
+Probability sampling is the approach where each member of the target population has a known, non-zero chance of being selected, making the sample theoretically representative of the population.
+This method, which is often employed in high-stakes polling (e.g., election forecasting), is seen as the gold standard for ensuring unbiased, representative data (@citeYouGovWebsite).
 
-## Sampling Approach and Trade-offs
+However, YouGov uses a nonprobability sampling method, in which the panelists are drawn from an opt-in online panel rather than randomly from the entire U.S.
+adult population.
+Nonprobability sampling doesn’t guarantee that every individual has an equal chance of selection; instead, it focuses on constructing a sample that closely matches the population based on key demographic characteristics through weighting.
+YouGov’s approach enables it to conduct surveys quickly and cost-effectively while also allowing targeted sampling of specific groups of interest, which can be beneficial for identifying subpopulation insights or trends (@citeYouGovWebsite).
 
-YouGov employs a nonprobability sampling approach, meaning that not every individual in the population has an equal chance of selection.
-Within its panel, YouGov uses stratified sampling, drawing subsets of respondents based on demographic targets (e.g., age, race, gender, and region) to match the sample as closely as possible to the desired population structure.
+While nonprobability sampling offers these efficiencies, it introduces the risk of selection bias, as the individuals who join an opt-in panel may not fully reflect the population’s diversity in attitudes or behaviors.
+For example, those who choose to participate might have higher engagement in political matters than the general public.
+To mitigate these potential biases, YouGov weights the sample on various demographic variables to match national population benchmarks, making the findings more reflective of the broader U.S.
+adult population (@citeYouGovWebsite).
 
-### Trade-offs of the Nonprobability Approach
-- **Strengths**: Nonprobability sampling allows YouGov to gather data rapidly and cost-effectively.
-By using stratified sampling and post-survey weighting, the company aims to approximate the representativeness of probability-based samples while maintaining flexibility in addressing specific research goals and client needs (YouGov).
-- **Limitations**: Because nonprobability samples lack random selection, they do not guarantee true representativeness, which can introduce unknown biases.
-YouGov addresses this partially by applying demographic weights, but nonprobability sampling’s inherent limitations mean results should be interpreted as estimates rather than fully precise reflections of the target population (Huffington Post).
+## Non-Response Handling and Weighting
 
-## Handling Non-Response
+Non-response bias is a concern in all survey methods and arises when certain types of individuals in the target population are less likely to participate, potentially skewing the results (@citeYouGovWebsite) In the Economist/YouGov poll, respondents who are unwilling or unable to participate may differ in meaningful ways from those who do participate, and these differences could influence survey outcomes if left unaddressed.
+For instance, if younger adults are less likely to respond, the survey could over-represent older adults’ opinions, leading to results that don’t accurately reflect the broader population (@citeYouGovMethodology).
 
-Non-response is a common issue in survey research, particularly with online surveys where participants may decline to participate, partially complete surveys, or provide inconsistent answers.
-YouGov tackles non-response bias through quality control processes that exclude unreliable responses.
-These controls involve detecting respondents who complete surveys too quickly, answer inconsistently, or fail attention checks (YouGov).
+To address non-response, YouGov employs weighting to adjust the sample composition.
+Weighting assigns different statistical weights to respondents based on their demographic characteristics — such as age, gender, race, income, and voting history — to ensure these characteristics align with those of the target population as measured by reliable sources like the U.S.
+Census.
+This process gives less frequently represented groups a higher weight in the analysis and more commonly represented groups a lower weight, balancing the sample to mitigate non-response effects.
+Weighting can’t entirely eliminate the effects of non-response but substantially reduces its potential bias, making the survey findings more credible (@citeYouGovReport).
 
-In addition, YouGov adjusts for non-response by weighting the final sample to reflect the target population's demographic characteristics more accurately.
-This adjustment helps address imbalances resulting from non-response, enhancing the data’s generalizability.
-However, non-response bias remains a concern, especially as weighting cannot entirely account for individuals not present in the sample or for differences in survey engagement across demographics (YouGov).
+## Questionnaire Design and Quality Control
 
-## Strengths and Weaknesses of YouGov’s Methodology
+YouGov prioritizes clarity, neutrality, and accessibility in questionnaire design.
+Clear wording helps prevent misunderstandings, while neutral language avoids leading respondents to particular answers.
+The survey also incorporates randomization of question and response option orders, a strategy that reduces the likelihood of order bias, where responses may be influenced by the sequence in which options are presented.
+YouGov’s commitment to neutrality and randomization adds to the reliability and validity of the responses, making the findings more trustworthy @citeYouGovMethodology.
 
-### Strengths
-- **Efficient Data Collection**: YouGov’s nonprobability online sampling allows for efficient, cost-effective data collection, enabling timely survey responses that can address rapidly changing social and political topics.
-- **Targeted Panel Management**: YouGov’s proprietary panel enables consistent, direct contact with respondents, allowing for long-term engagement and improved tracking of demographic and opinion changes without needing repetitive data entry.
-- **Rigorous Quality Controls**: Extensive quality checks, including IP verification, email authentication, and response validity checks, help YouGov maintain high data integrity.
-Respondents who fail quality checks are excluded, helping to reduce noise from unreliable data.
-- **Adjustments for Representativeness**: While nonprobability sampling has limitations, YouGov partially mitigates these by applying sophisticated weighting based on benchmarks from sources like the U.S.
-Census.
-This enhances the sample’s demographic alignment with the general population (YouGov).
+Quality control measures further reinforce the survey’s integrity.
+YouGov’s approach includes verifying panelists’ identity and monitoring their responses for consistency.
+For instance, individuals providing contradictory answers or completing the survey unusually quickly are flagged, with their data excluded from the final analysis.
+This process ensures that only high-quality responses contribute to the survey’s conclusions @citeYouGovWebsite.
 
-### Weaknesses
-- **Nonprobability Sampling Limitations**: The lack of true random sampling introduces potential bias, as certain population segments may be underrepresented.
-For example, people without internet access or those less inclined toward online engagement are systematically excluded, which could affect representativeness.
-- **Potential Selection Bias**: Although incentives are modest, they may still attract individuals who are already more engaged or motivated to participate in surveys, which could influence results.
-The weighting procedures help but may not fully eliminate biases if certain groups are consistently underrepresented.
-- **Limitations of Online-Only Surveys**: Although internet penetration in the U.S.
-is high, reliance on online-only surveys may still leave out individuals less comfortable with or able to access online technology, skewing results slightly.
-- **Questionnaire Design Constraints**: While YouGov’s questionnaire design is generally sound, with randomized question orders and multimedia inclusion for clarity, online surveys can limit response depth compared to in-person or phone surveys.
-Responses are constrained by pre-set answer options, potentially oversimplifying complex views and reducing respondent nuance (Huffington Post).
+While the survey’s straightforward question format enhances accessibility, it can limit depth in exploring complex topics, as respondents may not have the opportunity to fully express nuanced views.
+For example, questions about candidate preference capture top-line support but may lack the depth to reveal the underlying motivations or concerns driving these preferences.
+
+## Strengths and Limitations of YouGov’s Methodology
+
+YouGov’s methodology provides a flexible and efficient way to gather public opinion, allowing rapid data collection across a broad demographic range.
+The use of an opt-in panel enables YouGov to survey specific subgroups effectively and maintain control over respondent quality.
+By applying weighting to compensate for nonprobability sampling, YouGov achieves a sample composition that closely resembles the U.S.
+adult population, allowing generalizations about national opinion.
+
+However, the reliance on nonprobability sampling introduces certain limitations.
+Since the sample is drawn from an opt-in panel, there is an inherent risk of selection bias, which, despite efforts to control for it through weighting, may affect the representativeness of the findings.
+The use of online-only surveys also limits participation to individuals with internet access, although this exclusion is less impactful in the U.S., where internet penetration is high.
+
+In conclusion, YouGov’s methodology balances efficiency and accuracy well, leveraging demographic weighting and robust quality controls to produce credible insights.
+While limitations related to nonprobability sampling and selection bias exist, these are mitigated through strategic adjustments, making the poll a reliable source for gauging national opinions.
 
@@
 
-## Methodology
-This part of the appendix provides a detailed methodology and survey design to forecast the 2024 U.S.
-presidential election.
-Our survey focuses on swing states: Arizona, Georgia, Michigan, Nevada, North Carolina, Pennsylvania, and Wisconsin due to the results of other states being certain.
-The survey targets different age groups using tailored recruitment strategies.
-Below, we break down the methodology, budget, recruitment strategies, and survey design to ensure representative participation.
+## Overview
+This methodology presents an election forecasting plan with a budget of $100,000 focusing on swing states which are states where election outcomes are uncertain, making them crucial for forecasting the Electoral College result.
+Drawing on insights from YouGov and  Annual Review of Economics regarding survey methods, we chose an online format to improve accessibility and minimize selection bias, allowing respondents to participate at their convenience.
+This approach is especially suitable for students and working-age individuals, who may have limited availability during traditional hours.
+Mobile technology further enhances engagement, reaching populations that are otherwise challenging to access, such as seniors and mobile-first respondents.
+To maintain engagement and prevent drop-offs, we designed a concise survey with digital incentives to attract a broad participant base across income levels.
+By incorporating techniques from both institutions, our methodology is designed to be cost-effective and demographically balanced, producing reliable predictions for the 2024 U.S.
+Presidential Election.
 
-### Sampling Approach
-- Total Sample Size: 7,000 respondents (1,000 participants per state).
-- Target Population: Eligible voters from the following swing states: Arizona, Georgia, Michigan, Nevada, North Carolina, Pennsylvania, Wisconsin.
+## Sampling Approach
+This methodology uses a multi-mode sampling approach, integrating both probability and non-probability methods to achieve broad demographic reach and representativeness.
+This approach enables us to capture an inclusive snapshot of voter preferences in critical electoral regions.
 
-#### Sampling Breakdown by Age Group:
-- 18-24 years: 150 participants per state (total 1,050) – reached through university students.
-- 25-60 years: 700 participants across states (total 4,900) – reached via online ads and survey platforms.
-- 60+ years: 150 participants per state (total 1,050) – reached through phone calls.
+### Target Population
+The target population is eligible voters in the seven swing states: Arizona, Georgia, Michigan, Nevada, North Carolina, Pennsylvania, and Wisconsin.
+By focusing on these states, the survey aims to forecast potential outcomes in critical areas for the Electoral College.
 
-- Stratified Random Sampling:
-  - Stratify by age, gender, race/ethnicity, education, income, and region.
-  - Ensure proportional representation based on **U.S. Census data** to avoid bias.
+### Sampling Frame and Sample Size
+The sampling frame combines both verified voter lists (probability-based) and opt-in online panels (non-probability) to access a comprehensive range of respondents.
+Our total sample size is 7,000 respondents (1,000 per state), which supports statistically reliable insights across age groups and geographic regions.
 
-- Weighting Strategy:
-  - Apply **post-stratification weighting** to adjust for any sampling imbalance, aligning with national demographics.
+### Sample Recruitment by Age Group
+- 18-24 years: Recruited through university partnerships, with a target of 150 respondents per state (1,050 total).
+- 25-60 years: Recruited via online ads on platforms like Facebook and Prolific, targeting 700 respondents per state (4,900 total).
+- 60+ years: Reached through live phone calls, with 150 respondents per state (1,050 total).
 
-### Recruitment Plan
+### Sampling Methods
+Probability Sampling (Phone Interviews): For the 60+ age group, live phone interviews and Interactive Voice Response (IVR) calls are employed.
+Using verified voter lists reduces bias and increases data accuracy for less digitally active participants.
+Non-Probability Sampling (Online Surveys): For participants aged 18-60, online surveys target mobile-first and younger voters through social media and survey platforms.
+Although not all respondents have equal selection probability, quota sampling and post-stratification weighting enhance representativeness.
 
-#### 18-24 Years (University Students):
-- University Collaboration: Partner with academic institutions in each swing state to send survey invitations via email on behalf of the project.
-- Rationale: Universities provide direct access to students, improving recruitment efficiency and response rates.
-- Incentive: Each respondent receives a $10 e-gift card for a Walmart or Costco purchase.
+### Stratified Sampling and Weighting
+Stratified Sampling: The sample is stratified by demographic characteristics such as age, gender, race/ethnicity, education, and income, to improve representativeness.
+Post-Stratification Weighting: To correct for any sample imbalances, post-stratification weighting adjusts the sample to match demographic proportions from U.S.
+Census data, ensuring balanced representation across demographic categories.
 
-#### 25-60 Years (General Population):
-- Online Ads and Survey Platforms: Use Facebook, Instagram, and platforms like Prolific to recruit participants from swing states.
-- Budget Allocation: Allocate $10,000 for online ads to reach residents aged 25-60.
-- Incentive: Participants receive e-gift cards upon survey completion.
+## Recruitment Strategy
+Using verified voter lists and opt-in online panels as the sampling frame, this survey focuses on likely voters in the 2024 election.
+Likely voters are identified based on past voting behavior and registration status.
+To align with demographic targets, quota sampling is employed.
+Quota sampling allows us to proportionally represent demographic groups by age, gender, race, and education, ensuring the sample reflects the U.S.
+electorate's profile.
+Our primary focus is on controlling age distribution.
+As each age group reaches its target sample size, we close the survey for that group to prevent over-representation.
+This method ensures that all age demographics are adequately represented without skewing results due to excess responses from any particular age group.
+Incentives: To encourage participation, especially for online surveys targeting younger and working-age demographics, we offer a $10 digital gift card to each respondent upon survey completion.
+This incentive helps attract a more diverse group, increasing the likelihood of representative participation across income levels and ensuring a higher response rate.
 
-#### 60+ Years (Senior Citizens):
-- Phone Surveys: Conduct live calls to reach seniors, considering that older people are not comfortable using electronic devices.
-Phone numbers will be sourced from voter registration databases (where legally accessible) or senior community networks.
-- Incentive: Seniors can choose a physical Walmart or Costco gift card, which will be sent by mail.
+## Data Validation
+Given the hybrid data collection format, we use several validation techniques to maintain data quality:
+- Duplicate detection (based on IP addresses and phone numbers) ensures unique responses.
+- Attention checks help identify respondents who may not be fully engaged.
+- Conflict detection: Responses showing contradictions (e.g., conflicting demographic details or inconsistencies in voting behavior) are flagged.
+If respondents provide conflicting answers, their data is excluded, as this may indicate they completed the survey solely for incentives without thoughtful engagement.
+Both duplicate and inattentive responses introduce bias and are therefore removed from the data set. This filtering process improves data accuracy and reliability.
+To further align the sample with national demographics, post-stratification weighting is applied.
+Weights are calculated based on key variables such as race, gender, and education, following Census benchmarks.
+This weighting corrects for any under- or over-represented groups, resulting in data that is more reflective of the broader electorate.
 
-- Recruitment Channels:
-  - Complement with **social media ads** on Facebook, Instagram, and LinkedIn to reach underrepresented groups.
-  - **Incentives**: Offer **$10 gift cards** to increase participation and engagement.
+## Trade-Offs
+Data Diversity vs.
+Recruitment Control: Although quota sampling on age helps ensure demographic diversity, strict quotas for every characteristic (such as race and income) are difficult to impose.
+This may lead to over- or under-representation of certain groups.
+Solution: Post-stratification weighting is used to adjust the sample based on Census proportions, improving demographic balance.
+Accurate Senior Outreach vs.
+Higher Costs: Phone interviews are essential to reach senior citizens but come at a higher cost.
+Additionally, some seniors may remain unreachable, potentially skewing representation.
+Solution: Allocate phone interview resources to maximize outreach while acknowledging potential non-response among unreachable seniors.
+Incentives vs.
+Economic Bias: Offering $10 digital incentives may disproportionately attract lower-income individuals, possibly skewing the sample toward lower socioeconomic backgrounds.
+Solution: Income-based weighting in post-stratification helps correct for any economic biases that might affect the sample’s representativeness.
 
-### Trade-off
+## Conclusion
+By integrating YouGov’s multi-modal sampling with the Economist’s robust weighting approach, this methodology effectively captures a broad cross-section of voter demographics.
+The use of both probability-based and non-probability-based sampling methods, along with rigorous data validation, ensures a reliable forecast for the 2024 U.S.
+Presidential Election.
 
-#### Data Representativeness vs. Control over Data Collection
-- Issue: Although age quotas ensure participation from different age groups (18-24, 25-60, 60+), it is not feasible to set strict limits for race and income.
-Without perfectly matched samples for race and income, bias may arise in the survey results.
+## Survey Link
+[https://forms.gle/2MGYeZavDsCNuWZ1A](https://forms.gle/2MGYeZavDsCNuWZ1A)
 
-- Solution: 
-  - Weighting Strategy: Calculate population proportions for race and income within each state using Census data. Assign weights to groups based on their representation to mitigate bias.
-
-#### Efficient Recruitment vs. Potential Selection Bias
-- Issue: Limiting the 18-24 age group to university students may introduce selection bias.
-University students often differ from their non-student peers in socioeconomic background and possibly political perspectives.
-- Impact: This selection bias may affect the generalizability of findings, as university students’ perspectives might differ from all young adults.
-
-#### Effective Senior Outreach vs. Higher Costs and Response Bias
-- Issue: Using live phone operators to reach seniors increases costs, and some seniors may remain unreachable by phone.
-- Impact: Higher costs may reduce resources for other age groups. Response bias may arise if unreachable seniors have different views, affecting the survey's representativeness.
-
-#### Incentivizing Participation vs. Economic Bias in Sample
-- Issue: Offering $10 gift cards as an incentive could attract participants more likely to need the incentive, potentially introducing economic bias.
-- Impact: Overrepresentation of lower-income participants could skew results, affecting insights if income level correlates with political perspectives.
-
-### Survey Implementation and Design
-In designing this survey, I referenced insights from the article on survey methods from @AnnualReviewofEconomics, particularly on the advantages of online surveys over in-person, phone, or mail surveys.
-The article highlighted that online surveys provide flexibility, allowing respondents to complete them at their convenience, which minimizes selection bias related to work schedules or availability.
-This flexibility is especially beneficial for students and working-age individuals, who may find it challenging to respond during traditional hours.
-The article also emphasized how mobile technology can increase participation by reaching populations that are otherwise hard to engage, such as younger respondents, frequent movers, or those in remote areas.
-In line with these insights, I designed this survey with an online format for younger and working-age participants, maximizing accessibility and reducing drop-out rates.
-Additionally, I applied the article’s suggestion of keeping surveys concise to prevent fatigue and disengagement, which helps maintain completion rates and improve data quality.
-The use of digital incentives, as noted in the article, also broadens the appeal and ensures we reach a diverse participant base across income levels, providing flexibility in rewards to cater to different motivations.
-This approach helped shape a balanced methodology that optimizes participation across demographic groups and aligns with best practices in survey design.
-
-- Survey Platform: Google Forms  
-  - **Link**: [https://forms.gle/2MGYeZavDsCNuWZ1A](https://forms.gle/2MGYeZavDsCNuWZ1A)
-  - Accessible to respondents via **email, social media, and direct recruitment channels**.
-
-- Survey Structure:
-  1. Demographics Section: Age, gender, race/ethnicity, income, education, and state of residence.
-  2. Voting Preferences Section: Candidate choice, likelihood of voting, and party affiliation.
-  3. Key Issues Section: Identify priority issues (e.g., economy, healthcare, immigration).
-  4. Thank You Message:  
-     - *“Thank you for completing the survey! Your input is greatly appreciated and will help provide insights into the upcoming 2024 election.”*
-
-### Data Validation
-
-- Techniques for Data Quality:
-  1. Screening Questions: Confirm eligibility (e.g., 18+ years old, registered voter status).
-  2. Attention Checks: Include a question like *“Please select ‘Agree’ for this item”* to verify respondents are attentive.
-  3. IP Geolocation: Validate state residency based on reported location.
-  4. Duplicate Detection: Identify and remove duplicate responses.
-
-### Poll Aggregation and Reporting
-
-- Poll Aggregation:  
-  - Use **weighted averages** to account for differences in sample size and demographics.
-
-- Margin of Error**:  
-  - National Margin of Error: ±1% at the 95% confidence level.  
-  - State-Level Margins: ±5-10% depending on the sample size for each state.
-
-### Budget Allocation
-
-| **Expense**                                        | **Estimated Cost**  |
-|---------------------------------------------------|---------------------|
-| Participant Incentives                             | $70,000            |
-| Online Ads and Panel Provider Fees                 | $10,000            |
-| Phone Survey Salaries                              | $8,000             |
-| Google Forms (Platform)                            | Free               |
-| Data Validation & Analysis                         | $10,000            |
-| Miscellaneous Expenses                             | $2,000             |
-| **Total**                                          | **$100,000**       |
-
-## Survey Questions
-
+## Copy of Survey
 Below is the full content of the survey to be implemented using Google Forms:
@@
 
-## Google Forms Link
-[https://forms.gle/2MGYeZavDsCNuWZ1A](https://forms.gle/2MGYeZavDsCNuWZ1A)
-
 # References

### 2024-11-03 paper/paper.qmd
Smoothed modeling procedure introduction.
Accordingly added references.

@@
 
-## 1. Baseline Model (Winner-Take-All National Model)
-The baseline model aggregates national polling data to predict a winner, with all electoral votes awarded to the candidate with the higher national polling percentage.
-   Let:
-   - $P_H(t)$: Harris’s national polling percentage at $t$ days towards the election.
-   - $P_T(t)$: Trump’s national polling percentage at $t$ days towards the election.
+### Baseline Model (Winner-Take-All National Model)  
+In our baseline model, we predict the election winner by using national polling data and assigning all electoral votes to the candidate with the higher projected percentage on election day.
+This "winner-take-all" approach assumes that the candidate leading in national polling would theoretically secure all electoral votes.
 
-   We model each candidate’s polling as:
+To build this model, we define each candidate’s polling trend over time using simple linear regression:
+
+- Let $P_H(t)$ represent Kamala Harris’s national polling percentage at $t$ days before the election, and $P_T(t)$ represent Donald Trump’s percentage at the same time.
+
+We express each candidate's polling percentage as a linear function of time:
+
 $$
@@
 $$
+
 $$
@@
 
-   where $\alpha_H$ and $\alpha_T$ are the intercepts (predicted percentages on election day, $t = 0$), and $\beta_H$ and $\beta_T$ are the slopes.
+where:
+- $\alpha_H$ and $\alpha_T$ are the intercepts, representing Harris’s and Trump’s predicted polling percentages on election day (when $t = 0$).
+- $\beta_H$ and $\beta_T$ are the slopes, capturing the rate of change in each candidate’s polling percentage as election day approaches.
 
-Then, our aim is the intercept, $P_H(0) = \alpha_H, \quad P_T(0) = \alpha_T$.
+Our primary interest is in estimating these intercepts, $\alpha_H$ and $\alpha_T$, since they give the predicted polling percentages for each candidate on election day.
+To predict the winner, we compare these intercepts:
 
-We then draw the prediction result as follows: Harris wins (all electoral votes) if $\alpha_H > \alpha_T$, and Trump wins (all electoral votes) otherwise.
+- If $\alpha_H > \alpha_T$, we predict that Kamala Harris wins the election and receives all electoral votes.
+- Conversely, if $\alpha_T > \alpha_H$, Donald Trump is predicted to win all electoral votes.
+
+This model simplifies the electoral system by assuming that the national polling leader would win the overall election, without accounting for individual state results.
 
@@
 
-## 2. Swing State-Based Model
-This model forecasts electoral outcomes by projecting state-level polling results for each candidate, combining swing state outcomes with votes from solid states.
+### 2. Swing State-Based Model  
+This model forecasts electoral outcomes by projecting each candidate’s polling results in individual swing states, then combining those results with electoral votes from states that are already solidly in favor of one candidate or the other.
 
 1. **Swing State Polling Projections**  
-   For each swing state $s \in S$, let:
-   - $P_{H_s}(t)$: Harris’s polling percentage in state $s$ at $t$ days before the election.
-   - $P_{T_s}(t)$: Trump’s polling percentage in state $s$ at $t$ days before the election.
+   To predict each candidate’s chances in swing states, we model their polling trends over time for each swing state $s \in S$. Let:
 
-   We model each swing state polling as:
+   - $P_{H_s}(t)$ be Kamala Harris’s polling percentage in state $s$ at $t$ days before the election.
+   - $P_{T_s}(t)$ be Donald Trump’s polling percentage in state $s$ at $t$ days before the election.
+
+   We express each candidate's polling percentage in each swing state as a linear function of time:
+
    $$
@@
    $$
+
    $$
@@
 
-   where $\alpha_{H_s}$ and $\alpha_{T_s}$ are intercepts (predicted percentages at $t = 0$) and $\beta_{H_s}$, $\beta_{T_s}$ are slopes.
+   where:
+   - $\alpha_{H_s}$ and $\alpha_{T_s}$ represent the intercepts, or the predicted polling percentages for Harris and Trump on election day (when $t = 0$).
+   - $\beta_{H_s}$ and $\beta_{T_s}$ are the slopes, indicating how each candidate’s polling percentage changes over time in state $s$.
 
-Then, we obtain the predicted polling percentage for Harris in state $s:P_{H_s}(0) = \alpha_{H_s},$ and that for Trump in state $s: \quad P_{T_s}(0) = \alpha_{T_s}$.
-The candidate mentioned above wins in state s if their predicted polling percentage is higher than the other candidate.
+   For each swing state, we focus on the predicted polling percentages on election day, $P_{H_s}(0) = \alpha_{H_s}$ for Harris and $P_{T_s}(0) = \alpha_{T_s}$ for Trump.
+We predict the winner of state $s$ based on which candidate has the higher projected percentage: if $\alpha_{H_s} > \alpha_{T_s}$, Harris wins the state; otherwise, Trump does.
 
 2. **Electoral Vote Aggregation**  
-  Based on the electoral vote policy in swing states, the winner of the state obtains all the vote from that state.
-Obtaining the predicted winner of the swing states, we calculate their total electoral votes as two components: their votes from the solid states as mentioned by Electoral Ventures LLC (2024), and the votes from the swing states that would advocate the candidate based on the predictions.
-  Eventually, the candidate surpassing 270 electoral votes in our prediction wins.
+   Once we have determined the predicted winner in each swing state, we calculate the total electoral votes for each candidate by combining:
+   - Electoral votes from solid states, as defined by @electoral_ventures_2024.
+   - Electoral votes from the swing states predicted to support each candidate.
+
+   In this approach, the candidate who surpasses the 270 electoral votes threshold is predicted to win the election.
+This model considers the variability of swing states, differentiating it from the winner-take-all national model by capturing the dynamics of individual state races.
 
@@
 # References
-
-Electoral Ventures LLC, (2024). 270toWin - 2024 Presidential Election Interactive Map. 270toWin.com. https://www.270towin.com/

### 2024-11-03 paper/paper.qmd
Updated Swing State Definition

@@
 date-format: long
-abstract: "This paper presents a forecasting model for the 2024 U.S.
-Presidential Election, using polling data to analyze voter support for Kamala Harris and Donald Trump.
-Our approach combines a Baseline Model, which captures national polling trends, with a Primary Model focused on key swing states.
-Findings suggest a national advantage for Harris, with critical leads in swing states that could secure her a projected 292 electoral votes.
-This dual-model approach underscores the influence of state-level dynamics on national outcomes, offering insights into how polling data can more accurately capture voter behavior across a diverse electoral landscape."
+abstract: "The upcoming U.S.
+Presidential Election on November 5th features a closely contested race between Vice President Kamala Harris and former President Donald Trump.
+This paper uses a poll-of-polls approach, combined with a dynamic linear regression model that updates daily with the latest data, to forecast the popular vote and outcomes in seven battleground states: Arizona, Georgia, Nevada, North Carolina, Michigan, Wisconsin, and Pennsylvania.
+Our analysis currently projects that Vice President Harris will win the popular vote, 48.19% to 46.01%, and secure the electoral college with 302 votes to Trump’s 236, by winning five of these seven swing states: Nevada, North Carolina, Michigan, Wisconsin, and Pennsylvania.
+By aggregating multiple polls rather than relying on a single poll, our model provides a more robust prediction, supporting the likelihood of a Harris victory."
 format: pdf
@@
 library(broom)
+library(styler)
 ```
@@
 
-The U.S.
-Presidential Election is a critical event shaping the country’s political direction, often influenced by a complex interplay of public opinion, socio-economic factors, and electoral mechanisms.
-In recent election cycles, the predictive accuracy of polling has been a topic of significant discussion, as polls not only gauge public sentiment but also influence campaign strategies, media narratives, and voter perceptions.
-However, challenges such as non-response bias, methodological inconsistencies, and a misalignment between the popular vote and electoral outcomes highlight the need for a robust forecasting model that captures both national and state-specific trends.
+The race between Vice President Kamala Harris and former President Donald Trump for the 2024 presidential election will conclude on November 5, 2024.
+President Joe Biden's decision on July 21, 2024, to withdraw from this year’s race led to Vice President Kamala Harris becoming the official Democratic nominee, supported by Biden and confirmed through a virtual roll call on August 2.
+Even before Biden’s withdrawal, polling organizations had gauged public opinion on a potential matchup between Harris and former President Donald Trump.
+Early polls showed Harris trailing Trump, but her support increased following Biden's exit, making the outcome of this election uncertain.This paper employs a poll-of-polls approach and a dynamic linear model to project each candidate's likely support on election day, both nationally and within swing states.
 
-This paper aims to address these challenges by developing a polling-based forecasting model for the 2024 U.S.
-Presidential Election, with a focus on the two main candidates, Kamala Harris and Donald Trump.
-Using a dual-model approach, we employ a **Baseline Model** to provide a broad national outlook and a **Primary Model** to examine state-level dynamics, especially in key swing states.
-The Baseline Model aggregates national polling data to predict which candidate would win a majority of popular support, while the Primary Model applies a more nuanced, state-level analysis aligned with the electoral college structure.
-This combination seeks to address the gap in existing models, which often fail to account for the specific impact of swing states on electoral outcomes, despite their pivotal role in determining the presidency.
+The primary estimand in this study is the predicted percentage of support each candidate will receive on election day, both nationally and within critical swing states.
+This percentage serves as the foundation for forecasting which candidate is likely to win the election, by capturing trends in public sentiment over time and projecting how these trends may manifest in the final vote count.
 
-Our analysis indicates that while Kamala Harris shows a lead in national polling, as reflected in the Baseline Model, the decisive factors lie within swing states such as Pennsylvania, Michigan, and Wisconsin, where the Primary Model highlights Harris’s slight advantages.
-The state-level predictions from the Primary Model suggest a possible electoral college win for Harris, projecting her to receive 292 electoral votes, above the 270-vote threshold needed to secure the presidency.
-This finding underscores the unique nature of U.S.
-elections, where winning the national popular vote does not necessarily translate to an electoral college victory.
-Our approach, by leveraging poll data with attention to poll quality, transparency, sample size, and geographic variation, seeks to provide a nuanced and accurate forecast that reflects both general sentiment and the regional intricacies of the election.
+We apply a dynamic linear regression model named “ Baseline Model” to provide a national overview and another dynamic linear regression model named “Primary Model” to assess state-level dynamics, especially in key battlegrounds.
+The Baseline Model aggregates national polling data to estimate popular vote share, while the Primary Model offers a state-specific analysis aligned with the electoral college structure.
+This approach addresses a gap in existing models that often overlook the unique impact of swing states on electoral outcomes.
+Our model projects that Vice President Harris will secure 48.19% of the popular vote, compared to 46.01% for Trump.
+However, as U.S.
+elections are decided by the electoral college rather than the popular vote, a candidate can win the presidency without a majority of popular support.
+There are seven swing states, Arizona, Georgia, Nevada, North Carolina, Michigan, Wisconsin, and Pennsylvania, holding a collective 93 electoral votes, are determining factors to the election’s outcome.
+Excluding swing states, Harris would receive 226 electoral votes, while Trump would receive 219.
+According to our Primary Model, Harris is expected to capture five of the seven swing states: Nevada, North Carolina, Michigan, Wisconsin, and Pennsylvania, yielding a total of 302 electoral votes and thus securing the presidency.
+Trump would win two swing states, Arizona and Georgia, ending with 236 electoral votes.
+Although Harris's lead in North Carolina is narrow (by just 0.036%), which may switch to voting for Trump in the future, but 19 votes in this state in the face of overwhelming vote margins won't have much of an impact on the outcome.
+
+Predicting the next U.S.
+president holds significant implications for the nation’s future and its role on the global stage.
+The elected leader will influence domestic policy on economic growth, healthcare, and social issues, while also shaping international relations, defense strategies, and trade policies.
+In an era of geopolitical uncertainty, including conflicts and economic fluctuations, understanding potential election outcomes can help inform the public, policymakers, and global leaders, providing a foundation for navigating the challenges ahead.
 
@@
 @sec-results presents the results, including national and state-level predictions, followed by @sec-disc, which explores the implications of these findings, discusses limitations, and suggests future research directions.
-An appendix provides additional methodological details and diagnostics.
-
-## Estimand
-
-The primary estimand in this study is the predicted percentage of support each candidate will receive on election day, both nationally and within critical swing states.
-This percentage serves as the foundation for forecasting which candidate is likely to win the election, by capturing trends in public sentiment over time and projecting how these trends may manifest in the final vote count.
+The three appendices provide a detailed exploration of key aspects relevant to the 2024 U.S.
+Presidential Election.
+@sec-swingsolid explains the distinction between swing states and solid states, highlighting their importance in election outcomes.
+@sec-meth and @sec-survey delve into the methodology and design of the Economist/YouGov poll and an election forecasting survey, outlining sampling methods, data validation processes, and strategic considerations for accurate and reliable polling results.
 
@@
 
-### Baseline Model (Winner-Take-All National Model)  
+## Baseline Model (Winner-Take-All National Model)  
 In our baseline model, we predict the election winner by using national polling data and assigning all electoral votes to the candidate with the higher projected percentage on election day.
@@
 
-### 2. Swing State-Based Model  
+## Swing State-Based Model  
 This model forecasts electoral outcomes by projecting each candidate’s polling results in individual swing states, then combining those results with electoral votes from states that are already solidly in favor of one candidate or the other.
@@
 \appendix
-# Appendix {-}
+# Swing State and Solid State{#sec-swingsolid}
+In the context of U.S.
+presidential elections, states are often classified as either "swing states" or "solid states" based on their voting behavior and predictability.
+Swing states, sometimes referred to as "battleground states," are those where neither major political party has a consistent or dominant advantage.
+This makes their electoral outcomes highly competitive and crucial for candidates aiming to secure a majority in the Electoral College.
+These states can shift between supporting Republican and Democratic candidates from one election to the next, depending on factors such as voter turnout, shifting demographics, and regional issues.
+Examples of prominent swing states for the 2024 election include Arizona, Georgia, Pennsylvania, Michigan, Nevada, North Carolina, and Wisconsin, as these states have shown significant variability in their support for both parties in recent election cycles (@citeSwing1) (@citeSwing2).
 
-# Methodology Analysis of The Economist/YouGov Poll (October 6–7, 2024)
+In contrast, solid states are those that consistently support one political party by a substantial margin, making their outcomes highly predictable in presidential elections.
+For instance, states like California and New York are considered solidly Democratic, while states like Alabama and Idaho are reliably Republican.
+These solid states play a lesser role in the competitive dynamics of presidential campaigns, as their electoral votes are typically seen as secure for the party that historically dominates them.
+Consequently, candidates often focus their campaign efforts, resources, and messaging on swing states where the race is closer, since these states ultimately have the potential to decide the outcome of the election (@citeSwing1).
+
+# Methodology Analysis of The Economist/YouGov Poll (October 6–7, 2024) {#sec-meth}
 
@@
 
-# Methodology and Survey Design for 2024 U.S. Presidential Election Forecast
+# Methodology and Survey Design for 2024 U.S. Presidential Election Forecast {#sec-survey}
 
 ## Overview
-This methodology presents an election forecasting plan with a budget of $100,000 focusing on swing states which are states where election outcomes are uncertain, making them crucial for forecasting the Electoral College result.
-Drawing on insights from YouGov and  Annual Review of Economics regarding survey methods, we chose an online format to improve accessibility and minimize selection bias, allowing respondents to participate at their convenience.
-This approach is especially suitable for students and working-age individuals, who may have limited availability during traditional hours.
-Mobile technology further enhances engagement, reaching populations that are otherwise challenging to access, such as seniors and mobile-first respondents.
-To maintain engagement and prevent drop-offs, we designed a concise survey with digital incentives to attract a broad participant base across income levels.
-By incorporating techniques from both institutions, our methodology is designed to be cost-effective and demographically balanced, producing reliable predictions for the 2024 U.S.
-Presidential Election.
+This methodology outlines an election forecasting plan with a budget of $100,000, focusing on swing states where election outcomes are uncertain, making them essential for forecasting the Electoral College result.
+Drawing on research from YouGov and the Annual Review of Economics on survey methods, we selected an online format to improve accessibility and reduce selection bias, allowing respondents to participate at their convenience(@citeStantcheva2023).
+This approach is particularly suited for students and working-age individuals who may have limited availability during traditional hours.
+Mobile technology also increases participation, reaching groups that are otherwise difficult to access, such as seniors and individuals who primarily use mobile devices.
+To encourage participation and reduce drop-offs, we created a concise survey with digital incentives to attract a broad range of respondents across income levels.
+By incorporating methods from both sources, our approach is designed to be cost-effective and demographically balanced, offering reliable predictions for the 2024 U.S. Presidential Election.
 

### 2024-11-03 paper/paper.qmd
Update state_votes correspondence.

@@
 
-intercept_wide$`Votes` <- c(6, 11, 10, 15, 19, 16, 16)
+# Used dictionary-like vector to ensure the correct correspondence
+state_votes <- c(
+  Nevada = 6,
+  Arizona = 11,
+  Wisconsin = 10,
+  Michigan = 15,
+  Pennsylvania = 19,
+  `North Carolina` = 16,
+  Georgia = 16
+)
+
+# Use the named vector to add the votes to intercept_wide
+intercept_wide <- intercept_wide %>%
+  mutate(Votes = state_votes[State])
 

### 2024-11-03 paper/paper.qmd
Updated introduction and abstract

@@
 This paper uses a poll-of-polls approach, combined with a dynamic linear regression model that updates daily with the latest data, to forecast the popular vote and outcomes in seven battleground states: Arizona, Georgia, Nevada, North Carolina, Michigan, Wisconsin, and Pennsylvania.
-Our analysis currently projects that Vice President Harris will win the popular vote, 48.19% to 46.01%, and secure the electoral college with 302 votes to Trump’s 236, by winning five of these seven swing states: Nevada, North Carolina, Michigan, Wisconsin, and Pennsylvania.
+Our analysis currently projects that Vice President Harris will win the popular vote, 48.19% to 46.01%, and secure the electoral college with 292 votes to Trump’s 246, by winning five of these seven swing states: Nevada, North Carolina, Michigan, Wisconsin, and Pennsylvania.
 By aggregating multiple polls rather than relying on a single poll, our model provides a more robust prediction, supporting the likelihood of a Harris victory."
@@
 Excluding swing states, Harris would receive 226 electoral votes, while Trump would receive 219.
-According to our Primary Model, Harris is expected to capture five of the seven swing states: Nevada, North Carolina, Michigan, Wisconsin, and Pennsylvania, yielding a total of 302 electoral votes and thus securing the presidency.
-Trump would win two swing states, Arizona and Georgia, ending with 236 electoral votes.
+According to our Primary Model, Harris is expected to capture five of the seven swing states: Nevada, North Carolina, Michigan, Wisconsin, and Pennsylvania, yielding a total of 292 electoral votes and thus securing the presidency.
+Trump would win two swing states, Arizona and Georgia, ending with 246 electoral votes.
 Although Harris's lead in North Carolina is narrow (by just 0.036%), which may switch to voting for Trump in the future, but 19 votes in this state in the face of overwhelming vote margins won't have much of an impact on the outcome.

### 2024-11-04 paper/paper.qmd
Created acknowledgements and citations.
Added references.bib accordingly.

@@
 library(styler)
+library(lubridate)
+library(validate)
 ```
@@
 ## Dataset Overview
+
+The dataset by @fivethirtyeight2024 comprises 16,867 rows and 52 columns, offering a detailed representation of polling data relevant to electoral analysis.
+To derive the percentage of support for each choice from the pollster, the raw vote counts associated with each candidate or option are normalized by dividing them by the total sample size for that particular poll.
+This calculation converts the raw counts into percentages (pct), allowing for a clearer comparison of candidate support across different polls and facilitating more straightforward interpretations of public sentiment regarding the electoral options presented.
 
@@
 
+Here’s the revised acknowledgments section using "we" and incorporating `@citeR` for R:
+
+# Acknowledgements
+
+We would like to express our gratitude to the developers and contributors of the R programming language by @citeR and its ecosystem of packages, which have been invaluable in conducting this research.
+The **tidyverse** collection by @tidyverse, particularly its extensive functionality for data manipulation and visualization, has greatly enhanced the clarity and effectiveness of our analysis.
+
+For generating compact and informative summaries of our data, we utilized the **skimr** package by @skimr, which provided a flexible overview of the dataset.
+The **knitr** package by @knitr facilitated the dynamic report generation, allowing us to seamlessly integrate analysis results into our documentation.
+
+To enhance our visualizations, we employed **GGally** by @ggally, an extension of **ggplot2**, which allowed for more complex and informative graphics .
+The **dplyr** package by @dplyr was instrumental in data manipulation, enabling efficient data transformation and summarization.
+For converting statistical results into tidy formats, we relied on the **broom** package by @broom, which simplified the reporting of statistical outputs .
+
+We also utilized **styler** by @styler to maintain a clean and readable codebase, ensuring that our R scripts adhered to best practices for code formatting.
+The **lubridate** package by @lubridate simplified the handling of date and time data, which was crucial for temporal analyses .
+Lastly, the **validate** package by @validate played a key role in ensuring the integrity and validity of our data throughout the research process.
+
+The contributions of these packages have greatly enriched our work, and we appreciate the effort of the R community in maintaining and enhancing these resources.
+
 # References

### 2024-11-04 paper/paper.qmd
Applied use of parquet files for analysis data.

@@
 library(validate)
+library(arrow)
 ```
@@
 #| include: false
-data <- read.csv("../data/02-analysis_data/cleaned_president_polls.csv")
+data <- read_parquet("../data/02-analysis_data/cleaned_president_polls.parquet")
 ```
@@
 We would like to express our gratitude to the developers and contributors of the R programming language by @citeR and its ecosystem of packages, which have been invaluable in conducting this research.
-The **tidyverse** collection by @tidyverse, particularly its extensive functionality for data manipulation and visualization, has greatly enhanced the clarity and effectiveness of our analysis.
+The **tidyverse** collection by @tidyverse, particularly its extensive functionality for data manipulation and visualization, has greatly enhanced the clarity and effectiveness of our analysis, and **arrow** package by @arrow enables us to work with parquet files.
 

### 2024-11-04 scripts/02-clean_data.R

@@ -7,6 +7,13 @@
 
 #### Workspace setup ####
 library(tidyverse)
+if (!requireNamespace("arrow", quietly = TRUE)) {
+  install.packages("arrow")
+}
+
+# Load the arrow package
+library(arrow)
+
 
 #### Clean data ####
 data <- read_csv("data/01-raw_data/president_polls.csv")
@@ -46,5 +53,8 @@ data <- data %>%
 
 
 #### Save data ####
-write_csv(data, "data/02-analysis_data/cleaned_president_polls.csv")
+# write_csv(data, "data/02-analysis_data/cleaned_president_polls.csv")
 
+
+# Write the data to a Parquet file
+write_parquet(data, "data/02-analysis_data/cleaned_president_polls.parquet")

### 2024-11-04 scripts/03-test_analysis_data.R

@@ -8,10 +8,10 @@
 #### Workspace setup ####
 library(tidyverse)
 library(validate)
+library(arrow)
 
 # Load data
-# data <- read_csv("data/00-simulated_data/simulated_polls.csv")
-data <- read_csv("data/02-analysis_data/cleaned_president_polls.csv")
+data <- read_parquet("data/02-analysis_data/cleaned_president_polls.parquet")
 
 # Define validation rules
 rules <- validator(

### 2024-11-04 paper/paper.qmd
Updated title and caption

@@
 title: "Forecasting the 2024 U.S. Presidential Election: A Poll-Based Approach"
-subtitle: "Kamala Harris Poised for Victory"
+subtitle: "Kamala Harris Projected to Win the Electoral College with 292 Votes to Donald Trump’s 246"
 author: 
@@
 
-![Result](../other/photos/Predicted_Result.png){#fig-result}
+![Projected Electoral College Results for the 2024 U.S.
+Presidential Election, with Kamala Harris Expected to Secure 292 Electoral Votes Against Donald Trump’s 246](../other/photos/Predicted_Result.png){#fig-result}
 
@@
 
-![YouGov Welcome Page](../other/photos/YouGov_Welcome_Page.png){#fig-YouGovWelcomePage width=60%}
+![Initial welcome screen during YouGov onboarding, confirming country of residence and introducing users to the platform's privacy policies and terms](../other/photos/YouGov_Welcome_Page.png){#fig-YouGovWelcomePage width=60%}
 
@@
 
-![YouGov Survey](../other/photos/YouGov_Survey.png){#fig-YouGovSurvey width=60%}
+![Example of a YouGov survey question, designed to gather demographic information and establish privacy preferences, fostering user engagement through a clear and straightforward layout](../other/photos/YouGov_Survey.png){#fig-YouGovSurvey width=60%}
 
@@
 
-![YouGov Email Verification](../other/photos/YouGov_Email_Verification.png){#fig-YouGovEmailVerification width=60%}
+![Email verification screen to confirm user identity, enhancing data integrity by preventing duplicate or fraudulent accounts](../other/photos/YouGov_Email_Verification.png){#fig-YouGovEmailVerification width=60%}
 
@@
 
-![YouGov Data Privacy](../other/photos/YouGov_Data_Privacy.png){#fig-YouGovDataPrivacy width=60%}
+![Data privacy options allowing users to control the sharing of their information with third parties, reflecting YouGov’s commitment to transparency and user autonomy](../other/photos/YouGov_Data_Privacy.png){#fig-YouGovDataPrivacy width=60%}
 
@@
 
-![YouGov Interface](../other/photos/YouGov_Interface.png){#fig-YouGovInterface width=60%}
+![Overview of YouGov’s gamified rewards system, where participants accumulate points redeemable for gift cards, potentially motivating user engagement with surveys](../other/photos/YouGov_Interface.png){#fig-YouGovInterface width=60%}
 

### 2024-11-04 paper/paper.qmd
Updated EDA part

@@
 @sec-meth and @sec-survey delve into the methodology and design of the Economist/YouGov poll and an election forecasting survey, outlining sampling methods, data validation processes, and strategic considerations for accurate and reliable polling results.
+@sec-ack acknowledges the invaluable contributions of various R packages and their developers, which enabled efficient data manipulation, visualization, and analysis, ensuring the clarity, reliability, and integrity of the research.
 
@@
 #| echo: false
+#| label: fig-mtl
+#| fig-cap: Pair Plot of Numeric Predictors for Poll Quality Metrics
 numeric_data <- data %>% 
@@
 
+### Swing State Summary Statistics
 ```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-sum
+#| tbl-cap: Summary Statistics of Poll Quality Metrics Across Key Swing States
+
 data_swing <- data %>% filter(state %in% c("Nevada", "Arizona", "Wisconsin", "Michigan", "Pennsylvania", "North Carolina", "Georgia"))
@@
 ```
+@tbl-sum provides summary statistics for seven key swing states, focusing on mean values of poll-related metrics, including "pollscore," "numeric_grade," "transparency_score," and "sample_size." These averages offer a snapshot of polling data characteristics in each state, emphasizing differences in sample quality and transparency.
+Understanding these state-level nuances aids in refining state-specific projections in our electoral model.
 
+### Distribution of Sample Sizes
 ```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: fig-sam
+#| fig-cap: Histogram of Poll Sample Sizes Below 10,000 Respondents
 data %>% 
@@
 ```
-
+@fig-sam displays the distribution of poll sample sizes for values below 10,000.
+By illustrating the frequency of various sample sizes, this plot highlights the typical range of sample sizes in our dataset, with a majority clustering under 2,000.
+This visualization informs the model's sensitivity to sample size variability, which can impact the reliability of poll predictions.
 ```{r}
+#| warning: false
+#| message: false
+#| include: false
 data %>% 
@@
 
-To understand the general trends in the data, we conducted exploratory data analysis using summary statistics and visualizations.
-Figure 1 (below) illustrates the polling percentages for each candidate over time, allowing us to observe fluctuations in support as the election day draws near.
-
+### Polling Percentage Over Time by Candidate
+@fig-pct illustrates polling percentages for Kamala Harris and Donald Trump over time, with data points spanning from early 2024 to the election date.
+Smoothed trend lines capture fluctuations in public support, providing a clear visual of each candidate's trajectory as election day nears.
+Notable shifts in polling percentage offer insights into campaign impacts and shifting voter sentiment.
 ```{r}
@@
 
-# Acknowledgements
+# Acknowledgements{#sec-ack}
 

### 2024-11-04 paper/paper.qmd
Updated plots

@@
 
-This study leverages a dataset of polling data for the 2024 U.S.
+This study leverages the dataset of polling data for the 2024 U.S.
 Presidential Election, focusing on predicting support for the two main candidates, Kamala Harris and Donald Trump.
@@
 Kamala Harris is projected to win 292 electoral votes, surpassing the 270-vote threshold required to secure victory.
-Donald Trump, by comparison, is projected to receive 246 electoral votes.
-This projection, based on aggregating state-level outcomes, suggests that Harris has a favorable chance of achieving the necessary electoral college majority if current polling trends continue.
+Donald Trump, by comparison, is projected to receive 246 electoral votes, as shown in @tbl-res and @fig-result .This projection, based on aggregating state-level outcomes, suggests that Harris has a favorable chance of achieving the necessary electoral college majority if current polling trends continue.
 The model indicates that Harris’s projected wins in swing states like Wisconsin, Michigan, and Pennsylvania could be critical to her securing an electoral majority.
@@
 #| warning: false
+#| label: tbl-res
+#| tbl-cap: Predicted Electoral Votes for Each Candidate
 solid_state_votes <- data.frame(
@@
 # View the results
-kable(total_votes, caption = "Predicted Electoral Votes for Each Candidate")
+kable(total_votes)
 

### 2024-11-04 paper/paper.qmd
Updated data section

@@
 
-The dataset by @fivethirtyeight2024 comprises 16,867 rows and 52 columns, offering a detailed representation of polling data relevant to electoral analysis.
-To derive the percentage of support for each choice from the pollster, the raw vote counts associated with each candidate or option are normalized by dividing them by the total sample size for that particular poll.
-This calculation converts the raw counts into percentages (pct), allowing for a clearer comparison of candidate support across different polls and facilitating more straightforward interpretations of public sentiment regarding the electoral options presented.
+The dataset by @fivethirtyeight2024 provides comprehensive polling data for the U.S.
+Presidential Election, originally containing 16,867 rows and 52 columns.
+This raw data has been processed to yield a more focused dataset of 5,187 entries and 11 columns, which is used for future analysis.
+A detailed explanatory analysis and statistical summaries are mentioned in @sec-eda.
+The cleaned dataset includes essential details necessary for modeling and forecasting electoral outcomes.
 
-This study leverages the dataset of polling data for the 2024 U.S.
-Presidential Election, focusing on predicting support for the two main candidates, Kamala Harris and Donald Trump.
-Each entry in the dataset represents results from individual polls, capturing both the timing and geographical scope of polling, which is crucial for analyzing national trends and state-specific shifts, particularly in key swing states.
-By collating data from multiple polling sources, the dataset captures a broad snapshot of voter sentiment across the country, reflecting variations across time, poll methodologies, and geographic regions.
+Each row in the dataset represents the outcome of one candidate in a poll, capturing both the poll date, location, estimated quality of the pollster, and the questions mentioned in the poll, which is instrumental in tracking national trends and observing variations across different states, particularly swing states.
+Polling data from a variety of sources is aggregated, offering a broad view of voter sentiment across diverse regions and demographic groups, as well as over time.
 
-The outcome variable, **Polling Percentage ("pct")**, represents the percentage of respondents in each poll who indicate support for either Harris or Trump.
-This variable is central to our analysis, as it reflects the changing landscape of voter sentiment and serves as the basis for our forecasts.
+The primary outcome variable, **Polling Percentage ("pct")**, represents the percentage of poll respondents supporting either Kamala Harris or Donald Trump in each poll.
+This measure, derived by normalizing each candidate’s vote count by the total sample size of each poll, provides a standardized way to compare support levels across polls, enabling a clearer analysis of voter preferences and shifts in public opinion.
 
@@
 
-## Exploratory Data Analysis and Summary Statistics
+## Exploratory Data Analysis and Summary Statistics{#sec-eda}
 

### 2024-11-04 paper/paper.qmd
Updated file structure and survey

@@
 
-## Swing State-Based Model  
+## Primary Model (Swing State-Based Model)                                                   
 This model forecasts electoral outcomes by projecting each candidate’s polling results in individual swing states, then combining those results with electoral votes from states that are already solidly in favor of one candidate or the other.
@@
 ## Copy of Survey
-Below is the full content of the survey to be implemented using Google Forms:
+2024 U.S. Presidential Election Survey
 
-1. What is your age?  
+Thank you for participating in this survey about the 2024 U.S. presidential election.
+
+Please note that:
+- All responses will remain strictly confidential and will only be used for research purposes.
+- Your participation is voluntary, and you may withdraw from the survey at any time.
+- The survey contains 21 questions and should take about 10 minutes to complete.
+
+We kindly ask that you answer each question honestly and to the best of your knowledge.
+
+For questions or concerns, please contact:
+**Ariel Xing, Research Coordinator**  
+Email: [ariel.xing@mail.utoronto.ca](mailto:ariel.xing@mail.utoronto.ca)
+
+---
+
+## Section 1: Eligibility Screening
+
+1. **Are you a U.S. citizen?**  
+   - Yes  
+   - No
+
+2. **Will you be 18 or older by November 5, 2024 (Election Day)?**  
+   - Yes  
+   - No
+
+3. **Are you registered to vote in the United States?**  
+   - Yes  
+   - No  
+   - Plan to register before the election  
+   - Not sure
+
+4. **Have you ever been convicted of a crime that affects your voting eligibility?**  
+   - No  
+   - Yes, but my voting rights have been restored  
+   - Yes, and my voting rights have not been restored yet  
+   - Not Sure  
+   - Prefer not to say
+
+5. **Which state do you currently reside in?**  
+   - Arizona  
+   - Georgia  
+   - Nevada  
+   - North Carolina  
+   - Michigan  
+   - Wisconsin  
+   - Pennsylvania  
+   - Other: [Short text answer]
+
+---
+
+## Section 2: Demographic Information
+
+**Note:** Your responses in this survey will be treated with the highest level of confidentiality and will only be used for research purposes.
+No identifying information will be shared outside of the research team, ensuring your privacy is fully protected.
+
+6. **What is your age?**  
    - 18-24  
@@
 
-2. What is your gender?  
+7. **What is your gender?**  
    - Male  
    - Female  
-   - Other: ___
+   - Other: [Short text answer]
 
-3. What is your race/ethnicity?  
+8. **What is your race/ethnicity?**  
    - White  
@@
    - Indigenous  
-   - Other: ___
+   - Other: [Short text answer]
 
-4. What is your highest level of education?  
+9. **What is your highest level of education?**  
    - Less than high school  
@@
 
-5. What is your annual household income?  
+10. **What is your annual household income?**  
     - Less than $25,000  
@@
 
-6. Which state do you currently reside in?
+---
 
-7. Are you a registered voter?  
-   - Yes  
-   - No  
-   - Not sure
+## Section 3: Political Views and Voting Intentions
 
-8. How likely are you to vote in the 2024 presidential election?  
-   - 1 (Definitely will not vote)  
+11. **How likely are you to vote in the 2024 presidential election?**  
+    - Definitely will not vote  
+    - 1  
     - 2  
@@
     - 4  
-   - 5 (Definitely will vote)
+    - Definitely will vote
 
-9. If the 2024 election were held today, who would you vote for?  
+12. **Generally speaking, how do you identify politically?**  
+    - Democrat  
+    - Republican  
+    - Independent  
+    - Other: [Short text answer]
+
+13. **How open are you to changing your political views if presented with new information or perspectives?**  
+    - Very open  
+    - 1  
+    - 2  
+    - 3  
+    - 4  
+    - Not at all open
+
+14. **What is your opinion on the effectiveness of the current U.S. government administration?**  
+    - Very effective  
+    - Somewhat effective  
+    - Neutral  
+    - Somewhat ineffective  
+    - Very ineffective  
+    - Prefer not to say
+
+15. **If the 2024 election were held today, who would you vote for?**  
     - Kamala Harris (Democrat)  
@@
     - Undecided  
-   - Other: ___
+    - Other: [Short text answer]
 
-10. What is the most important issue for you in this election?  
+16. **What is the most important issue for you in this election?**  
     - The economy  
@@
 
-11. In your opinion, how will the majority in your state vote in 2024?  
+17. **In your opinion, how will the majority in your state vote in 2024?**  
     - Democrat  
@@
 
-12. Do you have any additional comments or suggestions?
+18. **Have you previously voted in a U.S. Presidential election?**  
+    - Yes  
+    - No, because this is the first year I am eligible to vote  
+    - No, I chose not to vote in the past  
+    - Prefer not to say
 
-Thank you for completing the survey! Your input is greatly appreciated and will help provide insights into the upcoming 2024 election.
+---
 
-Here’s the revised acknowledgments section using "we" and incorporating `@citeR` for R:
+## Section 4: Information Sources and Engagement
+
+19. **How closely have you been following news about the 2024 Presidential election?**  
+    - Very closely  
+    - Somewhat closely  
+    - Not too closely  
+    - Not at all
+
+---
+
+## Section 5: Verification and Consent
+
+20. **To help us verify that this survey is being completed by a real person, please select the largest number from the following choices:**  
+    - 4  
+    - 10  
+    - 7  
+    - 2
+
+21.
+**Do you agree to participate in this survey with the understanding that your involvement is entirely voluntary, that you may choose to stop at any time, and that all of your responses will be kept confidential and used solely for research purposes?**
+    - Yes, I understand that my participation is voluntary, that I can withdraw at any time, and that my responses will remain confidential and used only for research.  
+    - No, I do not agree to these terms.
+
+---
+
+**Thank You Message**
+
+Thank you for taking the time to complete this survey!
+We are grateful for your willingness to share your thoughts, and your input will play an important role in shaping a clearer picture of voter opinions and priorities.
+Your response will be kept confidential.
+If you have any further questions or would like to stay updated on the findings from this survey, please feel free to reach out to us.
 
